---
title: "StateSpaceHerbaceous"
author: "Samuel Worley"
date: "Wednesday, April 01, 2015"
output: html_document
---
```{r}
library(rjags)
library(R2WinBUGS)
```

#data connection
```{r}
dat.herb=read.csv("HerbaceousBiomass.csv",header=TRUE)
years=c("08S", "08F", "09S", "09F", "10S", "10F", "11S", "11F", "12S", "12F", "13S", "13F", "14S", "14F")

## 2008 year subsetted by season 
dat.08=dat.herb[dat.herb$Year==2008,]
dat.08.fall=dat.08[dat.08$Season=="Fall",]
dat.08.summ=dat.08[dat.08$Season=="Summer",]
dat.08.fall.m=as.numeric(dat.08.fall$Total.Mass)
dat.08.summ.m=as.numeric(dat.08.summ$Total.Mass)
#Means,95% intervals, standarad deviation, 
dat.08.fall.95=quantile(dat.08.fall.m,c(.05,.95))
dat.08.summ.95=quantile(dat.08.summ.m,c(.05,.95))
dat.08.fall.mean=mean(dat.08.fall.m)
dat.08.summ.mean=mean(dat.08.summ.m)
dat.08.fall.sd=sd(dat.08.fall.m)
dat.08.summ.sd=sd(dat.08.summ.m)
```

#2008
```{r}
#functional group by plot
#dat.13.fall.c4=as.numeric(dat.13.fall$C4) #36*2 for each plot there is two subplots


#2008 
p1.08.f.C4=sum(as.numeric(p1.08.f$C4))
p1.08.f.C3=sum(as.numeric(p1.08.f$C3))
p1.08.f.Pr=sum(as.numeric(p1.08.f$Perennial))
p1.08.f.AB=sum(as.numeric(p1.08.f$Annl.Biennial))

p2.08.f.C4=sum(as.numeric(p2.08.f$C4))
p2.08.f.C3=sum(as.numeric(p2.08.f$C3))
p2.08.f.Pr=sum(as.numeric(p2.08.f$Perennial))
p2.08.f.AB=sum(as.numeric(p2.08.f$Annl.Biennial))

p3.08.f.C4=sum(as.numeric(p3.08.f$C4))
p3.08.f.C3=sum(as.numeric(p3.08.f$C3))
p3.08.f.Pr=sum(as.numeric(p3.08.f$Perennial))
p3.08.f.AB=sum(as.numeric(p3.08.f$Annl.Biennial))

p4.08.f.C4=sum(as.numeric(p4.08.f$C4))
p4.08.f.C3=sum(as.numeric(p4.08.f$C3))
p4.08.f.Pr=sum(as.numeric(p4.08.f$Perennial))
p4.08.f.AB=sum(as.numeric(p4.08.f$Annl.Biennial))

p5.08.f.C4=sum(as.numeric(p5.08.f$C4))
p5.08.f.C3=sum(as.numeric(p5.08.f$C3))
p5.08.f.Pr=sum(as.numeric(p5.08.f$Perennial))
p5.08.f.AB=sum(as.numeric(p5.08.f$Annl.Biennial))

p6.08.f.C4=sum(as.numeric(p6.08.f$C4))
p6.08.f.C3=sum(as.numeric(p6.08.f$C3))
p6.08.f.Pr=sum(as.numeric(p6.08.f$Perennial))
p6.08.f.AB=sum(as.numeric(p6.08.f$Annl.Biennial))

p7.08.f.C4=sum(as.numeric(p7.08.f$C4))
p7.08.f.C3=sum(as.numeric(p7.08.f$C3))
p7.08.f.Pr=sum(as.numeric(p7.08.f$Perennial))
p7.08.f.AB=sum(as.numeric(p7.08.f$Annl.Biennial))

p8.08.f.C4=sum(as.numeric(p8.08.f$C4))
p8.08.f.C3=sum(as.numeric(p8.08.f$C3))
p8.08.f.Pr=sum(as.numeric(p8.08.f$Perennial))
p8.08.f.AB=sum(as.numeric(p8.08.f$Annl.Biennial))

p9.08.f.C4=sum(as.numeric(p9.08.f$C4))
p9.08.f.C3=sum(as.numeric(p9.08.f$C3))
p9.08.f.Pr=sum(as.numeric(p9.08.f$Perennial))
p9.08.f.AB=sum(as.numeric(p9.08.f$Annl.Biennial))

p10.08.f.C4=sum(as.numeric(p10.08.f$C4))
p10.08.f.C3=sum(as.numeric(p10.08.f$C3))
p10.08.f.Pr=sum(as.numeric(p10.08.f$Perennial))
p10.08.f.AB=sum(as.numeric(p10.08.f$Annl.Biennial))

p11.08.f.C4=sum(as.numeric(p11.08.f$C4))
p11.08.f.C3=sum(as.numeric(p11.08.f$C3))
p11.08.f.Pr=sum(as.numeric(p11.08.f$Perennial))
p11.08.f.AB=sum(as.numeric(p11.08.f$Annl.Biennial))

p12.08.f.C4=sum(as.numeric(p12.08.f$C4))
p12.08.f.C3=sum(as.numeric(p12.08.f$C3))
p12.08.f.Pr=sum(as.numeric(p12.08.f$Perennial))
p12.08.f.AB=sum(as.numeric(p12.08.f$Annl.Biennial))

p13.08.f.C4=sum(as.numeric(p13.08.f$C4))
p13.08.f.C3=sum(as.numeric(p13.08.f$C3))
p13.08.f.Pr=sum(as.numeric(p13.08.f$Perennial))
p13.08.f.AB=sum(as.numeric(p13.08.f$Annl.Biennial))

p14.08.f.C4=sum(as.numeric(p14.08.f$C4))
p14.08.f.C3=sum(as.numeric(p14.08.f$C3))
p14.08.f.Pr=sum(as.numeric(p14.08.f$Perennial))
p14.08.f.AB=sum(as.numeric(p14.08.f$Annl.Biennial))

p15.08.f.C4=sum(as.numeric(p15.08.f$C4))
p15.08.f.C3=sum(as.numeric(p15.08.f$C3))
p15.08.f.Pr=sum(as.numeric(p15.08.f$Perennial))
p15.08.f.AB=sum(as.numeric(p15.08.f$Annl.Biennial))

p16.08.f.C4=sum(as.numeric(p16.08.f$C4))
p16.08.f.C3=sum(as.numeric(p16.08.f$C3))
p16.08.f.Pr=sum(as.numeric(p16.08.f$Perennial))
p16.08.f.AB=sum(as.numeric(p16.08.f$Annl.Biennial))

p17.08.f.C4=sum(as.numeric(p17.08.f$C4))
p17.08.f.C3=sum(as.numeric(p17.08.f$C3))
p17.08.f.Pr=sum(as.numeric(p17.08.f$Perennial))
p17.08.f.AB=sum(as.numeric(p17.08.f$Annl.Biennial))

p18.08.f.C4=sum(as.numeric(p18.08.f$C4))
p18.08.f.C3=sum(as.numeric(p18.08.f$C3))
p18.08.f.Pr=sum(as.numeric(p18.08.f$Perennial))
p18.08.f.AB=sum(as.numeric(p18.08.f$Annl.Biennial))

p19.08.f.C4=sum(as.numeric(p19.08.f$C4))
p19.08.f.C3=sum(as.numeric(p19.08.f$C3))
p19.08.f.Pr=sum(as.numeric(p19.08.f$Perennial))
p19.08.f.AB=sum(as.numeric(p19.08.f$Annl.Biennial))

p20.08.f.C4=sum(as.numeric(p20.08.f$C4))
p20.08.f.C3=sum(as.numeric(p20.08.f$C3))
p20.08.f.Pr=sum(as.numeric(p20.08.f$Perennial))
p20.08.f.AB=sum(as.numeric(p20.08.f$Annl.Biennial))

p21.08.f.C4=sum(as.numeric(p21.08.f$C4))
p21.08.f.C3=sum(as.numeric(p21.08.f$C3))
p21.08.f.Pr=sum(as.numeric(p21.08.f$Perennial))
p21.08.f.AB=sum(as.numeric(p21.08.f$Annl.Biennial))

p22.08.f.C4=sum(as.numeric(p22.08.f$C4))
p22.08.f.C3=sum(as.numeric(p22.08.f$C3))
p22.08.f.Pr=sum(as.numeric(p22.08.f$Perennial))
p22.08.f.AB=sum(as.numeric(p22.08.f$Annl.Biennial))

p23.08.f.C4=sum(as.numeric(p23.08.f$C4))
p23.08.f.C3=sum(as.numeric(p23.08.f$C3))
p23.08.f.Pr=sum(as.numeric(p23.08.f$Perennial))
p23.08.f.AB=sum(as.numeric(p23.08.f$Annl.Biennial))

p24.08.f.C4=sum(as.numeric(p24.08.f$C4))
p24.08.f.C3=sum(as.numeric(p24.08.f$C3))
p24.08.f.Pr=sum(as.numeric(p24.08.f$Perennial))
p24.08.f.AB=sum(as.numeric(p24.08.f$Annl.Biennial))

p25.08.f.C4=sum(as.numeric(p25.08.f$C4))
p25.08.f.C3=sum(as.numeric(p25.08.f$C3))
p25.08.f.Pr=sum(as.numeric(p25.08.f$Perennial))
p25.08.f.AB=sum(as.numeric(p25.08.f$Annl.Biennial))

p26.08.f.C4=sum(as.numeric(p26.08.f$C4))
p26.08.f.C3=sum(as.numeric(p26.08.f$C3))
p26.08.f.Pr=sum(as.numeric(p26.08.f$Perennial))
p26.08.f.AB=sum(as.numeric(p26.08.f$Annl.Biennial))

p27.08.f.C4=sum(as.numeric(p27.08.f$C4))
p27.08.f.C3=sum(as.numeric(p27.08.f$C3))
p27.08.f.Pr=sum(as.numeric(p27.08.f$Perennial))
p27.08.f.AB=sum(as.numeric(p27.08.f$Annl.Biennial))

p28.08.f.C4=sum(as.numeric(p28.08.f$C4))
p28.08.f.C3=sum(as.numeric(p28.08.f$C3))
p28.08.f.Pr=sum(as.numeric(p28.08.f$Perennial))
p28.08.f.AB=sum(as.numeric(p28.08.f$Annl.Biennial))

p29.08.f.C4=sum(as.numeric(p29.08.f$C4))
p29.08.f.C3=sum(as.numeric(p29.08.f$C3))
p29.08.f.Pr=sum(as.numeric(p29.08.f$Perennial))
p29.08.f.AB=sum(as.numeric(p29.08.f$Annl.Biennial))

p30.08.f.C4=sum(as.numeric(p30.08.f$C4))
p30.08.f.C3=sum(as.numeric(p30.08.f$C3))
p30.08.f.Pr=sum(as.numeric(p30.08.f$Perennial))
p30.08.f.AB=sum(as.numeric(p30.08.f$Annl.Biennial))

p31.08.f.C4=sum(as.numeric(p31.08.f$C4))
p31.08.f.C3=sum(as.numeric(p31.08.f$C3))
p31.08.f.Pr=sum(as.numeric(p31.08.f$Perennial))
p31.08.f.AB=sum(as.numeric(p31.08.f$Annl.Biennial))

p32.08.f.C4=sum(as.numeric(p32.08.f$C4))
p32.08.f.C3=sum(as.numeric(p32.08.f$C3))
p32.08.f.Pr=sum(as.numeric(p32.08.f$Perennial))
p32.08.f.AB=sum(as.numeric(p32.08.f$Annl.Biennial))

p33.08.f.C4=sum(as.numeric(p33.08.f$C4))
p33.08.f.C3=sum(as.numeric(p33.08.f$C3))
p33.08.f.Pr=sum(as.numeric(p33.08.f$Perennial))
p33.08.f.AB=sum(as.numeric(p33.08.f$Annl.Biennial))

p34.08.f.C4=sum(as.numeric(p34.08.f$C4))
p34.08.f.C3=sum(as.numeric(p34.08.f$C3))
p34.08.f.Pr=sum(as.numeric(p34.08.f$Perennial))
p34.08.f.AB=sum(as.numeric(p34.08.f$Annl.Biennial))

p35.08.f.C4=sum(as.numeric(p35.08.f$C4))
p35.08.f.C3=sum(as.numeric(p35.08.f$C3))
p35.08.f.Pr=sum(as.numeric(p35.08.f$Perennial))
p35.08.f.AB=sum(as.numeric(p35.08.f$Annl.Biennial))

p36.08.f.C4=sum(as.numeric(p36.08.f$C4))
p36.08.f.C3=sum(as.numeric(p36.08.f$C3))
p36.08.f.Pr=sum(as.numeric(p36.08.f$Perennial))
p36.08.f.AB=sum(as.numeric(p36.08.f$Annl.Biennial))

#summer
p1.08.s.C4=sum(as.numeric(p1.08.s$C4))
p1.08.s.C3=sum(as.numeric(p1.08.s$C3))
p1.08.s.Pr=sum(as.numeric(p1.08.s$Perennial))
p1.08.s.AB=sum(as.numeric(p1.08.s$Annl.Biennial))

p2.08.s.C4=sum(as.numeric(p2.08.s$C4))
p2.08.s.C3=sum(as.numeric(p2.08.s$C3))
p2.08.s.Pr=sum(as.numeric(p2.08.s$Perennial))
p2.08.s.AB=sum(as.numeric(p2.08.s$Annl.Biennial))

p3.08.s.C4=sum(as.numeric(p3.08.s$C4))
p3.08.s.C3=sum(as.numeric(p3.08.s$C3))
p3.08.s.Pr=sum(as.numeric(p3.08.s$Perennial))
p3.08.s.AB=sum(as.numeric(p3.08.s$Annl.Biennial))

p4.08.s.C4=sum(as.numeric(p4.08.s$C4))
p4.08.s.C3=sum(as.numeric(p4.08.s$C3))
p4.08.s.Pr=sum(as.numeric(p4.08.s$Perennial))
p4.08.s.AB=sum(as.numeric(p4.08.s$Annl.Biennial))

p5.08.s.C4=sum(as.numeric(p5.08.s$C4))
p5.08.s.C3=sum(as.numeric(p5.08.s$C3))
p5.08.s.Pr=sum(as.numeric(p5.08.s$Perennial))
p5.08.s.AB=sum(as.numeric(p5.08.s$Annl.Biennial))

p6.08.s.C4=sum(as.numeric(p6.08.s$C4))
p6.08.s.C3=sum(as.numeric(p6.08.s$C3))
p6.08.s.Pr=sum(as.numeric(p6.08.s$Perennial))
p6.08.s.AB=sum(as.numeric(p6.08.s$Annl.Biennial))

p7.08.s.C4=sum(as.numeric(p7.08.s$C4))
p7.08.s.C3=sum(as.numeric(p7.08.s$C3))
p7.08.s.Pr=sum(as.numeric(p7.08.s$Perennial))
p7.08.s.AB=sum(as.numeric(p7.08.s$Annl.Biennial))

p8.08.s.C4=sum(as.numeric(p8.08.s$C4))
p8.08.s.C3=sum(as.numeric(p8.08.s$C3))
p8.08.s.Pr=sum(as.numeric(p8.08.s$Perennial))
p8.08.s.AB=sum(as.numeric(p8.08.s$Annl.Biennial))

p9.08.s.C4=sum(as.numeric(p9.08.s$C4))
p9.08.s.C3=sum(as.numeric(p9.08.s$C3))
p9.08.s.Pr=sum(as.numeric(p9.08.s$Perennial))
p9.08.s.AB=sum(as.numeric(p9.08.s$Annl.Biennial))

p10.08.s.C4=sum(as.numeric(p10.08.s$C4))
p10.08.s.C3=sum(as.numeric(p10.08.s$C3))
p10.08.s.Pr=sum(as.numeric(p10.08.s$Perennial))
p10.08.s.AB=sum(as.numeric(p10.08.s$Annl.Biennial))

p11.08.s.C4=sum(as.numeric(p11.08.s$C4))
p11.08.s.C3=sum(as.numeric(p11.08.s$C3))
p11.08.s.Pr=sum(as.numeric(p11.08.s$Perennial))
p11.08.s.AB=sum(as.numeric(p11.08.s$Annl.Biennial))

p12.08.s.C4=sum(as.numeric(p12.08.s$C4))
p12.08.s.C3=sum(as.numeric(p12.08.s$C3))
p12.08.s.Pr=sum(as.numeric(p12.08.s$Perennial))
p12.08.s.AB=sum(as.numeric(p12.08.s$Annl.Biennial))

p13.08.s.C4=sum(as.numeric(p13.08.s$C4))
p13.08.s.C3=sum(as.numeric(p13.08.s$C3))
p13.08.s.Pr=sum(as.numeric(p13.08.s$Perennial))
p13.08.s.AB=sum(as.numeric(p13.08.s$Annl.Biennial))

p14.08.s.C4=sum(as.numeric(p14.08.s$C4))
p14.08.s.C3=sum(as.numeric(p14.08.s$C3))
p14.08.s.Pr=sum(as.numeric(p14.08.s$Perennial))
p14.08.s.AB=sum(as.numeric(p14.08.s$Annl.Biennial))

p15.08.s.C4=sum(as.numeric(p15.08.s$C4))
p15.08.s.C3=sum(as.numeric(p15.08.s$C3))
p15.08.s.Pr=sum(as.numeric(p15.08.s$Perennial))
p15.08.s.AB=sum(as.numeric(p15.08.s$Annl.Biennial))

p16.08.s.C4=sum(as.numeric(p16.08.s$C4))
p16.08.s.C3=sum(as.numeric(p16.08.s$C3))
p16.08.s.Pr=sum(as.numeric(p16.08.s$Perennial))
p16.08.s.AB=sum(as.numeric(p16.08.s$Annl.Biennial))

p17.08.s.C4=sum(as.numeric(p17.08.s$C4))
p17.08.s.C3=sum(as.numeric(p17.08.s$C3))
p17.08.s.Pr=sum(as.numeric(p17.08.s$Perennial))
p17.08.s.AB=sum(as.numeric(p17.08.s$Annl.Biennial))

p18.08.s.C4=sum(as.numeric(p18.08.s$C4))
p18.08.s.C3=sum(as.numeric(p18.08.s$C3))
p18.08.s.Pr=sum(as.numeric(p18.08.s$Perennial))
p18.08.s.AB=sum(as.numeric(p18.08.s$Annl.Biennial))

p19.08.s.C4=sum(as.numeric(p19.08.s$C4))
p19.08.s.C3=sum(as.numeric(p19.08.s$C3))
p19.08.s.Pr=sum(as.numeric(p19.08.s$Perennial))
p19.08.s.AB=sum(as.numeric(p19.08.s$Annl.Biennial))

p20.08.s.C4=sum(as.numeric(p20.08.s$C4))
p20.08.s.C3=sum(as.numeric(p20.08.s$C3))
p20.08.s.Pr=sum(as.numeric(p20.08.s$Perennial))
p20.08.s.AB=sum(as.numeric(p20.08.s$Annl.Biennial))

p21.08.s.C4=sum(as.numeric(p21.08.s$C4))
p21.08.s.C3=sum(as.numeric(p21.08.s$C3))
p21.08.s.Pr=sum(as.numeric(p21.08.s$Perennial))
p21.08.s.AB=sum(as.numeric(p21.08.s$Annl.Biennial))

p22.08.s.C4=sum(as.numeric(p22.08.s$C4))
p22.08.s.C3=sum(as.numeric(p22.08.s$C3))
p22.08.s.Pr=sum(as.numeric(p22.08.s$Perennial))
p22.08.s.AB=sum(as.numeric(p22.08.s$Annl.Biennial))

p23.08.s.C4=sum(as.numeric(p23.08.s$C4))
p23.08.s.C3=sum(as.numeric(p23.08.s$C3))
p23.08.s.Pr=sum(as.numeric(p23.08.s$Perennial))
p23.08.s.AB=sum(as.numeric(p23.08.s$Annl.Biennial))

p24.08.s.C4=sum(as.numeric(p24.08.s$C4))
p24.08.s.C3=sum(as.numeric(p24.08.s$C3))
p24.08.s.Pr=sum(as.numeric(p24.08.s$Perennial))
p24.08.s.AB=sum(as.numeric(p24.08.s$Annl.Biennial))

p25.08.s.C4=sum(as.numeric(p25.08.s$C4))
p25.08.s.C3=sum(as.numeric(p25.08.s$C3))
p25.08.s.Pr=sum(as.numeric(p25.08.s$Perennial))
p25.08.s.AB=sum(as.numeric(p25.08.s$Annl.Biennial))

p26.08.s.C4=sum(as.numeric(p26.08.s$C4))
p26.08.s.C3=sum(as.numeric(p26.08.s$C3))
p26.08.s.Pr=sum(as.numeric(p26.08.s$Perennial))
p26.08.s.AB=sum(as.numeric(p26.08.s$Annl.Biennial))

p27.08.s.C4=sum(as.numeric(p27.08.s$C4))
p27.08.s.C3=sum(as.numeric(p27.08.s$C3))
p27.08.s.Pr=sum(as.numeric(p27.08.s$Perennial))
p27.08.s.AB=sum(as.numeric(p27.08.s$Annl.Biennial))

p28.08.s.C4=sum(as.numeric(p28.08.s$C4))
p28.08.s.C3=sum(as.numeric(p28.08.s$C3))
p28.08.s.Pr=sum(as.numeric(p28.08.s$Perennial))
p28.08.s.AB=sum(as.numeric(p28.08.s$Annl.Biennial))

p29.08.s.C4=sum(as.numeric(p29.08.s$C4))
p29.08.s.C3=sum(as.numeric(p29.08.s$C3))
p29.08.s.Pr=sum(as.numeric(p29.08.s$Perennial))
p29.08.s.AB=sum(as.numeric(p29.08.s$Annl.Biennial))

p30.08.s.C4=sum(as.numeric(p30.08.s$C4))
p30.08.s.C3=sum(as.numeric(p30.08.s$C3))
p30.08.s.Pr=sum(as.numeric(p30.08.s$Perennial))
p30.08.s.AB=sum(as.numeric(p30.08.s$Annl.Biennial))

p31.08.s.C4=sum(as.numeric(p31.08.s$C4))
p31.08.s.C3=sum(as.numeric(p31.08.s$C3))
p31.08.s.Pr=sum(as.numeric(p31.08.s$Perennial))
p31.08.s.AB=sum(as.numeric(p31.08.s$Annl.Biennial))

p32.08.s.C4=sum(as.numeric(p32.08.s$C4))
p32.08.s.C3=sum(as.numeric(p32.08.s$C3))
p32.08.s.Pr=sum(as.numeric(p32.08.s$Perennial))
p32.08.s.AB=sum(as.numeric(p32.08.s$Annl.Biennial))

p33.08.s.C4=sum(as.numeric(p33.08.s$C4))
p33.08.s.C3=sum(as.numeric(p33.08.s$C3))
p33.08.s.Pr=sum(as.numeric(p33.08.s$Perennial))
p33.08.s.AB=sum(as.numeric(p33.08.s$Annl.Biennial))

p34.08.s.C4=sum(as.numeric(p34.08.s$C4))
p34.08.s.C3=sum(as.numeric(p34.08.s$C3))
p34.08.s.Pr=sum(as.numeric(p34.08.s$Perennial))
p34.08.s.AB=sum(as.numeric(p34.08.s$Annl.Biennial))

p35.08.s.C4=sum(as.numeric(p35.08.s$C4))
p35.08.s.C3=sum(as.numeric(p35.08.s$C3))
p35.08.s.Pr=sum(as.numeric(p35.08.s$Perennial))
p35.08.s.AB=sum(as.numeric(p35.08.s$Annl.Biennial))

p36.08.s.C4=sum(as.numeric(p36.08.s$C4))
p36.08.s.C3=sum(as.numeric(p36.08.s$C3))
p36.08.s.Pr=sum(as.numeric(p36.08.s$Perennial))
p36.08.s.AB=sum(as.numeric(p36.08.s$Annl.Biennial))
```

#2009
```{r}
p1.09.f.C4=sum(as.numeric(p1.09.f$C4))
p1.09.f.C3=sum(as.numeric(p1.09.f$C3))
p1.09.f.Pr=sum(as.numeric(p1.09.f$Perennial))
p1.09.f.AB=sum(as.numeric(p1.09.f$Annl.Biennial))

p2.09.f.C4=sum(as.numeric(p2.09.f$C4))
p2.09.f.C3=sum(as.numeric(p2.09.f$C3))
p2.09.f.Pr=sum(as.numeric(p2.09.f$Perennial))
p2.09.f.AB=sum(as.numeric(p2.09.f$Annl.Biennial))

p3.09.f.C4=sum(as.numeric(p3.09.f$C4))
p3.09.f.C3=sum(as.numeric(p3.09.f$C3))
p3.09.f.Pr=sum(as.numeric(p3.09.f$Perennial))
p3.09.f.AB=sum(as.numeric(p3.09.f$Annl.Biennial))

p4.09.f.C4=sum(as.numeric(p4.09.f$C4))
p4.09.f.C3=sum(as.numeric(p4.09.f$C3))
p4.09.f.Pr=sum(as.numeric(p4.09.f$Perennial))
p4.09.f.AB=sum(as.numeric(p4.09.f$Annl.Biennial))

p5.09.f.C4=sum(as.numeric(p5.09.f$C4))
p5.09.f.C3=sum(as.numeric(p5.09.f$C3))
p5.09.f.Pr=sum(as.numeric(p5.09.f$Perennial))
p5.09.f.AB=sum(as.numeric(p5.09.f$Annl.Biennial))

p6.09.f.C4=sum(as.numeric(p6.09.f$C4))
p6.09.f.C3=sum(as.numeric(p6.09.f$C3))
p6.09.f.Pr=sum(as.numeric(p6.09.f$Perennial))
p6.09.f.AB=sum(as.numeric(p6.09.f$Annl.Biennial))

p7.09.f.C4=sum(as.numeric(p7.09.f$C4))
p7.09.f.C3=sum(as.numeric(p7.09.f$C3))
p7.09.f.Pr=sum(as.numeric(p7.09.f$Perennial))
p7.09.f.AB=sum(as.numeric(p7.09.f$Annl.Biennial))

p8.09.f.C4=sum(as.numeric(p8.09.f$C4))
p8.09.f.C3=sum(as.numeric(p8.09.f$C3))
p8.09.f.Pr=sum(as.numeric(p8.09.f$Perennial))
p8.09.f.AB=sum(as.numeric(p8.09.f$Annl.Biennial))

p9.09.f.C4=sum(as.numeric(p9.09.f$C4))
p9.09.f.C3=sum(as.numeric(p9.09.f$C3))
p9.09.f.Pr=sum(as.numeric(p9.09.f$Perennial))
p9.09.f.AB=sum(as.numeric(p9.09.f$Annl.Biennial))

p10.09.f.C4=sum(as.numeric(p10.09.f$C4))
p10.09.f.C3=sum(as.numeric(p10.09.f$C3))
p10.09.f.Pr=sum(as.numeric(p10.09.f$Perennial))
p10.09.f.AB=sum(as.numeric(p10.09.f$Annl.Biennial))

p11.09.f.C4=sum(as.numeric(p11.09.f$C4))
p11.09.f.C3=sum(as.numeric(p11.09.f$C3))
p11.09.f.Pr=sum(as.numeric(p11.09.f$Perennial))
p11.09.f.AB=sum(as.numeric(p11.09.f$Annl.Biennial))

p12.09.f.C4=sum(as.numeric(p12.09.f$C4))
p12.09.f.C3=sum(as.numeric(p12.09.f$C3))
p12.09.f.Pr=sum(as.numeric(p12.09.f$Perennial))
p12.09.f.AB=sum(as.numeric(p12.09.f$Annl.Biennial))

p13.09.f.C4=sum(as.numeric(p13.09.f$C4))
p13.09.f.C3=sum(as.numeric(p13.09.f$C3))
p13.09.f.Pr=sum(as.numeric(p13.09.f$Perennial))
p13.09.f.AB=sum(as.numeric(p13.09.f$Annl.Biennial))

p14.09.f.C4=sum(as.numeric(p14.09.f$C4))
p14.09.f.C3=sum(as.numeric(p14.09.f$C3))
p14.09.f.Pr=sum(as.numeric(p14.09.f$Perennial))
p14.09.f.AB=sum(as.numeric(p14.09.f$Annl.Biennial))

p15.09.f.C4=sum(as.numeric(p15.09.f$C4))
p15.09.f.C3=sum(as.numeric(p15.09.f$C3))
p15.09.f.Pr=sum(as.numeric(p15.09.f$Perennial))
p15.09.f.AB=sum(as.numeric(p15.09.f$Annl.Biennial))

p16.09.f.C4=sum(as.numeric(p16.09.f$C4))
p16.09.f.C3=sum(as.numeric(p16.09.f$C3))
p16.09.f.Pr=sum(as.numeric(p16.09.f$Perennial))
p16.09.f.AB=sum(as.numeric(p16.09.f$Annl.Biennial))

p17.09.f.C4=sum(as.numeric(p17.09.f$C4))
p17.09.f.C3=sum(as.numeric(p17.09.f$C3))
p17.09.f.Pr=sum(as.numeric(p17.09.f$Perennial))
p17.09.f.AB=sum(as.numeric(p17.09.f$Annl.Biennial))

p18.09.f.C4=sum(as.numeric(p18.09.f$C4))
p18.09.f.C3=sum(as.numeric(p18.09.f$C3))
p18.09.f.Pr=sum(as.numeric(p18.09.f$Perennial))
p18.09.f.AB=sum(as.numeric(p18.09.f$Annl.Biennial))

p19.09.f.C4=sum(as.numeric(p19.09.f$C4))
p19.09.f.C3=sum(as.numeric(p19.09.f$C3))
p19.09.f.Pr=sum(as.numeric(p19.09.f$Perennial))
p19.09.f.AB=sum(as.numeric(p19.09.f$Annl.Biennial))

p20.09.f.C4=sum(as.numeric(p20.09.f$C4))
p20.09.f.C3=sum(as.numeric(p20.09.f$C3))
p20.09.f.Pr=sum(as.numeric(p20.09.f$Perennial))
p20.09.f.AB=sum(as.numeric(p20.09.f$Annl.Biennial))

p21.09.f.C4=sum(as.numeric(p21.09.f$C4))
p21.09.f.C3=sum(as.numeric(p21.09.f$C3))
p21.09.f.Pr=sum(as.numeric(p21.09.f$Perennial))
p21.09.f.AB=sum(as.numeric(p21.09.f$Annl.Biennial))

p22.09.f.C4=sum(as.numeric(p22.09.f$C4))
p22.09.f.C3=sum(as.numeric(p22.09.f$C3))
p22.09.f.Pr=sum(as.numeric(p22.09.f$Perennial))
p22.09.f.AB=sum(as.numeric(p22.09.f$Annl.Biennial))

p23.09.f.C4=sum(as.numeric(p23.09.f$C4))
p23.09.f.C3=sum(as.numeric(p23.09.f$C3))
p23.09.f.Pr=sum(as.numeric(p23.09.f$Perennial))
p23.09.f.AB=sum(as.numeric(p23.09.f$Annl.Biennial))

p24.09.f.C4=sum(as.numeric(p24.09.f$C4))
p24.09.f.C3=sum(as.numeric(p24.09.f$C3))
p24.09.f.Pr=sum(as.numeric(p24.09.f$Perennial))
p24.09.f.AB=sum(as.numeric(p24.09.f$Annl.Biennial))

p25.09.f.C4=sum(as.numeric(p25.09.f$C4))
p25.09.f.C3=sum(as.numeric(p25.09.f$C3))
p25.09.f.Pr=sum(as.numeric(p25.09.f$Perennial))
p25.09.f.AB=sum(as.numeric(p25.09.f$Annl.Biennial))

p26.09.f.C4=sum(as.numeric(p26.09.f$C4))
p26.09.f.C3=sum(as.numeric(p26.09.f$C3))
p26.09.f.Pr=sum(as.numeric(p26.09.f$Perennial))
p26.09.f.AB=sum(as.numeric(p26.09.f$Annl.Biennial))

p27.09.f.C4=sum(as.numeric(p27.09.f$C4))
p27.09.f.C3=sum(as.numeric(p27.09.f$C3))
p27.09.f.Pr=sum(as.numeric(p27.09.f$Perennial))
p27.09.f.AB=sum(as.numeric(p27.09.f$Annl.Biennial))

p28.09.f.C4=sum(as.numeric(p28.09.f$C4))
p28.09.f.C3=sum(as.numeric(p28.09.f$C3))
p28.09.f.Pr=sum(as.numeric(p28.09.f$Perennial))
p28.09.f.AB=sum(as.numeric(p28.09.f$Annl.Biennial))

p29.09.f.C4=sum(as.numeric(p29.09.f$C4))
p29.09.f.C3=sum(as.numeric(p29.09.f$C3))
p29.09.f.Pr=sum(as.numeric(p29.09.f$Perennial))
p29.09.f.AB=sum(as.numeric(p29.09.f$Annl.Biennial))

p30.09.f.C4=sum(as.numeric(p30.09.f$C4))
p30.09.f.C3=sum(as.numeric(p30.09.f$C3))
p30.09.f.Pr=sum(as.numeric(p30.09.f$Perennial))
p30.09.f.AB=sum(as.numeric(p30.09.f$Annl.Biennial))

p31.09.f.C4=sum(as.numeric(p31.09.f$C4))
p31.09.f.C3=sum(as.numeric(p31.09.f$C3))
p31.09.f.Pr=sum(as.numeric(p31.09.f$Perennial))
p31.09.f.AB=sum(as.numeric(p31.09.f$Annl.Biennial))

p32.09.f.C4=sum(as.numeric(p32.09.f$C4))
p32.09.f.C3=sum(as.numeric(p32.09.f$C3))
p32.09.f.Pr=sum(as.numeric(p32.09.f$Perennial))
p32.09.f.AB=sum(as.numeric(p32.09.f$Annl.Biennial))

p33.09.f.C4=sum(as.numeric(p33.09.f$C4))
p33.09.f.C3=sum(as.numeric(p33.09.f$C3))
p33.09.f.Pr=sum(as.numeric(p33.09.f$Perennial))
p33.09.f.AB=sum(as.numeric(p33.09.f$Annl.Biennial))

p34.09.f.C4=sum(as.numeric(p34.09.f$C4))
p34.09.f.C3=sum(as.numeric(p34.09.f$C3))
p34.09.f.Pr=sum(as.numeric(p34.09.f$Perennial))
p34.09.f.AB=sum(as.numeric(p34.09.f$Annl.Biennial))

p35.09.f.C4=sum(as.numeric(p35.09.f$C4))
p35.09.f.C3=sum(as.numeric(p35.09.f$C3))
p35.09.f.Pr=sum(as.numeric(p35.09.f$Perennial))
p35.09.f.AB=sum(as.numeric(p35.09.f$Annl.Biennial))

p36.09.f.C4=sum(as.numeric(p36.09.f$C4))
p36.09.f.C3=sum(as.numeric(p36.09.f$C3))
p36.09.f.Pr=sum(as.numeric(p36.09.f$Perennial))
p36.09.f.AB=sum(as.numeric(p36.09.f$Annl.Biennial))

##########summer
p1.09.s.C4=sum(as.numeric(p1.09.s$C4))
p1.09.s.C3=sum(as.numeric(p1.09.s$C3))
p1.09.s.Pr=sum(as.numeric(p1.09.s$Perennial))
p1.09.s.AB=sum(as.numeric(p1.09.s$Annl.Biennial))

p2.09.s.C4=sum(as.numeric(p2.09.s$C4))
p2.09.s.C3=sum(as.numeric(p2.09.s$C3))
p2.09.s.Pr=sum(as.numeric(p2.09.s$Perennial))
p2.09.s.AB=sum(as.numeric(p2.09.s$Annl.Biennial))

p3.09.s.C4=sum(as.numeric(p3.09.s$C4))
p3.09.s.C3=sum(as.numeric(p3.09.s$C3))
p3.09.s.Pr=sum(as.numeric(p3.09.s$Perennial))
p3.09.s.AB=sum(as.numeric(p3.09.s$Annl.Biennial))

p4.09.s.C4=sum(as.numeric(p4.09.s$C4))
p4.09.s.C3=sum(as.numeric(p4.09.s$C3))
p4.09.s.Pr=sum(as.numeric(p4.09.s$Perennial))
p4.09.s.AB=sum(as.numeric(p4.09.s$Annl.Biennial))

p5.09.s.C4=sum(as.numeric(p5.09.s$C4))
p5.09.s.C3=sum(as.numeric(p5.09.s$C3))
p5.09.s.Pr=sum(as.numeric(p5.09.s$Perennial))
p5.09.s.AB=sum(as.numeric(p5.09.s$Annl.Biennial))

p6.09.s.C4=sum(as.numeric(p6.09.s$C4))
p6.09.s.C3=sum(as.numeric(p6.09.s$C3))
p6.09.s.Pr=sum(as.numeric(p6.09.s$Perennial))
p6.09.s.AB=sum(as.numeric(p6.09.s$Annl.Biennial))

p7.09.s.C4=sum(as.numeric(p7.09.s$C4))
p7.09.s.C3=sum(as.numeric(p7.09.s$C3))
p7.09.s.Pr=sum(as.numeric(p7.09.s$Perennial))
p7.09.s.AB=sum(as.numeric(p7.09.s$Annl.Biennial))

p8.09.s.C4=sum(as.numeric(p8.09.s$C4))
p8.09.s.C3=sum(as.numeric(p8.09.s$C3))
p8.09.s.Pr=sum(as.numeric(p8.09.s$Perennial))
p8.09.s.AB=sum(as.numeric(p8.09.s$Annl.Biennial))

p9.09.s.C4=sum(as.numeric(p9.09.s$C4))
p9.09.s.C3=sum(as.numeric(p9.09.s$C3))
p9.09.s.Pr=sum(as.numeric(p9.09.s$Perennial))
p9.09.s.AB=sum(as.numeric(p9.09.s$Annl.Biennial))

p10.09.s.C4=sum(as.numeric(p10.09.s$C4))
p10.09.s.C3=sum(as.numeric(p10.09.s$C3))
p10.09.s.Pr=sum(as.numeric(p10.09.s$Perennial))
p10.09.s.AB=sum(as.numeric(p10.09.s$Annl.Biennial))

p11.09.s.C4=sum(as.numeric(p11.09.s$C4))
p11.09.s.C3=sum(as.numeric(p11.09.s$C3))
p11.09.s.Pr=sum(as.numeric(p11.09.s$Perennial))
p11.09.s.AB=sum(as.numeric(p11.09.s$Annl.Biennial))

p12.09.s.C4=sum(as.numeric(p12.09.s$C4))
p12.09.s.C3=sum(as.numeric(p12.09.s$C3))
p12.09.s.Pr=sum(as.numeric(p12.09.s$Perennial))
p12.09.s.AB=sum(as.numeric(p12.09.s$Annl.Biennial))

p13.09.s.C4=sum(as.numeric(p13.09.s$C4))
p13.09.s.C3=sum(as.numeric(p13.09.s$C3))
p13.09.s.Pr=sum(as.numeric(p13.09.s$Perennial))
p13.09.s.AB=sum(as.numeric(p13.09.s$Annl.Biennial))

p14.09.s.C4=sum(as.numeric(p14.09.s$C4))
p14.09.s.C3=sum(as.numeric(p14.09.s$C3))
p14.09.s.Pr=sum(as.numeric(p14.09.s$Perennial))
p14.09.s.AB=sum(as.numeric(p14.09.s$Annl.Biennial))

p15.09.s.C4=sum(as.numeric(p15.09.s$C4))
p15.09.s.C3=sum(as.numeric(p15.09.s$C3))
p15.09.s.Pr=sum(as.numeric(p15.09.s$Perennial))
p15.09.s.AB=sum(as.numeric(p15.09.s$Annl.Biennial))

p16.09.s.C4=sum(as.numeric(p16.09.s$C4))
p16.09.s.C3=sum(as.numeric(p16.09.s$C3))
p16.09.s.Pr=sum(as.numeric(p16.09.s$Perennial))
p16.09.s.AB=sum(as.numeric(p16.09.s$Annl.Biennial))

p17.09.s.C4=sum(as.numeric(p17.09.s$C4))
p17.09.s.C3=sum(as.numeric(p17.09.s$C3))
p17.09.s.Pr=sum(as.numeric(p17.09.s$Perennial))
p17.09.s.AB=sum(as.numeric(p17.09.s$Annl.Biennial))

p18.09.s.C4=sum(as.numeric(p18.09.s$C4))
p18.09.s.C3=sum(as.numeric(p18.09.s$C3))
p18.09.s.Pr=sum(as.numeric(p18.09.s$Perennial))
p18.09.s.AB=sum(as.numeric(p18.09.s$Annl.Biennial))

p19.09.s.C4=sum(as.numeric(p19.09.s$C4))
p19.09.s.C3=sum(as.numeric(p19.09.s$C3))
p19.09.s.Pr=sum(as.numeric(p19.09.s$Perennial))
p19.09.s.AB=sum(as.numeric(p19.09.s$Annl.Biennial))

p20.09.s.C4=sum(as.numeric(p20.09.s$C4))
p20.09.s.C3=sum(as.numeric(p20.09.s$C3))
p20.09.s.Pr=sum(as.numeric(p20.09.s$Perennial))
p20.09.s.AB=sum(as.numeric(p20.09.s$Annl.Biennial))

p21.09.s.C4=sum(as.numeric(p21.09.s$C4))
p21.09.s.C3=sum(as.numeric(p21.09.s$C3))
p21.09.s.Pr=sum(as.numeric(p21.09.s$Perennial))
p21.09.s.AB=sum(as.numeric(p21.09.s$Annl.Biennial))

p22.09.s.C4=sum(as.numeric(p22.09.s$C4))
p22.09.s.C3=sum(as.numeric(p22.09.s$C3))
p22.09.s.Pr=sum(as.numeric(p22.09.s$Perennial))
p22.09.s.AB=sum(as.numeric(p22.09.s$Annl.Biennial))

p23.09.s.C4=sum(as.numeric(p23.09.s$C4))
p23.09.s.C3=sum(as.numeric(p23.09.s$C3))
p23.09.s.Pr=sum(as.numeric(p23.09.s$Perennial))
p23.09.s.AB=sum(as.numeric(p23.09.s$Annl.Biennial))

p24.09.s.C4=sum(as.numeric(p24.09.s$C4))
p24.09.s.C3=sum(as.numeric(p24.09.s$C3))
p24.09.s.Pr=sum(as.numeric(p24.09.s$Perennial))
p24.09.s.AB=sum(as.numeric(p24.09.s$Annl.Biennial))

p25.09.s.C4=sum(as.numeric(p25.09.s$C4))
p25.09.s.C3=sum(as.numeric(p25.09.s$C3))
p25.09.s.Pr=sum(as.numeric(p25.09.s$Perennial))
p25.09.s.AB=sum(as.numeric(p25.09.s$Annl.Biennial))

p26.09.s.C4=sum(as.numeric(p26.09.s$C4))
p26.09.s.C3=sum(as.numeric(p26.09.s$C3))
p26.09.s.Pr=sum(as.numeric(p26.09.s$Perennial))
p26.09.s.AB=sum(as.numeric(p26.09.s$Annl.Biennial))

p27.09.s.C4=sum(as.numeric(p27.09.s$C4))
p27.09.s.C3=sum(as.numeric(p27.09.s$C3))
p27.09.s.Pr=sum(as.numeric(p27.09.s$Perennial))
p27.09.s.AB=sum(as.numeric(p27.09.s$Annl.Biennial))

p28.09.s.C4=sum(as.numeric(p28.09.s$C4))
p28.09.s.C3=sum(as.numeric(p28.09.s$C3))
p28.09.s.Pr=sum(as.numeric(p28.09.s$Perennial))
p28.09.s.AB=sum(as.numeric(p28.09.s$Annl.Biennial))

p29.09.s.C4=sum(as.numeric(p29.09.s$C4))
p29.09.s.C3=sum(as.numeric(p29.09.s$C3))
p29.09.s.Pr=sum(as.numeric(p29.09.s$Perennial))
p29.09.s.AB=sum(as.numeric(p29.09.s$Annl.Biennial))

p30.09.s.C4=sum(as.numeric(p30.09.s$C4))
p30.09.s.C3=sum(as.numeric(p30.09.s$C3))
p30.09.s.Pr=sum(as.numeric(p30.09.s$Perennial))
p30.09.s.AB=sum(as.numeric(p30.09.s$Annl.Biennial))

p31.09.s.C4=sum(as.numeric(p31.09.s$C4))
p31.09.s.C3=sum(as.numeric(p31.09.s$C3))
p31.09.s.Pr=sum(as.numeric(p31.09.s$Perennial))
p31.09.s.AB=sum(as.numeric(p31.09.s$Annl.Biennial))

p32.09.s.C4=sum(as.numeric(p32.09.s$C4))
p32.09.s.C3=sum(as.numeric(p32.09.s$C3))
p32.09.s.Pr=sum(as.numeric(p32.09.s$Perennial))
p32.09.s.AB=sum(as.numeric(p32.09.s$Annl.Biennial))

p33.09.s.C4=sum(as.numeric(p33.09.s$C4))
p33.09.s.C3=sum(as.numeric(p33.09.s$C3))
p33.09.s.Pr=sum(as.numeric(p33.09.s$Perennial))
p33.09.s.AB=sum(as.numeric(p33.09.s$Annl.Biennial))

p34.09.s.C4=sum(as.numeric(p34.09.s$C4))
p34.09.s.C3=sum(as.numeric(p34.09.s$C3))
p34.09.s.Pr=sum(as.numeric(p34.09.s$Perennial))
p34.09.s.AB=sum(as.numeric(p34.09.s$Annl.Biennial))

p35.09.s.C4=sum(as.numeric(p35.09.s$C4))
p35.09.s.C3=sum(as.numeric(p35.09.s$C3))
p35.09.s.Pr=sum(as.numeric(p35.09.s$Perennial))
p35.09.s.AB=sum(as.numeric(p35.09.s$Annl.Biennial))

p36.09.s.C4=sum(as.numeric(p36.09.s$C4))
p36.09.s.C3=sum(as.numeric(p36.09.s$C3))
p36.09.s.Pr=sum(as.numeric(p36.09.s$Perennial))
p36.09.s.AB=sum(as.numeric(p36.09.s$Annl.Biennial))

```

#2010
```{r}

#Use column/row of NA's for Fall2010
na.vec= c(NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,NA)

#summer
p1.10.s.C4=sum(as.numeric(p1.10.s$C4))
p1.10.s.C3=sum(as.numeric(p1.10.s$C3))
p1.10.s.Pr=sum(as.numeric(p1.10.s$Perennial))
p1.10.s.AB=sum(as.numeric(p1.10.s$Annl.Biennial))

p2.10.s.C4=sum(as.numeric(p2.10.s$C4))
p2.10.s.C3=sum(as.numeric(p2.10.s$C3))
p2.10.s.Pr=sum(as.numeric(p2.10.s$Perennial))
p2.10.s.AB=sum(as.numeric(p2.10.s$Annl.Biennial))

p3.10.s.C4=sum(as.numeric(p3.10.s$C4))
p3.10.s.C3=sum(as.numeric(p3.10.s$C3))
p3.10.s.Pr=sum(as.numeric(p3.10.s$Perennial))
p3.10.s.AB=sum(as.numeric(p3.10.s$Annl.Biennial))

p4.10.s.C4=sum(as.numeric(p4.10.s$C4))
p4.10.s.C3=sum(as.numeric(p4.10.s$C3))
p4.10.s.Pr=sum(as.numeric(p4.10.s$Perennial))
p4.10.s.AB=sum(as.numeric(p4.10.s$Annl.Biennial))

p5.10.s.C4=sum(as.numeric(p5.10.s$C4))
p5.10.s.C3=sum(as.numeric(p5.10.s$C3))
p5.10.s.Pr=sum(as.numeric(p5.10.s$Perennial))
p5.10.s.AB=sum(as.numeric(p5.10.s$Annl.Biennial))

p6.10.s.C4=sum(as.numeric(p6.10.s$C4))
p6.10.s.C3=sum(as.numeric(p6.10.s$C3))
p6.10.s.Pr=sum(as.numeric(p6.10.s$Perennial))
p6.10.s.AB=sum(as.numeric(p6.10.s$Annl.Biennial))

p7.10.s.C4=sum(as.numeric(p7.10.s$C4))
p7.10.s.C3=sum(as.numeric(p7.10.s$C3))
p7.10.s.Pr=sum(as.numeric(p7.10.s$Perennial))
p7.10.s.AB=sum(as.numeric(p7.10.s$Annl.Biennial))

p8.10.s.C4=sum(as.numeric(p8.10.s$C4))
p8.10.s.C3=sum(as.numeric(p8.10.s$C3))
p8.10.s.Pr=sum(as.numeric(p8.10.s$Perennial))
p8.10.s.AB=sum(as.numeric(p8.10.s$Annl.Biennial))

p9.10.s.C4=sum(as.numeric(p9.10.s$C4))
p9.10.s.C3=sum(as.numeric(p9.10.s$C3))
p9.10.s.Pr=sum(as.numeric(p9.10.s$Perennial))
p9.10.s.AB=sum(as.numeric(p9.10.s$Annl.Biennial))

p10.10.s.C4=sum(as.numeric(p10.10.s$C4))
p10.10.s.C3=sum(as.numeric(p10.10.s$C3))
p10.10.s.Pr=sum(as.numeric(p10.10.s$Perennial))
p10.10.s.AB=sum(as.numeric(p10.10.s$Annl.Biennial))

p11.10.s.C4=sum(as.numeric(p11.10.s$C4))
p11.10.s.C3=sum(as.numeric(p11.10.s$C3))
p11.10.s.Pr=sum(as.numeric(p11.10.s$Perennial))
p11.10.s.AB=sum(as.numeric(p11.10.s$Annl.Biennial))

p12.10.s.C4=sum(as.numeric(p12.10.s$C4))
p12.10.s.C3=sum(as.numeric(p12.10.s$C3))
p12.10.s.Pr=sum(as.numeric(p12.10.s$Perennial))
p12.10.s.AB=sum(as.numeric(p12.10.s$Annl.Biennial))

p13.10.s.C4=sum(as.numeric(p13.10.s$C4))
p13.10.s.C3=sum(as.numeric(p13.10.s$C3))
p13.10.s.Pr=sum(as.numeric(p13.10.s$Perennial))
p13.10.s.AB=sum(as.numeric(p13.10.s$Annl.Biennial))

p14.10.s.C4=sum(as.numeric(p14.10.s$C4))
p14.10.s.C3=sum(as.numeric(p14.10.s$C3))
p14.10.s.Pr=sum(as.numeric(p14.10.s$Perennial))
p14.10.s.AB=sum(as.numeric(p14.10.s$Annl.Biennial))

p15.10.s.C4=sum(as.numeric(p15.10.s$C4))
p15.10.s.C3=sum(as.numeric(p15.10.s$C3))
p15.10.s.Pr=sum(as.numeric(p15.10.s$Perennial))
p15.10.s.AB=sum(as.numeric(p15.10.s$Annl.Biennial))

p16.10.s.C4=sum(as.numeric(p16.10.s$C4))
p16.10.s.C3=sum(as.numeric(p16.10.s$C3))
p16.10.s.Pr=sum(as.numeric(p16.10.s$Perennial))
p16.10.s.AB=sum(as.numeric(p16.10.s$Annl.Biennial))

p17.10.s.C4=sum(as.numeric(p17.10.s$C4))
p17.10.s.C3=sum(as.numeric(p17.10.s$C3))
p17.10.s.Pr=sum(as.numeric(p17.10.s$Perennial))
p17.10.s.AB=sum(as.numeric(p17.10.s$Annl.Biennial))

p18.10.s.C4=sum(as.numeric(p18.10.s$C4))
p18.10.s.C3=sum(as.numeric(p18.10.s$C3))
p18.10.s.Pr=sum(as.numeric(p18.10.s$Perennial))
p18.10.s.AB=sum(as.numeric(p18.10.s$Annl.Biennial))

p19.10.s.C4=sum(as.numeric(p19.10.s$C4))
p19.10.s.C3=sum(as.numeric(p19.10.s$C3))
p19.10.s.Pr=sum(as.numeric(p19.10.s$Perennial))
p19.10.s.AB=sum(as.numeric(p19.10.s$Annl.Biennial))

p20.10.s.C4=sum(as.numeric(p20.10.s$C4))
p20.10.s.C3=sum(as.numeric(p20.10.s$C3))
p20.10.s.Pr=sum(as.numeric(p20.10.s$Perennial))
p20.10.s.AB=sum(as.numeric(p20.10.s$Annl.Biennial))

p21.10.s.C4=sum(as.numeric(p21.10.s$C4))
p21.10.s.C3=sum(as.numeric(p21.10.s$C3))
p21.10.s.Pr=sum(as.numeric(p21.10.s$Perennial))
p21.10.s.AB=sum(as.numeric(p21.10.s$Annl.Biennial))

p22.10.s.C4=sum(as.numeric(p22.10.s$C4))
p22.10.s.C3=sum(as.numeric(p22.10.s$C3))
p22.10.s.Pr=sum(as.numeric(p22.10.s$Perennial))
p22.10.s.AB=sum(as.numeric(p22.10.s$Annl.Biennial))

p23.10.s.C4=sum(as.numeric(p23.10.s$C4))
p23.10.s.C3=sum(as.numeric(p23.10.s$C3))
p23.10.s.Pr=sum(as.numeric(p23.10.s$Perennial))
p23.10.s.AB=sum(as.numeric(p23.10.s$Annl.Biennial))

p24.10.s.C4=sum(as.numeric(p24.10.s$C4))
p24.10.s.C3=sum(as.numeric(p24.10.s$C3))
p24.10.s.Pr=sum(as.numeric(p24.10.s$Perennial))
p24.10.s.AB=sum(as.numeric(p24.10.s$Annl.Biennial))

p25.10.s.C4=sum(as.numeric(p25.10.s$C4))
p25.10.s.C3=sum(as.numeric(p25.10.s$C3))
p25.10.s.Pr=sum(as.numeric(p25.10.s$Perennial))
p25.10.s.AB=sum(as.numeric(p25.10.s$Annl.Biennial))

p26.10.s.C4=sum(as.numeric(p26.10.s$C4))
p26.10.s.C3=sum(as.numeric(p26.10.s$C3))
p26.10.s.Pr=sum(as.numeric(p26.10.s$Perennial))
p26.10.s.AB=sum(as.numeric(p26.10.s$Annl.Biennial))

p27.10.s.C4=sum(as.numeric(p27.10.s$C4))
p27.10.s.C3=sum(as.numeric(p27.10.s$C3))
p27.10.s.Pr=sum(as.numeric(p27.10.s$Perennial))
p27.10.s.AB=sum(as.numeric(p27.10.s$Annl.Biennial))

p28.10.s.C4=sum(as.numeric(p28.10.s$C4))
p28.10.s.C3=sum(as.numeric(p28.10.s$C3))
p28.10.s.Pr=sum(as.numeric(p28.10.s$Perennial))
p28.10.s.AB=sum(as.numeric(p28.10.s$Annl.Biennial))

p29.10.s.C4=sum(as.numeric(p29.10.s$C4))
p29.10.s.C3=sum(as.numeric(p29.10.s$C3))
p29.10.s.Pr=sum(as.numeric(p29.10.s$Perennial))
p29.10.s.AB=sum(as.numeric(p29.10.s$Annl.Biennial))

p30.10.s.C4=sum(as.numeric(p30.10.s$C4))
p30.10.s.C3=sum(as.numeric(p30.10.s$C3))
p30.10.s.Pr=sum(as.numeric(p30.10.s$Perennial))
p30.10.s.AB=sum(as.numeric(p30.10.s$Annl.Biennial))

p31.10.s.C4=sum(as.numeric(p31.10.s$C4))
p31.10.s.C3=sum(as.numeric(p31.10.s$C3))
p31.10.s.Pr=sum(as.numeric(p31.10.s$Perennial))
p31.10.s.AB=sum(as.numeric(p31.10.s$Annl.Biennial))

p32.10.s.C4=sum(as.numeric(p32.10.s$C4))
p32.10.s.C3=sum(as.numeric(p32.10.s$C3))
p32.10.s.Pr=sum(as.numeric(p32.10.s$Perennial))
p32.10.s.AB=sum(as.numeric(p32.10.s$Annl.Biennial))

p33.10.s.C4=sum(as.numeric(p33.10.s$C4))
p33.10.s.C3=sum(as.numeric(p33.10.s$C3))
p33.10.s.Pr=sum(as.numeric(p33.10.s$Perennial))
p33.10.s.AB=sum(as.numeric(p33.10.s$Annl.Biennial))

p34.10.s.C4=sum(as.numeric(p34.10.s$C4))
p34.10.s.C3=sum(as.numeric(p34.10.s$C3))
p34.10.s.Pr=sum(as.numeric(p34.10.s$Perennial))
p34.10.s.AB=sum(as.numeric(p34.10.s$Annl.Biennial))

p35.10.s.C4=sum(as.numeric(p35.10.s$C4))
p35.10.s.C3=sum(as.numeric(p35.10.s$C3))
p35.10.s.Pr=sum(as.numeric(p35.10.s$Perennial))
p35.10.s.AB=sum(as.numeric(p35.10.s$Annl.Biennial))

p36.10.s.C4=sum(as.numeric(p36.10.s$C4))
p36.10.s.C3=sum(as.numeric(p36.10.s$C3))
p36.10.s.Pr=sum(as.numeric(p36.10.s$Perennial))
p36.10.s.AB=sum(as.numeric(p36.10.s$Annl.Biennial))

```

#2011
```{r}
p1.11.f.C4=sum(as.numeric(p1.11.f$C4))
p1.11.f.C3=sum(as.numeric(p1.11.f$C3))
p1.11.f.Pr=sum(as.numeric(p1.11.f$Perennial))
p1.11.f.AB=sum(as.numeric(p1.11.f$Annl.Biennial))

p2.11.f.C4=sum(as.numeric(p2.11.f$C4))
p2.11.f.C3=sum(as.numeric(p2.11.f$C3))
p2.11.f.Pr=sum(as.numeric(p2.11.f$Perennial))
p2.11.f.AB=sum(as.numeric(p2.11.f$Annl.Biennial))

p3.11.f.C4=sum(as.numeric(p3.11.f$C4))
p3.11.f.C3=sum(as.numeric(p3.11.f$C3))
p3.11.f.Pr=sum(as.numeric(p3.11.f$Perennial))
p3.11.f.AB=sum(as.numeric(p3.11.f$Annl.Biennial))

p4.11.f.C4=sum(as.numeric(p4.11.f$C4))
p4.11.f.C3=sum(as.numeric(p4.11.f$C3))
p4.11.f.Pr=sum(as.numeric(p4.11.f$Perennial))
p4.11.f.AB=sum(as.numeric(p4.11.f$Annl.Biennial))

p5.11.f.C4=sum(as.numeric(p5.11.f$C4))
p5.11.f.C3=sum(as.numeric(p5.11.f$C3))
p5.11.f.Pr=sum(as.numeric(p5.11.f$Perennial))
p5.11.f.AB=sum(as.numeric(p5.11.f$Annl.Biennial))

p6.11.f.C4=sum(as.numeric(p6.11.f$C4))
p6.11.f.C3=sum(as.numeric(p6.11.f$C3))
p6.11.f.Pr=sum(as.numeric(p6.11.f$Perennial))
p6.11.f.AB=sum(as.numeric(p6.11.f$Annl.Biennial))

p7.11.f.C4=sum(as.numeric(p7.11.f$C4))
p7.11.f.C3=sum(as.numeric(p7.11.f$C3))
p7.11.f.Pr=sum(as.numeric(p7.11.f$Perennial))
p7.11.f.AB=sum(as.numeric(p7.11.f$Annl.Biennial))

p8.11.f.C4=sum(as.numeric(p8.11.f$C4))
p8.11.f.C3=sum(as.numeric(p8.11.f$C3))
p8.11.f.Pr=sum(as.numeric(p8.11.f$Perennial))
p8.11.f.AB=sum(as.numeric(p8.11.f$Annl.Biennial))

p9.11.f.C4=sum(as.numeric(p9.11.f$C4))
p9.11.f.C3=sum(as.numeric(p9.11.f$C3))
p9.11.f.Pr=sum(as.numeric(p9.11.f$Perennial))
p9.11.f.AB=sum(as.numeric(p9.11.f$Annl.Biennial))

p10.11.f.C4=sum(as.numeric(p10.11.f$C4))
p10.11.f.C3=sum(as.numeric(p10.11.f$C3))
p10.11.f.Pr=sum(as.numeric(p10.11.f$Perennial))
p10.11.f.AB=sum(as.numeric(p10.11.f$Annl.Biennial))

p11.11.f.C4=sum(as.numeric(p11.11.f$C4))
p11.11.f.C3=sum(as.numeric(p11.11.f$C3))
p11.11.f.Pr=sum(as.numeric(p11.11.f$Perennial))
p11.11.f.AB=sum(as.numeric(p11.11.f$Annl.Biennial))

p12.11.f.C4=sum(as.numeric(p12.11.f$C4))
p12.11.f.C3=sum(as.numeric(p12.11.f$C3))
p12.11.f.Pr=sum(as.numeric(p12.11.f$Perennial))
p12.11.f.AB=sum(as.numeric(p12.11.f$Annl.Biennial))

p13.11.f.C4=sum(as.numeric(p13.11.f$C4))
p13.11.f.C3=sum(as.numeric(p13.11.f$C3))
p13.11.f.Pr=sum(as.numeric(p13.11.f$Perennial))
p13.11.f.AB=sum(as.numeric(p13.11.f$Annl.Biennial))

p14.11.f.C4=sum(as.numeric(p14.11.f$C4))
p14.11.f.C3=sum(as.numeric(p14.11.f$C3))
p14.11.f.Pr=sum(as.numeric(p14.11.f$Perennial))
p14.11.f.AB=sum(as.numeric(p14.11.f$Annl.Biennial))

p15.11.f.C4=sum(as.numeric(p15.11.f$C4))
p15.11.f.C3=sum(as.numeric(p15.11.f$C3))
p15.11.f.Pr=sum(as.numeric(p15.11.f$Perennial))
p15.11.f.AB=sum(as.numeric(p15.11.f$Annl.Biennial))

p16.11.f.C4=sum(as.numeric(p16.11.f$C4))
p16.11.f.C3=sum(as.numeric(p16.11.f$C3))
p16.11.f.Pr=sum(as.numeric(p16.11.f$Perennial))
p16.11.f.AB=sum(as.numeric(p16.11.f$Annl.Biennial))

p17.11.f.C4=sum(as.numeric(p17.11.f$C4))
p17.11.f.C3=sum(as.numeric(p17.11.f$C3))
p17.11.f.Pr=sum(as.numeric(p17.11.f$Perennial))
p17.11.f.AB=sum(as.numeric(p17.11.f$Annl.Biennial))

p18.11.f.C4=sum(as.numeric(p18.11.f$C4))
p18.11.f.C3=sum(as.numeric(p18.11.f$C3))
p18.11.f.Pr=sum(as.numeric(p18.11.f$Perennial))
p18.11.f.AB=sum(as.numeric(p18.11.f$Annl.Biennial))

p19.11.f.C4=sum(as.numeric(p19.11.f$C4))
p19.11.f.C3=sum(as.numeric(p19.11.f$C3))
p19.11.f.Pr=sum(as.numeric(p19.11.f$Perennial))
p19.11.f.AB=sum(as.numeric(p19.11.f$Annl.Biennial))

p20.11.f.C4=sum(as.numeric(p20.11.f$C4))
p20.11.f.C3=sum(as.numeric(p20.11.f$C3))
p20.11.f.Pr=sum(as.numeric(p20.11.f$Perennial))
p20.11.f.AB=sum(as.numeric(p20.11.f$Annl.Biennial))

p21.11.f.C4=sum(as.numeric(p21.11.f$C4))
p21.11.f.C3=sum(as.numeric(p21.11.f$C3))
p21.11.f.Pr=sum(as.numeric(p21.11.f$Perennial))
p21.11.f.AB=sum(as.numeric(p21.11.f$Annl.Biennial))

p22.11.f.C4=sum(as.numeric(p22.11.f$C4))
p22.11.f.C3=sum(as.numeric(p22.11.f$C3))
p22.11.f.Pr=sum(as.numeric(p22.11.f$Perennial))
p22.11.f.AB=sum(as.numeric(p22.11.f$Annl.Biennial))

p23.11.f.C4=sum(as.numeric(p23.11.f$C4))
p23.11.f.C3=sum(as.numeric(p23.11.f$C3))
p23.11.f.Pr=sum(as.numeric(p23.11.f$Perennial))
p23.11.f.AB=sum(as.numeric(p23.11.f$Annl.Biennial))

p24.11.f.C4=sum(as.numeric(p24.11.f$C4))
p24.11.f.C3=sum(as.numeric(p24.11.f$C3))
p24.11.f.Pr=sum(as.numeric(p24.11.f$Perennial))
p24.11.f.AB=sum(as.numeric(p24.11.f$Annl.Biennial))

p25.11.f.C4=sum(as.numeric(p25.11.f$C4))
p25.11.f.C3=sum(as.numeric(p25.11.f$C3))
p25.11.f.Pr=sum(as.numeric(p25.11.f$Perennial))
p25.11.f.AB=sum(as.numeric(p25.11.f$Annl.Biennial))

p26.11.f.C4=sum(as.numeric(p26.11.f$C4))
p26.11.f.C3=sum(as.numeric(p26.11.f$C3))
p26.11.f.Pr=sum(as.numeric(p26.11.f$Perennial))
p26.11.f.AB=sum(as.numeric(p26.11.f$Annl.Biennial))

p27.11.f.C4=sum(as.numeric(p27.11.f$C4))
p27.11.f.C3=sum(as.numeric(p27.11.f$C3))
p27.11.f.Pr=sum(as.numeric(p27.11.f$Perennial))
p27.11.f.AB=sum(as.numeric(p27.11.f$Annl.Biennial))

p28.11.f.C4=sum(as.numeric(p28.11.f$C4))
p28.11.f.C3=sum(as.numeric(p28.11.f$C3))
p28.11.f.Pr=sum(as.numeric(p28.11.f$Perennial))
p28.11.f.AB=sum(as.numeric(p28.11.f$Annl.Biennial))

p29.11.f.C4=sum(as.numeric(p29.11.f$C4))
p29.11.f.C3=sum(as.numeric(p29.11.f$C3))
p29.11.f.Pr=sum(as.numeric(p29.11.f$Perennial))
p29.11.f.AB=sum(as.numeric(p29.11.f$Annl.Biennial))

p30.11.f.C4=sum(as.numeric(p30.11.f$C4))
p30.11.f.C3=sum(as.numeric(p30.11.f$C3))
p30.11.f.Pr=sum(as.numeric(p30.11.f$Perennial))
p30.11.f.AB=sum(as.numeric(p30.11.f$Annl.Biennial))

p31.11.f.C4=sum(as.numeric(p31.11.f$C4))
p31.11.f.C3=sum(as.numeric(p31.11.f$C3))
p31.11.f.Pr=sum(as.numeric(p31.11.f$Perennial))
p31.11.f.AB=sum(as.numeric(p31.11.f$Annl.Biennial))

p32.11.f.C4=sum(as.numeric(p32.11.f$C4))
p32.11.f.C3=sum(as.numeric(p32.11.f$C3))
p32.11.f.Pr=sum(as.numeric(p32.11.f$Perennial))
p32.11.f.AB=sum(as.numeric(p32.11.f$Annl.Biennial))

p33.11.f.C4=sum(as.numeric(p33.11.f$C4))
p33.11.f.C3=sum(as.numeric(p33.11.f$C3))
p33.11.f.Pr=sum(as.numeric(p33.11.f$Perennial))
p33.11.f.AB=sum(as.numeric(p33.11.f$Annl.Biennial))

p34.11.f.C4=sum(as.numeric(p34.11.f$C4))
p34.11.f.C3=sum(as.numeric(p34.11.f$C3))
p34.11.f.Pr=sum(as.numeric(p34.11.f$Perennial))
p34.11.f.AB=sum(as.numeric(p34.11.f$Annl.Biennial))

p35.11.f.C4=sum(as.numeric(p35.11.f$C4))
p35.11.f.C3=sum(as.numeric(p35.11.f$C3))
p35.11.f.Pr=sum(as.numeric(p35.11.f$Perennial))
p35.11.f.AB=sum(as.numeric(p35.11.f$Annl.Biennial))

p36.11.f.C4=sum(as.numeric(p36.11.f$C4))
p36.11.f.C3=sum(as.numeric(p36.11.f$C3))
p36.11.f.Pr=sum(as.numeric(p36.11.f$Perennial))
p36.11.f.AB=sum(as.numeric(p36.11.f$Annl.Biennial))

#summer
p1.11.s.C4=sum(as.numeric(p1.11.s$C4))
p1.11.s.C3=sum(as.numeric(p1.11.s$C3))
p1.11.s.Pr=sum(as.numeric(p1.11.s$Perennial))
p1.11.s.AB=sum(as.numeric(p1.11.s$Annl.Biennial))

p2.11.s.C4=sum(as.numeric(p2.11.s$C4))
p2.11.s.C3=sum(as.numeric(p2.11.s$C3))
p2.11.s.Pr=sum(as.numeric(p2.11.s$Perennial))
p2.11.s.AB=sum(as.numeric(p2.11.s$Annl.Biennial))

p3.11.s.C4=sum(as.numeric(p3.11.s$C4))
p3.11.s.C3=sum(as.numeric(p3.11.s$C3))
p3.11.s.Pr=sum(as.numeric(p3.11.s$Perennial))
p3.11.s.AB=sum(as.numeric(p3.11.s$Annl.Biennial))

p4.11.s.C4=sum(as.numeric(p4.11.s$C4))
p4.11.s.C3=sum(as.numeric(p4.11.s$C3))
p4.11.s.Pr=sum(as.numeric(p4.11.s$Perennial))
p4.11.s.AB=sum(as.numeric(p4.11.s$Annl.Biennial))

p5.11.s.C4=sum(as.numeric(p5.11.s$C4))
p5.11.s.C3=sum(as.numeric(p5.11.s$C3))
p5.11.s.Pr=sum(as.numeric(p5.11.s$Perennial))
p5.11.s.AB=sum(as.numeric(p5.11.s$Annl.Biennial))

p6.11.s.C4=sum(as.numeric(p6.11.s$C4))
p6.11.s.C3=sum(as.numeric(p6.11.s$C3))
p6.11.s.Pr=sum(as.numeric(p6.11.s$Perennial))
p6.11.s.AB=sum(as.numeric(p6.11.s$Annl.Biennial))

p7.11.s.C4=sum(as.numeric(p7.11.s$C4))
p7.11.s.C3=sum(as.numeric(p7.11.s$C3))
p7.11.s.Pr=sum(as.numeric(p7.11.s$Perennial))
p7.11.s.AB=sum(as.numeric(p7.11.s$Annl.Biennial))

p8.11.s.C4=sum(as.numeric(p8.11.s$C4))
p8.11.s.C3=sum(as.numeric(p8.11.s$C3))
p8.11.s.Pr=sum(as.numeric(p8.11.s$Perennial))
p8.11.s.AB=sum(as.numeric(p8.11.s$Annl.Biennial))

p9.11.s.C4=sum(as.numeric(p9.11.s$C4))
p9.11.s.C3=sum(as.numeric(p9.11.s$C3))
p9.11.s.Pr=sum(as.numeric(p9.11.s$Perennial))
p9.11.s.AB=sum(as.numeric(p9.11.s$Annl.Biennial))

p10.11.s.C4=sum(as.numeric(p10.11.s$C4))
p10.11.s.C3=sum(as.numeric(p10.11.s$C3))
p10.11.s.Pr=sum(as.numeric(p10.11.s$Perennial))
p10.11.s.AB=sum(as.numeric(p10.11.s$Annl.Biennial))

p11.11.s.C4=sum(as.numeric(p11.11.s$C4))
p11.11.s.C3=sum(as.numeric(p11.11.s$C3))
p11.11.s.Pr=sum(as.numeric(p11.11.s$Perennial))
p11.11.s.AB=sum(as.numeric(p11.11.s$Annl.Biennial))

p12.11.s.C4=sum(as.numeric(p12.11.s$C4))
p12.11.s.C3=sum(as.numeric(p12.11.s$C3))
p12.11.s.Pr=sum(as.numeric(p12.11.s$Perennial))
p12.11.s.AB=sum(as.numeric(p12.11.s$Annl.Biennial))

p13.11.s.C4=sum(as.numeric(p13.11.s$C4))
p13.11.s.C3=sum(as.numeric(p13.11.s$C3))
p13.11.s.Pr=sum(as.numeric(p13.11.s$Perennial))
p13.11.s.AB=sum(as.numeric(p13.11.s$Annl.Biennial))

p14.11.s.C4=sum(as.numeric(p14.11.s$C4))
p14.11.s.C3=sum(as.numeric(p14.11.s$C3))
p14.11.s.Pr=sum(as.numeric(p14.11.s$Perennial))
p14.11.s.AB=sum(as.numeric(p14.11.s$Annl.Biennial))

p15.11.s.C4=sum(as.numeric(p15.11.s$C4))
p15.11.s.C3=sum(as.numeric(p15.11.s$C3))
p15.11.s.Pr=sum(as.numeric(p15.11.s$Perennial))
p15.11.s.AB=sum(as.numeric(p15.11.s$Annl.Biennial))

p16.11.s.C4=sum(as.numeric(p16.11.s$C4))
p16.11.s.C3=sum(as.numeric(p16.11.s$C3))
p16.11.s.Pr=sum(as.numeric(p16.11.s$Perennial))
p16.11.s.AB=sum(as.numeric(p16.11.s$Annl.Biennial))

p17.11.s.C4=sum(as.numeric(p17.11.s$C4))
p17.11.s.C3=sum(as.numeric(p17.11.s$C3))
p17.11.s.Pr=sum(as.numeric(p17.11.s$Perennial))
p17.11.s.AB=sum(as.numeric(p17.11.s$Annl.Biennial))

p18.11.s.C4=sum(as.numeric(p18.11.s$C4))
p18.11.s.C3=sum(as.numeric(p18.11.s$C3))
p18.11.s.Pr=sum(as.numeric(p18.11.s$Perennial))
p18.11.s.AB=sum(as.numeric(p18.11.s$Annl.Biennial))

p19.11.s.C4=sum(as.numeric(p19.11.s$C4))
p19.11.s.C3=sum(as.numeric(p19.11.s$C3))
p19.11.s.Pr=sum(as.numeric(p19.11.s$Perennial))
p19.11.s.AB=sum(as.numeric(p19.11.s$Annl.Biennial))

p20.11.s.C4=sum(as.numeric(p20.11.s$C4))
p20.11.s.C3=sum(as.numeric(p20.11.s$C3))
p20.11.s.Pr=sum(as.numeric(p20.11.s$Perennial))
p20.11.s.AB=sum(as.numeric(p20.11.s$Annl.Biennial))

p21.11.s.C4=sum(as.numeric(p21.11.s$C4))
p21.11.s.C3=sum(as.numeric(p21.11.s$C3))
p21.11.s.Pr=sum(as.numeric(p21.11.s$Perennial))
p21.11.s.AB=sum(as.numeric(p21.11.s$Annl.Biennial))

p22.11.s.C4=sum(as.numeric(p22.11.s$C4))
p22.11.s.C3=sum(as.numeric(p22.11.s$C3))
p22.11.s.Pr=sum(as.numeric(p22.11.s$Perennial))
p22.11.s.AB=sum(as.numeric(p22.11.s$Annl.Biennial))

p23.11.s.C4=sum(as.numeric(p23.11.s$C4))
p23.11.s.C3=sum(as.numeric(p23.11.s$C3))
p23.11.s.Pr=sum(as.numeric(p23.11.s$Perennial))
p23.11.s.AB=sum(as.numeric(p23.11.s$Annl.Biennial))

p24.11.s.C4=sum(as.numeric(p24.11.s$C4))
p24.11.s.C3=sum(as.numeric(p24.11.s$C3))
p24.11.s.Pr=sum(as.numeric(p24.11.s$Perennial))
p24.11.s.AB=sum(as.numeric(p24.11.s$Annl.Biennial))

p25.11.s.C4=sum(as.numeric(p25.11.s$C4))
p25.11.s.C3=sum(as.numeric(p25.11.s$C3))
p25.11.s.Pr=sum(as.numeric(p25.11.s$Perennial))
p25.11.s.AB=sum(as.numeric(p25.11.s$Annl.Biennial))

p26.11.s.C4=sum(as.numeric(p26.11.s$C4))
p26.11.s.C3=sum(as.numeric(p26.11.s$C3))
p26.11.s.Pr=sum(as.numeric(p26.11.s$Perennial))
p26.11.s.AB=sum(as.numeric(p26.11.s$Annl.Biennial))

p27.11.s.C4=sum(as.numeric(p27.11.s$C4))
p27.11.s.C3=sum(as.numeric(p27.11.s$C3))
p27.11.s.Pr=sum(as.numeric(p27.11.s$Perennial))
p27.11.s.AB=sum(as.numeric(p27.11.s$Annl.Biennial))

p28.11.s.C4=sum(as.numeric(p28.11.s$C4))
p28.11.s.C3=sum(as.numeric(p28.11.s$C3))
p28.11.s.Pr=sum(as.numeric(p28.11.s$Perennial))
p28.11.s.AB=sum(as.numeric(p28.11.s$Annl.Biennial))

p29.11.s.C4=sum(as.numeric(p29.11.s$C4))
p29.11.s.C3=sum(as.numeric(p29.11.s$C3))
p29.11.s.Pr=sum(as.numeric(p29.11.s$Perennial))
p29.11.s.AB=sum(as.numeric(p29.11.s$Annl.Biennial))

p30.11.s.C4=sum(as.numeric(p30.11.s$C4))
p30.11.s.C3=sum(as.numeric(p30.11.s$C3))
p30.11.s.Pr=sum(as.numeric(p30.11.s$Perennial))
p30.11.s.AB=sum(as.numeric(p30.11.s$Annl.Biennial))

p31.11.s.C4=sum(as.numeric(p31.11.s$C4))
p31.11.s.C3=sum(as.numeric(p31.11.s$C3))
p31.11.s.Pr=sum(as.numeric(p31.11.s$Perennial))
p31.11.s.AB=sum(as.numeric(p31.11.s$Annl.Biennial))

p32.11.s.C4=sum(as.numeric(p32.11.s$C4))
p32.11.s.C3=sum(as.numeric(p32.11.s$C3))
p32.11.s.Pr=sum(as.numeric(p32.11.s$Perennial))
p32.11.s.AB=sum(as.numeric(p32.11.s$Annl.Biennial))

p33.11.s.C4=sum(as.numeric(p33.11.s$C4))
p33.11.s.C3=sum(as.numeric(p33.11.s$C3))
p33.11.s.Pr=sum(as.numeric(p33.11.s$Perennial))
p33.11.s.AB=sum(as.numeric(p33.11.s$Annl.Biennial))

p34.11.s.C4=sum(as.numeric(p34.11.s$C4))
p34.11.s.C3=sum(as.numeric(p34.11.s$C3))
p34.11.s.Pr=sum(as.numeric(p34.11.s$Perennial))
p34.11.s.AB=sum(as.numeric(p34.11.s$Annl.Biennial))

p35.11.s.C4=sum(as.numeric(p35.11.s$C4))
p35.11.s.C3=sum(as.numeric(p35.11.s$C3))
p35.11.s.Pr=sum(as.numeric(p35.11.s$Perennial))
p35.11.s.AB=sum(as.numeric(p35.11.s$Annl.Biennial))

p36.11.s.C4=sum(as.numeric(p36.11.s$C4))
p36.11.s.C3=sum(as.numeric(p36.11.s$C3))
p36.11.s.Pr=sum(as.numeric(p36.11.s$Perennial))
p36.11.s.AB=sum(as.numeric(p36.11.s$Annl.Biennial))


```

#2012
```{r}
p1.12.f.C4=sum(as.numeric(p1.12.f$C4))
p1.12.f.C3=sum(as.numeric(p1.12.f$C3))
p1.12.f.Pr=sum(as.numeric(p1.12.f$Perennial))
p1.12.f.AB=sum(as.numeric(p1.12.f$Annl.Biennial))

p2.12.f.C4=sum(as.numeric(p2.12.f$C4))
p2.12.f.C3=sum(as.numeric(p2.12.f$C3))
p2.12.f.Pr=sum(as.numeric(p2.12.f$Perennial))
p2.12.f.AB=sum(as.numeric(p2.12.f$Annl.Biennial))

p3.12.f.C4=sum(as.numeric(p3.12.f$C4))
p3.12.f.C3=sum(as.numeric(p3.12.f$C3))
p3.12.f.Pr=sum(as.numeric(p3.12.f$Perennial))
p3.12.f.AB=sum(as.numeric(p3.12.f$Annl.Biennial))

p4.12.f.C4=sum(as.numeric(p4.12.f$C4))
p4.12.f.C3=sum(as.numeric(p4.12.f$C3))
p4.12.f.Pr=sum(as.numeric(p4.12.f$Perennial))
p4.12.f.AB=sum(as.numeric(p4.12.f$Annl.Biennial))

p5.12.f.C4=sum(as.numeric(p5.12.f$C4))
p5.12.f.C3=sum(as.numeric(p5.12.f$C3))
p5.12.f.Pr=sum(as.numeric(p5.12.f$Perennial))
p5.12.f.AB=sum(as.numeric(p5.12.f$Annl.Biennial))

p6.12.f.C4=sum(as.numeric(p6.12.f$C4))
p6.12.f.C3=sum(as.numeric(p6.12.f$C3))
p6.12.f.Pr=sum(as.numeric(p6.12.f$Perennial))
p6.12.f.AB=sum(as.numeric(p6.12.f$Annl.Biennial))

p7.12.f.C4=sum(as.numeric(p7.12.f$C4))
p7.12.f.C3=sum(as.numeric(p7.12.f$C3))
p7.12.f.Pr=sum(as.numeric(p7.12.f$Perennial))
p7.12.f.AB=sum(as.numeric(p7.12.f$Annl.Biennial))

p8.12.f.C4=sum(as.numeric(p8.12.f$C4))
p8.12.f.C3=sum(as.numeric(p8.12.f$C3))
p8.12.f.Pr=sum(as.numeric(p8.12.f$Perennial))
p8.12.f.AB=sum(as.numeric(p8.12.f$Annl.Biennial))

p9.12.f.C4=sum(as.numeric(p9.12.f$C4))
p9.12.f.C3=sum(as.numeric(p9.12.f$C3))
p9.12.f.Pr=sum(as.numeric(p9.12.f$Perennial))
p9.12.f.AB=sum(as.numeric(p9.12.f$Annl.Biennial))

p10.12.f.C4=sum(as.numeric(p10.12.f$C4))
p10.12.f.C3=sum(as.numeric(p10.12.f$C3))
p10.12.f.Pr=sum(as.numeric(p10.12.f$Perennial))
p10.12.f.AB=sum(as.numeric(p10.12.f$Annl.Biennial))

p11.12.f.C4=sum(as.numeric(p11.12.f$C4))
p11.12.f.C3=sum(as.numeric(p11.12.f$C3))
p11.12.f.Pr=sum(as.numeric(p11.12.f$Perennial))
p11.12.f.AB=sum(as.numeric(p11.12.f$Annl.Biennial))

p12.12.f.C4=sum(as.numeric(p12.12.f$C4))
p12.12.f.C3=sum(as.numeric(p12.12.f$C3))
p12.12.f.Pr=sum(as.numeric(p12.12.f$Perennial))
p12.12.f.AB=sum(as.numeric(p12.12.f$Annl.Biennial))

p13.12.f.C4=sum(as.numeric(p13.12.f$C4))
p13.12.f.C3=sum(as.numeric(p13.12.f$C3))
p13.12.f.Pr=sum(as.numeric(p13.12.f$Perennial))
p13.12.f.AB=sum(as.numeric(p13.12.f$Annl.Biennial))

p14.12.f.C4=sum(as.numeric(p14.12.f$C4))
p14.12.f.C3=sum(as.numeric(p14.12.f$C3))
p14.12.f.Pr=sum(as.numeric(p14.12.f$Perennial))
p14.12.f.AB=sum(as.numeric(p14.12.f$Annl.Biennial))

p15.12.f.C4=sum(as.numeric(p15.12.f$C4))
p15.12.f.C3=sum(as.numeric(p15.12.f$C3))
p15.12.f.Pr=sum(as.numeric(p15.12.f$Perennial))
p15.12.f.AB=sum(as.numeric(p15.12.f$Annl.Biennial))

p16.12.f.C4=sum(as.numeric(p16.12.f$C4))
p16.12.f.C3=sum(as.numeric(p16.12.f$C3))
p16.12.f.Pr=sum(as.numeric(p16.12.f$Perennial))
p16.12.f.AB=sum(as.numeric(p16.12.f$Annl.Biennial))

p17.12.f.C4=sum(as.numeric(p17.12.f$C4))
p17.12.f.C3=sum(as.numeric(p17.12.f$C3))
p17.12.f.Pr=sum(as.numeric(p17.12.f$Perennial))
p17.12.f.AB=sum(as.numeric(p17.12.f$Annl.Biennial))

p18.12.f.C4=sum(as.numeric(p18.12.f$C4))
p18.12.f.C3=sum(as.numeric(p18.12.f$C3))
p18.12.f.Pr=sum(as.numeric(p18.12.f$Perennial))
p18.12.f.AB=sum(as.numeric(p18.12.f$Annl.Biennial))

p19.12.f.C4=sum(as.numeric(p19.12.f$C4))
p19.12.f.C3=sum(as.numeric(p19.12.f$C3))
p19.12.f.Pr=sum(as.numeric(p19.12.f$Perennial))
p19.12.f.AB=sum(as.numeric(p19.12.f$Annl.Biennial))

p20.12.f.C4=sum(as.numeric(p20.12.f$C4))
p20.12.f.C3=sum(as.numeric(p20.12.f$C3))
p20.12.f.Pr=sum(as.numeric(p20.12.f$Perennial))
p20.12.f.AB=sum(as.numeric(p20.12.f$Annl.Biennial))

p21.12.f.C4=sum(as.numeric(p21.12.f$C4))
p21.12.f.C3=sum(as.numeric(p21.12.f$C3))
p21.12.f.Pr=sum(as.numeric(p21.12.f$Perennial))
p21.12.f.AB=sum(as.numeric(p21.12.f$Annl.Biennial))

p22.12.f.C4=sum(as.numeric(p22.12.f$C4))
p22.12.f.C3=sum(as.numeric(p22.12.f$C3))
p22.12.f.Pr=sum(as.numeric(p22.12.f$Perennial))
p22.12.f.AB=sum(as.numeric(p22.12.f$Annl.Biennial))

p23.12.f.C4=sum(as.numeric(p23.12.f$C4))
p23.12.f.C3=sum(as.numeric(p23.12.f$C3))
p23.12.f.Pr=sum(as.numeric(p23.12.f$Perennial))
p23.12.f.AB=sum(as.numeric(p23.12.f$Annl.Biennial))

p24.12.f.C4=sum(as.numeric(p24.12.f$C4))
p24.12.f.C3=sum(as.numeric(p24.12.f$C3))
p24.12.f.Pr=sum(as.numeric(p24.12.f$Perennial))
p24.12.f.AB=sum(as.numeric(p24.12.f$Annl.Biennial))

p25.12.f.C4=sum(as.numeric(p25.12.f$C4))
p25.12.f.C3=sum(as.numeric(p25.12.f$C3))
p25.12.f.Pr=sum(as.numeric(p25.12.f$Perennial))
p25.12.f.AB=sum(as.numeric(p25.12.f$Annl.Biennial))

p26.12.f.C4=sum(as.numeric(p26.12.f$C4))
p26.12.f.C3=sum(as.numeric(p26.12.f$C3))
p26.12.f.Pr=sum(as.numeric(p26.12.f$Perennial))
p26.12.f.AB=sum(as.numeric(p26.12.f$Annl.Biennial))

p27.12.f.C4=sum(as.numeric(p27.12.f$C4))
p27.12.f.C3=sum(as.numeric(p27.12.f$C3))
p27.12.f.Pr=sum(as.numeric(p27.12.f$Perennial))
p27.12.f.AB=sum(as.numeric(p27.12.f$Annl.Biennial))

p28.12.f.C4=sum(as.numeric(p28.12.f$C4))
p28.12.f.C3=sum(as.numeric(p28.12.f$C3))
p28.12.f.Pr=sum(as.numeric(p28.12.f$Perennial))
p28.12.f.AB=sum(as.numeric(p28.12.f$Annl.Biennial))

p29.12.f.C4=sum(as.numeric(p29.12.f$C4))
p29.12.f.C3=sum(as.numeric(p29.12.f$C3))
p29.12.f.Pr=sum(as.numeric(p29.12.f$Perennial))
p29.12.f.AB=sum(as.numeric(p29.12.f$Annl.Biennial))

p30.12.f.C4=sum(as.numeric(p30.12.f$C4))
p30.12.f.C3=sum(as.numeric(p30.12.f$C3))
p30.12.f.Pr=sum(as.numeric(p30.12.f$Perennial))
p30.12.f.AB=sum(as.numeric(p30.12.f$Annl.Biennial))

p31.12.f.C4=sum(as.numeric(p31.12.f$C4))
p31.12.f.C3=sum(as.numeric(p31.12.f$C3))
p31.12.f.Pr=sum(as.numeric(p31.12.f$Perennial))
p31.12.f.AB=sum(as.numeric(p31.12.f$Annl.Biennial))

p32.12.f.C4=sum(as.numeric(p32.12.f$C4))
p32.12.f.C3=sum(as.numeric(p32.12.f$C3))
p32.12.f.Pr=sum(as.numeric(p32.12.f$Perennial))
p32.12.f.AB=sum(as.numeric(p32.12.f$Annl.Biennial))

p33.12.f.C4=sum(as.numeric(p33.12.f$C4))
p33.12.f.C3=sum(as.numeric(p33.12.f$C3))
p33.12.f.Pr=sum(as.numeric(p33.12.f$Perennial))
p33.12.f.AB=sum(as.numeric(p33.12.f$Annl.Biennial))

p34.12.f.C4=sum(as.numeric(p34.12.f$C4))
p34.12.f.C3=sum(as.numeric(p34.12.f$C3))
p34.12.f.Pr=sum(as.numeric(p34.12.f$Perennial))
p34.12.f.AB=sum(as.numeric(p34.12.f$Annl.Biennial))

p35.12.f.C4=sum(as.numeric(p35.12.f$C4))
p35.12.f.C3=sum(as.numeric(p35.12.f$C3))
p35.12.f.Pr=sum(as.numeric(p35.12.f$Perennial))
p35.12.f.AB=sum(as.numeric(p35.12.f$Annl.Biennial))

p36.12.f.C4=sum(as.numeric(p36.12.f$C4))
p36.12.f.C3=sum(as.numeric(p36.12.f$C3))
p36.12.f.Pr=sum(as.numeric(p36.12.f$Perennial))
p36.12.f.AB=sum(as.numeric(p36.12.f$Annl.Biennial))

#summer 
p1.12.s.C4=sum(as.numeric(p1.12.s$C4))
p1.12.s.C3=sum(as.numeric(p1.12.s$C3))
p1.12.s.Pr=sum(as.numeric(p1.12.s$Perennial))
p1.12.s.AB=sum(as.numeric(p1.12.s$Annl.Biennial))

p2.12.s.C4=sum(as.numeric(p2.12.s$C4))
p2.12.s.C3=sum(as.numeric(p2.12.s$C3))
p2.12.s.Pr=sum(as.numeric(p2.12.s$Perennial))
p2.12.s.AB=sum(as.numeric(p2.12.s$Annl.Biennial))

p3.12.s.C4=sum(as.numeric(p3.12.s$C4))
p3.12.s.C3=sum(as.numeric(p3.12.s$C3))
p3.12.s.Pr=sum(as.numeric(p3.12.s$Perennial))
p3.12.s.AB=sum(as.numeric(p3.12.s$Annl.Biennial))

p4.12.s.C4=sum(as.numeric(p4.12.s$C4))
p4.12.s.C3=sum(as.numeric(p4.12.s$C3))
p4.12.s.Pr=sum(as.numeric(p4.12.s$Perennial))
p4.12.s.AB=sum(as.numeric(p4.12.s$Annl.Biennial))

p5.12.s.C4=sum(as.numeric(p5.12.s$C4))
p5.12.s.C3=sum(as.numeric(p5.12.s$C3))
p5.12.s.Pr=sum(as.numeric(p5.12.s$Perennial))
p5.12.s.AB=sum(as.numeric(p5.12.s$Annl.Biennial))

p6.12.s.C4=sum(as.numeric(p6.12.s$C4))
p6.12.s.C3=sum(as.numeric(p6.12.s$C3))
p6.12.s.Pr=sum(as.numeric(p6.12.s$Perennial))
p6.12.s.AB=sum(as.numeric(p6.12.s$Annl.Biennial))

p7.12.s.C4=sum(as.numeric(p7.12.s$C4))
p7.12.s.C3=sum(as.numeric(p7.12.s$C3))
p7.12.s.Pr=sum(as.numeric(p7.12.s$Perennial))
p7.12.s.AB=sum(as.numeric(p7.12.s$Annl.Biennial))

p8.12.s.C4=sum(as.numeric(p8.12.s$C4))
p8.12.s.C3=sum(as.numeric(p8.12.s$C3))
p8.12.s.Pr=sum(as.numeric(p8.12.s$Perennial))
p8.12.s.AB=sum(as.numeric(p8.12.s$Annl.Biennial))

p9.12.s.C4=sum(as.numeric(p9.12.s$C4))
p9.12.s.C3=sum(as.numeric(p9.12.s$C3))
p9.12.s.Pr=sum(as.numeric(p9.12.s$Perennial))
p9.12.s.AB=sum(as.numeric(p9.12.s$Annl.Biennial))

p10.12.s.C4=sum(as.numeric(p10.12.s$C4))
p10.12.s.C3=sum(as.numeric(p10.12.s$C3))
p10.12.s.Pr=sum(as.numeric(p10.12.s$Perennial))
p10.12.s.AB=sum(as.numeric(p10.12.s$Annl.Biennial))

p11.12.s.C4=sum(as.numeric(p11.12.s$C4))
p11.12.s.C3=sum(as.numeric(p11.12.s$C3))
p11.12.s.Pr=sum(as.numeric(p11.12.s$Perennial))
p11.12.s.AB=sum(as.numeric(p11.12.s$Annl.Biennial))

p12.12.s.C4=sum(as.numeric(p12.12.s$C4))
p12.12.s.C3=sum(as.numeric(p12.12.s$C3))
p12.12.s.Pr=sum(as.numeric(p12.12.s$Perennial))
p12.12.s.AB=sum(as.numeric(p12.12.s$Annl.Biennial))

p13.12.s.C4=sum(as.numeric(p13.12.s$C4))
p13.12.s.C3=sum(as.numeric(p13.12.s$C3))
p13.12.s.Pr=sum(as.numeric(p13.12.s$Perennial))
p13.12.s.AB=sum(as.numeric(p13.12.s$Annl.Biennial))

p14.12.s.C4=sum(as.numeric(p14.12.s$C4))
p14.12.s.C3=sum(as.numeric(p14.12.s$C3))
p14.12.s.Pr=sum(as.numeric(p14.12.s$Perennial))
p14.12.s.AB=sum(as.numeric(p14.12.s$Annl.Biennial))

p15.12.s.C4=sum(as.numeric(p15.12.s$C4))
p15.12.s.C3=sum(as.numeric(p15.12.s$C3))
p15.12.s.Pr=sum(as.numeric(p15.12.s$Perennial))
p15.12.s.AB=sum(as.numeric(p15.12.s$Annl.Biennial))

p16.12.s.C4=sum(as.numeric(p16.12.s$C4))
p16.12.s.C3=sum(as.numeric(p16.12.s$C3))
p16.12.s.Pr=sum(as.numeric(p16.12.s$Perennial))
p16.12.s.AB=sum(as.numeric(p16.12.s$Annl.Biennial))

p17.12.s.C4=sum(as.numeric(p17.12.s$C4))
p17.12.s.C3=sum(as.numeric(p17.12.s$C3))
p17.12.s.Pr=sum(as.numeric(p17.12.s$Perennial))
p17.12.s.AB=sum(as.numeric(p17.12.s$Annl.Biennial))

p18.12.s.C4=sum(as.numeric(p18.12.s$C4))
p18.12.s.C3=sum(as.numeric(p18.12.s$C3))
p18.12.s.Pr=sum(as.numeric(p18.12.s$Perennial))
p18.12.s.AB=sum(as.numeric(p18.12.s$Annl.Biennial))

p19.12.s.C4=sum(as.numeric(p19.12.s$C4))
p19.12.s.C3=sum(as.numeric(p19.12.s$C3))
p19.12.s.Pr=sum(as.numeric(p19.12.s$Perennial))
p19.12.s.AB=sum(as.numeric(p19.12.s$Annl.Biennial))

p20.12.s.C4=sum(as.numeric(p20.12.s$C4))
p20.12.s.C3=sum(as.numeric(p20.12.s$C3))
p20.12.s.Pr=sum(as.numeric(p20.12.s$Perennial))
p20.12.s.AB=sum(as.numeric(p20.12.s$Annl.Biennial))

p21.12.s.C4=sum(as.numeric(p21.12.s$C4))
p21.12.s.C3=sum(as.numeric(p21.12.s$C3))
p21.12.s.Pr=sum(as.numeric(p21.12.s$Perennial))
p21.12.s.AB=sum(as.numeric(p21.12.s$Annl.Biennial))

p22.12.s.C4=sum(as.numeric(p22.12.s$C4))
p22.12.s.C3=sum(as.numeric(p22.12.s$C3))
p22.12.s.Pr=sum(as.numeric(p22.12.s$Perennial))
p22.12.s.AB=sum(as.numeric(p22.12.s$Annl.Biennial))

p23.12.s.C4=sum(as.numeric(p23.12.s$C4))
p23.12.s.C3=sum(as.numeric(p23.12.s$C3))
p23.12.s.Pr=sum(as.numeric(p23.12.s$Perennial))
p23.12.s.AB=sum(as.numeric(p23.12.s$Annl.Biennial))

p24.12.s.C4=sum(as.numeric(p24.12.s$C4))
p24.12.s.C3=sum(as.numeric(p24.12.s$C3))
p24.12.s.Pr=sum(as.numeric(p24.12.s$Perennial))
p24.12.s.AB=sum(as.numeric(p24.12.s$Annl.Biennial))

p25.12.s.C4=sum(as.numeric(p25.12.s$C4))
p25.12.s.C3=sum(as.numeric(p25.12.s$C3))
p25.12.s.Pr=sum(as.numeric(p25.12.s$Perennial))
p25.12.s.AB=sum(as.numeric(p25.12.s$Annl.Biennial))

p26.12.s.C4=sum(as.numeric(p26.12.s$C4))
p26.12.s.C3=sum(as.numeric(p26.12.s$C3))
p26.12.s.Pr=sum(as.numeric(p26.12.s$Perennial))
p26.12.s.AB=sum(as.numeric(p26.12.s$Annl.Biennial))

p27.12.s.C4=sum(as.numeric(p27.12.s$C4))
p27.12.s.C3=sum(as.numeric(p27.12.s$C3))
p27.12.s.Pr=sum(as.numeric(p27.12.s$Perennial))
p27.12.s.AB=sum(as.numeric(p27.12.s$Annl.Biennial))

p28.12.s.C4=sum(as.numeric(p28.12.s$C4))
p28.12.s.C3=sum(as.numeric(p28.12.s$C3))
p28.12.s.Pr=sum(as.numeric(p28.12.s$Perennial))
p28.12.s.AB=sum(as.numeric(p28.12.s$Annl.Biennial))

p29.12.s.C4=sum(as.numeric(p29.12.s$C4))
p29.12.s.C3=sum(as.numeric(p29.12.s$C3))
p29.12.s.Pr=sum(as.numeric(p29.12.s$Perennial))
p29.12.s.AB=sum(as.numeric(p29.12.s$Annl.Biennial))

p30.12.s.C4=sum(as.numeric(p30.12.s$C4))
p30.12.s.C3=sum(as.numeric(p30.12.s$C3))
p30.12.s.Pr=sum(as.numeric(p30.12.s$Perennial))
p30.12.s.AB=sum(as.numeric(p30.12.s$Annl.Biennial))

p31.12.s.C4=sum(as.numeric(p31.12.s$C4))
p31.12.s.C3=sum(as.numeric(p31.12.s$C3))
p31.12.s.Pr=sum(as.numeric(p31.12.s$Perennial))
p31.12.s.AB=sum(as.numeric(p31.12.s$Annl.Biennial))

p32.12.s.C4=sum(as.numeric(p32.12.s$C4))
p32.12.s.C3=sum(as.numeric(p32.12.s$C3))
p32.12.s.Pr=sum(as.numeric(p32.12.s$Perennial))
p32.12.s.AB=sum(as.numeric(p32.12.s$Annl.Biennial))

p33.12.s.C4=sum(as.numeric(p33.12.s$C4))
p33.12.s.C3=sum(as.numeric(p33.12.s$C3))
p33.12.s.Pr=sum(as.numeric(p33.12.s$Perennial))
p33.12.s.AB=sum(as.numeric(p33.12.s$Annl.Biennial))

p34.12.s.C4=sum(as.numeric(p34.12.s$C4))
p34.12.s.C3=sum(as.numeric(p34.12.s$C3))
p34.12.s.Pr=sum(as.numeric(p34.12.s$Perennial))
p34.12.s.AB=sum(as.numeric(p34.12.s$Annl.Biennial))

p35.12.s.C4=sum(as.numeric(p35.12.s$C4))
p35.12.s.C3=sum(as.numeric(p35.12.s$C3))
p35.12.s.Pr=sum(as.numeric(p35.12.s$Perennial))
p35.12.s.AB=sum(as.numeric(p35.12.s$Annl.Biennial))

p36.12.s.C4=sum(as.numeric(p36.12.s$C4))
p36.12.s.C3=sum(as.numeric(p36.12.s$C3))
p36.12.s.Pr=sum(as.numeric(p36.12.s$Perennial))
p36.12.s.AB=sum(as.numeric(p36.12.s$Annl.Biennial))


```

#2013
```{r}
#2013 Fall
p1.13.f.C4=sum(as.numeric(p1.13.f$C4))
p1.13.f.C3=sum(as.numeric(p1.13.f$C3))
p1.13.f.Pr=sum(as.numeric(p1.13.f$Perennial))
p1.13.f.AB=sum(as.numeric(p1.13.f$Annl.Biennial))

p2.13.f.C4=sum(as.numeric(p2.13.f$C4))
p2.13.f.C3=sum(as.numeric(p2.13.f$C3))
p2.13.f.Pr=sum(as.numeric(p2.13.f$Perennial))
p2.13.f.AB=sum(as.numeric(p2.13.f$Annl.Biennial))

p3.13.f.C4=sum(as.numeric(p3.13.f$C4))
p3.13.f.C3=sum(as.numeric(p3.13.f$C3))
p3.13.f.Pr=sum(as.numeric(p3.13.f$Perennial))
p3.13.f.AB=sum(as.numeric(p3.13.f$Annl.Biennial))

p4.13.f.C4=sum(as.numeric(p4.13.f$C4))
p4.13.f.C3=sum(as.numeric(p4.13.f$C3))
p4.13.f.Pr=sum(as.numeric(p4.13.f$Perennial))
p4.13.f.AB=sum(as.numeric(p4.13.f$Annl.Biennial))

p5.13.f.C4=sum(as.numeric(p5.13.f$C4))
p5.13.f.C3=sum(as.numeric(p5.13.f$C3))
p5.13.f.Pr=sum(as.numeric(p5.13.f$Perennial))
p5.13.f.AB=sum(as.numeric(p5.13.f$Annl.Biennial))

p6.13.f.C4=sum(as.numeric(p6.13.f$C4))
p6.13.f.C3=sum(as.numeric(p6.13.f$C3))
p6.13.f.Pr=sum(as.numeric(p6.13.f$Perennial))
p6.13.f.AB=sum(as.numeric(p6.13.f$Annl.Biennial))

p7.13.f.C4=sum(as.numeric(p7.13.f$C4))
p7.13.f.C3=sum(as.numeric(p7.13.f$C3))
p7.13.f.Pr=sum(as.numeric(p7.13.f$Perennial))
p7.13.f.AB=sum(as.numeric(p7.13.f$Annl.Biennial))

p8.13.f.C4=sum(as.numeric(p8.13.f$C4))
p8.13.f.C3=sum(as.numeric(p8.13.f$C3))
p8.13.f.Pr=sum(as.numeric(p8.13.f$Perennial))
p8.13.f.AB=sum(as.numeric(p8.13.f$Annl.Biennial))

p9.13.f.C4=sum(as.numeric(p9.13.f$C4))
p9.13.f.C3=sum(as.numeric(p9.13.f$C3))
p9.13.f.Pr=sum(as.numeric(p9.13.f$Perennial))
p9.13.f.AB=sum(as.numeric(p9.13.f$Annl.Biennial))

p10.13.f.C4=sum(as.numeric(p10.13.f$C4))
p10.13.f.C3=sum(as.numeric(p10.13.f$C3))
p10.13.f.Pr=sum(as.numeric(p10.13.f$Perennial))
p10.13.f.AB=sum(as.numeric(p10.13.f$Annl.Biennial))

p11.13.f.C4=sum(as.numeric(p11.13.f$C4))
p11.13.f.C3=sum(as.numeric(p11.13.f$C3))
p11.13.f.Pr=sum(as.numeric(p11.13.f$Perennial))
p11.13.f.AB=sum(as.numeric(p11.13.f$Annl.Biennial))

p12.13.f.C4=sum(as.numeric(p12.13.f$C4))
p12.13.f.C3=sum(as.numeric(p12.13.f$C3))
p12.13.f.Pr=sum(as.numeric(p12.13.f$Perennial))
p12.13.f.AB=sum(as.numeric(p12.13.f$Annl.Biennial))

p13.13.f.C4=sum(as.numeric(p13.13.f$C4))
p13.13.f.C3=sum(as.numeric(p13.13.f$C3))
p13.13.f.Pr=sum(as.numeric(p13.13.f$Perennial))
p13.13.f.AB=sum(as.numeric(p13.13.f$Annl.Biennial))

p14.13.f.C4=sum(as.numeric(p14.13.f$C4))
p14.13.f.C3=sum(as.numeric(p14.13.f$C3))
p14.13.f.Pr=sum(as.numeric(p14.13.f$Perennial))
p14.13.f.AB=sum(as.numeric(p14.13.f$Annl.Biennial))

p15.13.f.C4=sum(as.numeric(p15.13.f$C4))
p15.13.f.C3=sum(as.numeric(p15.13.f$C3))
p15.13.f.Pr=sum(as.numeric(p15.13.f$Perennial))
p15.13.f.AB=sum(as.numeric(p15.13.f$Annl.Biennial))

p16.13.f.C4=sum(as.numeric(p16.13.f$C4))
p16.13.f.C3=sum(as.numeric(p16.13.f$C3))
p16.13.f.Pr=sum(as.numeric(p16.13.f$Perennial))
p16.13.f.AB=sum(as.numeric(p16.13.f$Annl.Biennial))

p17.13.f.C4=sum(as.numeric(p17.13.f$C4))
p17.13.f.C3=sum(as.numeric(p17.13.f$C3))
p17.13.f.Pr=sum(as.numeric(p17.13.f$Perennial))
p17.13.f.AB=sum(as.numeric(p17.13.f$Annl.Biennial))

p18.13.f.C4=sum(as.numeric(p18.13.f$C4))
p18.13.f.C3=sum(as.numeric(p18.13.f$C3))
p18.13.f.Pr=sum(as.numeric(p18.13.f$Perennial))
p18.13.f.AB=sum(as.numeric(p18.13.f$Annl.Biennial))

p19.13.f.C4=sum(as.numeric(p19.13.f$C4))
p19.13.f.C3=sum(as.numeric(p19.13.f$C3))
p19.13.f.Pr=sum(as.numeric(p19.13.f$Perennial))
p19.13.f.AB=sum(as.numeric(p19.13.f$Annl.Biennial))

p20.13.f.C4=sum(as.numeric(p20.13.f$C4))
p20.13.f.C3=sum(as.numeric(p20.13.f$C3))
p20.13.f.Pr=sum(as.numeric(p20.13.f$Perennial))
p20.13.f.AB=sum(as.numeric(p20.13.f$Annl.Biennial))

p21.13.f.C4=sum(as.numeric(p21.13.f$C4))
p21.13.f.C3=sum(as.numeric(p21.13.f$C3))
p21.13.f.Pr=sum(as.numeric(p21.13.f$Perennial))
p21.13.f.AB=sum(as.numeric(p21.13.f$Annl.Biennial))

p22.13.f.C4=sum(as.numeric(p22.13.f$C4))
p22.13.f.C3=sum(as.numeric(p22.13.f$C3))
p22.13.f.Pr=sum(as.numeric(p22.13.f$Perennial))
p22.13.f.AB=sum(as.numeric(p22.13.f$Annl.Biennial))

p23.13.f.C4=sum(as.numeric(p23.13.f$C4))
p23.13.f.C3=sum(as.numeric(p23.13.f$C3))
p23.13.f.Pr=sum(as.numeric(p23.13.f$Perennial))
p23.13.f.AB=sum(as.numeric(p23.13.f$Annl.Biennial))

p24.13.f.C4=sum(as.numeric(p24.13.f$C4))
p24.13.f.C3=sum(as.numeric(p24.13.f$C3))
p24.13.f.Pr=sum(as.numeric(p24.13.f$Perennial))
p24.13.f.AB=sum(as.numeric(p24.13.f$Annl.Biennial))

p25.13.f.C4=sum(as.numeric(p25.13.f$C4))
p25.13.f.C3=sum(as.numeric(p25.13.f$C3))
p25.13.f.Pr=sum(as.numeric(p25.13.f$Perennial))
p25.13.f.AB=sum(as.numeric(p25.13.f$Annl.Biennial))

p26.13.f.C4=sum(as.numeric(p26.13.f$C4))
p26.13.f.C3=sum(as.numeric(p26.13.f$C3))
p26.13.f.Pr=sum(as.numeric(p26.13.f$Perennial))
p26.13.f.AB=sum(as.numeric(p26.13.f$Annl.Biennial))

p27.13.f.C4=sum(as.numeric(p27.13.f$C4))
p27.13.f.C3=sum(as.numeric(p27.13.f$C3))
p27.13.f.Pr=sum(as.numeric(p27.13.f$Perennial))
p27.13.f.AB=sum(as.numeric(p27.13.f$Annl.Biennial))

p28.13.f.C4=sum(as.numeric(p28.13.f$C4))
p28.13.f.C3=sum(as.numeric(p28.13.f$C3))
p28.13.f.Pr=sum(as.numeric(p28.13.f$Perennial))
p28.13.f.AB=sum(as.numeric(p28.13.f$Annl.Biennial))

p29.13.f.C4=sum(as.numeric(p29.13.f$C4))
p29.13.f.C3=sum(as.numeric(p29.13.f$C3))
p29.13.f.Pr=sum(as.numeric(p29.13.f$Perennial))
p29.13.f.AB=sum(as.numeric(p29.13.f$Annl.Biennial))

p30.13.f.C4=sum(as.numeric(p30.13.f$C4))
p30.13.f.C3=sum(as.numeric(p30.13.f$C3))
p30.13.f.Pr=sum(as.numeric(p30.13.f$Perennial))
p30.13.f.AB=sum(as.numeric(p30.13.f$Annl.Biennial))

p31.13.f.C4=sum(as.numeric(p31.13.f$C4))
p31.13.f.C3=sum(as.numeric(p31.13.f$C3))
p31.13.f.Pr=sum(as.numeric(p31.13.f$Perennial))
p31.13.f.AB=sum(as.numeric(p31.13.f$Annl.Biennial))

p32.13.f.C4=sum(as.numeric(p32.13.f$C4))
p32.13.f.C3=sum(as.numeric(p32.13.f$C3))
p32.13.f.Pr=sum(as.numeric(p32.13.f$Perennial))
p32.13.f.AB=sum(as.numeric(p32.13.f$Annl.Biennial))

p33.13.f.C4=sum(as.numeric(p33.13.f$C4))
p33.13.f.C3=sum(as.numeric(p33.13.f$C3))
p33.13.f.Pr=sum(as.numeric(p33.13.f$Perennial))
p33.13.f.AB=sum(as.numeric(p33.13.f$Annl.Biennial))

p34.13.f.C4=sum(as.numeric(p34.13.f$C4))
p34.13.f.C3=sum(as.numeric(p34.13.f$C3))
p34.13.f.Pr=sum(as.numeric(p34.13.f$Perennial))
p34.13.f.AB=sum(as.numeric(p34.13.f$Annl.Biennial))

p35.13.f.C4=sum(as.numeric(p35.13.f$C4))
p35.13.f.C3=sum(as.numeric(p35.13.f$C3))
p35.13.f.Pr=sum(as.numeric(p35.13.f$Perennial))
p35.13.f.AB=sum(as.numeric(p35.13.f$Annl.Biennial))

p36.13.f.C4=sum(as.numeric(p36.13.f$C4))
p36.13.f.C3=sum(as.numeric(p36.13.f$C3))
p36.13.f.Pr=sum(as.numeric(p36.13.f$Perennial))
p36.13.f.AB=sum(as.numeric(p36.13.f$Annl.Biennial))

#summer
p1.13.s.C4=sum(as.numeric(p1.13.s$C4))
p1.13.s.C3=sum(as.numeric(p1.13.s$C3))
p1.13.s.Pr=sum(as.numeric(p1.13.s$Perennial))
p1.13.s.AB=sum(as.numeric(p1.13.s$Annl.Biennial))

p2.13.s.C4=sum(as.numeric(p2.13.s$C4))
p2.13.s.C3=sum(as.numeric(p2.13.s$C3))
p2.13.s.Pr=sum(as.numeric(p2.13.s$Perennial))
p2.13.s.AB=sum(as.numeric(p2.13.s$Annl.Biennial))

p3.13.s.C4=sum(as.numeric(p3.13.s$C4))
p3.13.s.C3=sum(as.numeric(p3.13.s$C3))
p3.13.s.Pr=sum(as.numeric(p3.13.s$Perennial))
p3.13.s.AB=sum(as.numeric(p3.13.s$Annl.Biennial))

p4.13.s.C4=sum(as.numeric(p4.13.s$C4))
p4.13.s.C3=sum(as.numeric(p4.13.s$C3))
p4.13.s.Pr=sum(as.numeric(p4.13.s$Perennial))
p4.13.s.AB=sum(as.numeric(p4.13.s$Annl.Biennial))

p5.13.s.C4=sum(as.numeric(p5.13.s$C4))
p5.13.s.C3=sum(as.numeric(p5.13.s$C3))
p5.13.s.Pr=sum(as.numeric(p5.13.s$Perennial))
p5.13.s.AB=sum(as.numeric(p5.13.s$Annl.Biennial))

p6.13.s.C4=sum(as.numeric(p6.13.s$C4))
p6.13.s.C3=sum(as.numeric(p6.13.s$C3))
p6.13.s.Pr=sum(as.numeric(p6.13.s$Perennial))
p6.13.s.AB=sum(as.numeric(p6.13.s$Annl.Biennial))

p7.13.s.C4=sum(as.numeric(p7.13.s$C4))
p7.13.s.C3=sum(as.numeric(p7.13.s$C3))
p7.13.s.Pr=sum(as.numeric(p7.13.s$Perennial))
p7.13.s.AB=sum(as.numeric(p7.13.s$Annl.Biennial))

p8.13.s.C4=sum(as.numeric(p8.13.s$C4))
p8.13.s.C3=sum(as.numeric(p8.13.s$C3))
p8.13.s.Pr=sum(as.numeric(p8.13.s$Perennial))
p8.13.s.AB=sum(as.numeric(p8.13.s$Annl.Biennial))

p9.13.s.C4=sum(as.numeric(p9.13.s$C4))
p9.13.s.C3=sum(as.numeric(p9.13.s$C3))
p9.13.s.Pr=sum(as.numeric(p9.13.s$Perennial))
p9.13.s.AB=sum(as.numeric(p9.13.s$Annl.Biennial))

p10.13.s.C4=sum(as.numeric(p10.13.s$C4))
p10.13.s.C3=sum(as.numeric(p10.13.s$C3))
p10.13.s.Pr=sum(as.numeric(p10.13.s$Perennial))
p10.13.s.AB=sum(as.numeric(p10.13.s$Annl.Biennial))

p11.13.s.C4=sum(as.numeric(p11.13.s$C4))
p11.13.s.C3=sum(as.numeric(p11.13.s$C3))
p11.13.s.Pr=sum(as.numeric(p11.13.s$Perennial))
p11.13.s.AB=sum(as.numeric(p11.13.s$Annl.Biennial))

p12.13.s.C4=sum(as.numeric(p12.13.s$C4))
p12.13.s.C3=sum(as.numeric(p12.13.s$C3))
p12.13.s.Pr=sum(as.numeric(p12.13.s$Perennial))
p12.13.s.AB=sum(as.numeric(p12.13.s$Annl.Biennial))

p13.13.s.C4=sum(as.numeric(p13.13.s$C4))
p13.13.s.C3=sum(as.numeric(p13.13.s$C3))
p13.13.s.Pr=sum(as.numeric(p13.13.s$Perennial))
p13.13.s.AB=sum(as.numeric(p13.13.s$Annl.Biennial))

p14.13.s.C4=sum(as.numeric(p14.13.s$C4))
p14.13.s.C3=sum(as.numeric(p14.13.s$C3))
p14.13.s.Pr=sum(as.numeric(p14.13.s$Perennial))
p14.13.s.AB=sum(as.numeric(p14.13.s$Annl.Biennial))

p15.13.s.C4=sum(as.numeric(p15.13.s$C4))
p15.13.s.C3=sum(as.numeric(p15.13.s$C3))
p15.13.s.Pr=sum(as.numeric(p15.13.s$Perennial))
p15.13.s.AB=sum(as.numeric(p15.13.s$Annl.Biennial))

p16.13.s.C4=sum(as.numeric(p16.13.s$C4))
p16.13.s.C3=sum(as.numeric(p16.13.s$C3))
p16.13.s.Pr=sum(as.numeric(p16.13.s$Perennial))
p16.13.s.AB=sum(as.numeric(p16.13.s$Annl.Biennial))

p17.13.s.C4=sum(as.numeric(p17.13.s$C4))
p17.13.s.C3=sum(as.numeric(p17.13.s$C3))
p17.13.s.Pr=sum(as.numeric(p17.13.s$Perennial))
p17.13.s.AB=sum(as.numeric(p17.13.s$Annl.Biennial))

p18.13.s.C4=sum(as.numeric(p18.13.s$C4))
p18.13.s.C3=sum(as.numeric(p18.13.s$C3))
p18.13.s.Pr=sum(as.numeric(p18.13.s$Perennial))
p18.13.s.AB=sum(as.numeric(p18.13.s$Annl.Biennial))

p19.13.s.C4=sum(as.numeric(p19.13.s$C4))
p19.13.s.C3=sum(as.numeric(p19.13.s$C3))
p19.13.s.Pr=sum(as.numeric(p19.13.s$Perennial))
p19.13.s.AB=sum(as.numeric(p19.13.s$Annl.Biennial))

p20.13.s.C4=sum(as.numeric(p20.13.s$C4))
p20.13.s.C3=sum(as.numeric(p20.13.s$C3))
p20.13.s.Pr=sum(as.numeric(p20.13.s$Perennial))
p20.13.s.AB=sum(as.numeric(p20.13.s$Annl.Biennial))

p21.13.s.C4=sum(as.numeric(p21.13.s$C4))
p21.13.s.C3=sum(as.numeric(p21.13.s$C3))
p21.13.s.Pr=sum(as.numeric(p21.13.s$Perennial))
p21.13.s.AB=sum(as.numeric(p21.13.s$Annl.Biennial))

p22.13.s.C4=sum(as.numeric(p22.13.s$C4))
p22.13.s.C3=sum(as.numeric(p22.13.s$C3))
p22.13.s.Pr=sum(as.numeric(p22.13.s$Perennial))
p22.13.s.AB=sum(as.numeric(p22.13.s$Annl.Biennial))

p23.13.s.C4=sum(as.numeric(p23.13.s$C4))
p23.13.s.C3=sum(as.numeric(p23.13.s$C3))
p23.13.s.Pr=sum(as.numeric(p23.13.s$Perennial))
p23.13.s.AB=sum(as.numeric(p23.13.s$Annl.Biennial))

p24.13.s.C4=sum(as.numeric(p24.13.s$C4))
p24.13.s.C3=sum(as.numeric(p24.13.s$C3))
p24.13.s.Pr=sum(as.numeric(p24.13.s$Perennial))
p24.13.s.AB=sum(as.numeric(p24.13.s$Annl.Biennial))

p25.13.s.C4=sum(as.numeric(p25.13.s$C4))
p25.13.s.C3=sum(as.numeric(p25.13.s$C3))
p25.13.s.Pr=sum(as.numeric(p25.13.s$Perennial))
p25.13.s.AB=sum(as.numeric(p25.13.s$Annl.Biennial))

p26.13.s.C4=sum(as.numeric(p26.13.s$C4))
p26.13.s.C3=sum(as.numeric(p26.13.s$C3))
p26.13.s.Pr=sum(as.numeric(p26.13.s$Perennial))
p26.13.s.AB=sum(as.numeric(p26.13.s$Annl.Biennial))

p27.13.s.C4=sum(as.numeric(p27.13.s$C4))
p27.13.s.C3=sum(as.numeric(p27.13.s$C3))
p27.13.s.Pr=sum(as.numeric(p27.13.s$Perennial))
p27.13.s.AB=sum(as.numeric(p27.13.s$Annl.Biennial))

p28.13.s.C4=sum(as.numeric(p28.13.s$C4))
p28.13.s.C3=sum(as.numeric(p28.13.s$C3))
p28.13.s.Pr=sum(as.numeric(p28.13.s$Perennial))
p28.13.s.AB=sum(as.numeric(p28.13.s$Annl.Biennial))

p29.13.s.C4=sum(as.numeric(p29.13.s$C4))
p29.13.s.C3=sum(as.numeric(p29.13.s$C3))
p29.13.s.Pr=sum(as.numeric(p29.13.s$Perennial))
p29.13.s.AB=sum(as.numeric(p29.13.s$Annl.Biennial))

p30.13.s.C4=sum(as.numeric(p30.13.s$C4))
p30.13.s.C3=sum(as.numeric(p30.13.s$C3))
p30.13.s.Pr=sum(as.numeric(p30.13.s$Perennial))
p30.13.s.AB=sum(as.numeric(p30.13.s$Annl.Biennial))

p31.13.s.C4=sum(as.numeric(p31.13.s$C4))
p31.13.s.C3=sum(as.numeric(p31.13.s$C3))
p31.13.s.Pr=sum(as.numeric(p31.13.s$Perennial))
p31.13.s.AB=sum(as.numeric(p31.13.s$Annl.Biennial))

p32.13.s.C4=sum(as.numeric(p32.13.s$C4))
p32.13.s.C3=sum(as.numeric(p32.13.s$C3))
p32.13.s.Pr=sum(as.numeric(p32.13.s$Perennial))
p32.13.s.AB=sum(as.numeric(p32.13.s$Annl.Biennial))

p33.13.s.C4=sum(as.numeric(p33.13.s$C4))
p33.13.s.C3=sum(as.numeric(p33.13.s$C3))
p33.13.s.Pr=sum(as.numeric(p33.13.s$Perennial))
p33.13.s.AB=sum(as.numeric(p33.13.s$Annl.Biennial))

p34.13.s.C4=sum(as.numeric(p34.13.s$C4))
p34.13.s.C3=sum(as.numeric(p34.13.s$C3))
p34.13.s.Pr=sum(as.numeric(p34.13.s$Perennial))
p34.13.s.AB=sum(as.numeric(p34.13.s$Annl.Biennial))

p35.13.s.C4=sum(as.numeric(p35.13.s$C4))
p35.13.s.C3=sum(as.numeric(p35.13.s$C3))
p35.13.s.Pr=sum(as.numeric(p35.13.s$Perennial))
p35.13.s.AB=sum(as.numeric(p35.13.s$Annl.Biennial))

p36.13.s.C4=sum(as.numeric(p36.13.s$C4))
p36.13.s.C3=sum(as.numeric(p36.13.s$C3))
p36.13.s.Pr=sum(as.numeric(p36.13.s$Perennial))
p36.13.s.AB=sum(as.numeric(p36.13.s$Annl.Biennial))


```

#2014
```{r}
p1.14.f.C4=sum(as.numeric(p1.14.f$C4))
p1.14.f.C3=sum(as.numeric(p1.14.f$C3))
p1.14.f.Pr=sum(as.numeric(p1.14.f$Perennial))
p1.14.f.AB=sum(as.numeric(p1.14.f$Annl.Biennial))

p2.14.f.C4=sum(as.numeric(p2.14.f$C4))
p2.14.f.C3=sum(as.numeric(p2.14.f$C3))
p2.14.f.Pr=sum(as.numeric(p2.14.f$Perennial))
p2.14.f.AB=sum(as.numeric(p2.14.f$Annl.Biennial))

p3.14.f.C4=sum(as.numeric(p3.14.f$C4))
p3.14.f.C3=sum(as.numeric(p3.14.f$C3))
p3.14.f.Pr=sum(as.numeric(p3.14.f$Perennial))
p3.14.f.AB=sum(as.numeric(p3.14.f$Annl.Biennial))

p4.14.f.C4=sum(as.numeric(p4.14.f$C4))
p4.14.f.C3=sum(as.numeric(p4.14.f$C3))
p4.14.f.Pr=sum(as.numeric(p4.14.f$Perennial))
p4.14.f.AB=sum(as.numeric(p4.14.f$Annl.Biennial))

p5.14.f.C4=sum(as.numeric(p5.14.f$C4))
p5.14.f.C3=sum(as.numeric(p5.14.f$C3))
p5.14.f.Pr=sum(as.numeric(p5.14.f$Perennial))
p5.14.f.AB=sum(as.numeric(p5.14.f$Annl.Biennial))

p6.14.f.C4=sum(as.numeric(p6.14.f$C4))
p6.14.f.C3=sum(as.numeric(p6.14.f$C3))
p6.14.f.Pr=sum(as.numeric(p6.14.f$Perennial))
p6.14.f.AB=sum(as.numeric(p6.14.f$Annl.Biennial))

p7.14.f.C4=sum(as.numeric(p7.14.f$C4))
p7.14.f.C3=sum(as.numeric(p7.14.f$C3))
p7.14.f.Pr=sum(as.numeric(p7.14.f$Perennial))
p7.14.f.AB=sum(as.numeric(p7.14.f$Annl.Biennial))

p8.14.f.C4=sum(as.numeric(p8.14.f$C4))
p8.14.f.C3=sum(as.numeric(p8.14.f$C3))
p8.14.f.Pr=sum(as.numeric(p8.14.f$Perennial))
p8.14.f.AB=sum(as.numeric(p8.14.f$Annl.Biennial))

p9.14.f.C4=sum(as.numeric(p9.14.f$C4))
p9.14.f.C3=sum(as.numeric(p9.14.f$C3))
p9.14.f.Pr=sum(as.numeric(p9.14.f$Perennial))
p9.14.f.AB=sum(as.numeric(p9.14.f$Annl.Biennial))

p10.14.f.C4=sum(as.numeric(p10.14.f$C4))
p10.14.f.C3=sum(as.numeric(p10.14.f$C3))
p10.14.f.Pr=sum(as.numeric(p10.14.f$Perennial))
p10.14.f.AB=sum(as.numeric(p10.14.f$Annl.Biennial))

p11.14.f.C4=sum(as.numeric(p11.14.f$C4))
p11.14.f.C3=sum(as.numeric(p11.14.f$C3))
p11.14.f.Pr=sum(as.numeric(p11.14.f$Perennial))
p11.14.f.AB=sum(as.numeric(p11.14.f$Annl.Biennial))

p12.14.f.C4=sum(as.numeric(p12.14.f$C4))
p12.14.f.C3=sum(as.numeric(p12.14.f$C3))
p12.14.f.Pr=sum(as.numeric(p12.14.f$Perennial))
p12.14.f.AB=sum(as.numeric(p12.14.f$Annl.Biennial))

p13.14.f.C4=sum(as.numeric(p13.14.f$C4))
p13.14.f.C3=sum(as.numeric(p13.14.f$C3))
p13.14.f.Pr=sum(as.numeric(p13.14.f$Perennial))
p13.14.f.AB=sum(as.numeric(p13.14.f$Annl.Biennial))

p14.14.f.C4=sum(as.numeric(p14.14.f$C4))
p14.14.f.C3=sum(as.numeric(p14.14.f$C3))
p14.14.f.Pr=sum(as.numeric(p14.14.f$Perennial))
p14.14.f.AB=sum(as.numeric(p14.14.f$Annl.Biennial))

p15.14.f.C4=sum(as.numeric(p15.14.f$C4))
p15.14.f.C3=sum(as.numeric(p15.14.f$C3))
p15.14.f.Pr=sum(as.numeric(p15.14.f$Perennial))
p15.14.f.AB=sum(as.numeric(p15.14.f$Annl.Biennial))

p16.14.f.C4=sum(as.numeric(p16.14.f$C4))
p16.14.f.C3=sum(as.numeric(p16.14.f$C3))
p16.14.f.Pr=sum(as.numeric(p16.14.f$Perennial))
p16.14.f.AB=sum(as.numeric(p16.14.f$Annl.Biennial))

p17.14.f.C4=sum(as.numeric(p17.14.f$C4))
p17.14.f.C3=sum(as.numeric(p17.14.f$C3))
p17.14.f.Pr=sum(as.numeric(p17.14.f$Perennial))
p17.14.f.AB=sum(as.numeric(p17.14.f$Annl.Biennial))

p18.14.f.C4=sum(as.numeric(p18.14.f$C4))
p18.14.f.C3=sum(as.numeric(p18.14.f$C3))
p18.14.f.Pr=sum(as.numeric(p18.14.f$Perennial))
p18.14.f.AB=sum(as.numeric(p18.14.f$Annl.Biennial))

p19.14.f.C4=sum(as.numeric(p19.14.f$C4))
p19.14.f.C3=sum(as.numeric(p19.14.f$C3))
p19.14.f.Pr=sum(as.numeric(p19.14.f$Perennial))
p19.14.f.AB=sum(as.numeric(p19.14.f$Annl.Biennial))

p20.14.f.C4=sum(as.numeric(p20.14.f$C4))
p20.14.f.C3=sum(as.numeric(p20.14.f$C3))
p20.14.f.Pr=sum(as.numeric(p20.14.f$Perennial))
p20.14.f.AB=sum(as.numeric(p20.14.f$Annl.Biennial))

p21.14.f.C4=sum(as.numeric(p21.14.f$C4))
p21.14.f.C3=sum(as.numeric(p21.14.f$C3))
p21.14.f.Pr=sum(as.numeric(p21.14.f$Perennial))
p21.14.f.AB=sum(as.numeric(p21.14.f$Annl.Biennial))

p22.14.f.C4=sum(as.numeric(p22.14.f$C4))
p22.14.f.C3=sum(as.numeric(p22.14.f$C3))
p22.14.f.Pr=sum(as.numeric(p22.14.f$Perennial))
p22.14.f.AB=sum(as.numeric(p22.14.f$Annl.Biennial))

p23.14.f.C4=sum(as.numeric(p23.14.f$C4))
p23.14.f.C3=sum(as.numeric(p23.14.f$C3))
p23.14.f.Pr=sum(as.numeric(p23.14.f$Perennial))
p23.14.f.AB=sum(as.numeric(p23.14.f$Annl.Biennial))

p24.14.f.C4=sum(as.numeric(p24.14.f$C4))
p24.14.f.C3=sum(as.numeric(p24.14.f$C3))
p24.14.f.Pr=sum(as.numeric(p24.14.f$Perennial))
p24.14.f.AB=sum(as.numeric(p24.14.f$Annl.Biennial))

p25.14.f.C4=sum(as.numeric(p25.14.f$C4))
p25.14.f.C3=sum(as.numeric(p25.14.f$C3))
p25.14.f.Pr=sum(as.numeric(p25.14.f$Perennial))
p25.14.f.AB=sum(as.numeric(p25.14.f$Annl.Biennial))

p26.14.f.C4=sum(as.numeric(p26.14.f$C4))
p26.14.f.C3=sum(as.numeric(p26.14.f$C3))
p26.14.f.Pr=sum(as.numeric(p26.14.f$Perennial))
p26.14.f.AB=sum(as.numeric(p26.14.f$Annl.Biennial))

p27.14.f.C4=sum(as.numeric(p27.14.f$C4))
p27.14.f.C3=sum(as.numeric(p27.14.f$C3))
p27.14.f.Pr=sum(as.numeric(p27.14.f$Perennial))
p27.14.f.AB=sum(as.numeric(p27.14.f$Annl.Biennial))

p28.14.f.C4=sum(as.numeric(p28.14.f$C4))
p28.14.f.C3=sum(as.numeric(p28.14.f$C3))
p28.14.f.Pr=sum(as.numeric(p28.14.f$Perennial))
p28.14.f.AB=sum(as.numeric(p28.14.f$Annl.Biennial))

p29.14.f.C4=sum(as.numeric(p29.14.f$C4))
p29.14.f.C3=sum(as.numeric(p29.14.f$C3))
p29.14.f.Pr=sum(as.numeric(p29.14.f$Perennial))
p29.14.f.AB=sum(as.numeric(p29.14.f$Annl.Biennial))

p30.14.f.C4=sum(as.numeric(p30.14.f$C4))
p30.14.f.C3=sum(as.numeric(p30.14.f$C3))
p30.14.f.Pr=sum(as.numeric(p30.14.f$Perennial))
p30.14.f.AB=sum(as.numeric(p30.14.f$Annl.Biennial))

p31.14.f.C4=sum(as.numeric(p31.14.f$C4))
p31.14.f.C3=sum(as.numeric(p31.14.f$C3))
p31.14.f.Pr=sum(as.numeric(p31.14.f$Perennial))
p31.14.f.AB=sum(as.numeric(p31.14.f$Annl.Biennial))

p32.14.f.C4=sum(as.numeric(p32.14.f$C4))
p32.14.f.C3=sum(as.numeric(p32.14.f$C3))
p32.14.f.Pr=sum(as.numeric(p32.14.f$Perennial))
p32.14.f.AB=sum(as.numeric(p32.14.f$Annl.Biennial))

p33.14.f.C4=sum(as.numeric(p33.14.f$C4))
p33.14.f.C3=sum(as.numeric(p33.14.f$C3))
p33.14.f.Pr=sum(as.numeric(p33.14.f$Perennial))
p33.14.f.AB=sum(as.numeric(p33.14.f$Annl.Biennial))

p34.14.f.C4=sum(as.numeric(p34.14.f$C4))
p34.14.f.C3=sum(as.numeric(p34.14.f$C3))
p34.14.f.Pr=sum(as.numeric(p34.14.f$Perennial))
p34.14.f.AB=sum(as.numeric(p34.14.f$Annl.Biennial))

p35.14.f.C4=sum(as.numeric(p35.14.f$C4))
p35.14.f.C3=sum(as.numeric(p35.14.f$C3))
p35.14.f.Pr=sum(as.numeric(p35.14.f$Perennial))
p35.14.f.AB=sum(as.numeric(p35.14.f$Annl.Biennial))

p36.14.f.C4=sum(as.numeric(p36.14.f$C4))
p36.14.f.C3=sum(as.numeric(p36.14.f$C3))
p36.14.f.Pr=sum(as.numeric(p36.14.f$Perennial))
p36.14.f.AB=sum(as.numeric(p36.14.f$Annl.Biennial))

#summer use row NA's

```

#Matrix Data Formatting 
```{r}
c4.08f = c(p1.08.f.C4,p2.08.f.C4,p3.08.f.C4,p4.08.f.C4,p5.08.f.C4,p6.08.f.C4,p7.08.f.C4,p8.08.f.C4,p9.08.f.C4,p10.08.f.C4,p11.08.f.C4,p12.08.f.C4,p13.08.f.C4,p14.08.f.C4,p15.08.f.C4,p16.08.f.C4,p17.08.f.C4,p18.08.f.C4,p19.08.f.C4,p20.08.f.C4,p21.08.f.C4,p22.08.f.C4,p23.08.f.C4,p24.08.f.C4,p25.08.f.C4,p26.08.f.C4,p27.08.f.C4,p28.08.f.C4,p29.08.f.C4,p30.08.f.C4,p31.08.f.C4,p32.08.f.C4,p33.08.f.C4,p34.08.f.C4,p35.08.f.C4,p36.08.f.C4)
c4.08s = c(p1.08.s.C4,p2.08.s.C4,p3.08.s.C4,p4.08.s.C4,p5.08.s.C4,p6.08.s.C4,p7.08.s.C4,p8.08.s.C4,p9.08.s.C4,p10.08.s.C4,p11.08.s.C4,p12.08.s.C4,p13.08.s.C4,p14.08.s.C4,p15.08.s.C4,p16.08.s.C4,p17.08.s.C4,p18.08.s.C4,p19.08.s.C4,p20.08.s.C4,p21.08.s.C4,p22.08.s.C4,p23.08.s.C4,p24.08.s.C4,p25.08.s.C4,p26.08.s.C4,p27.08.s.C4,p28.08.s.C4,p29.08.s.C4,p30.08.s.C4,p31.08.s.C4,p32.08.s.C4,p33.08.s.C4,p34.08.s.C4,p35.08.s.C4,p36.08.s.C4)
c4.09f = c(p1.09.f.C4,p2.09.f.C4,p3.09.f.C4,p4.09.f.C4,p5.09.f.C4,p6.09.f.C4,p7.09.f.C4,p8.09.f.C4,p9.09.f.C4,p10.09.f.C4,p11.09.f.C4,p12.09.f.C4,p13.09.f.C4,p14.09.f.C4,p15.09.f.C4,p16.09.f.C4,p17.09.f.C4,p18.09.f.C4,p19.09.f.C4,p20.09.f.C4,p21.09.f.C4,p22.09.f.C4,p23.09.f.C4,p24.09.f.C4,p25.09.f.C4,p26.09.f.C4,p27.09.f.C4,p28.09.f.C4,p29.09.f.C4,p30.09.f.C4,p31.09.f.C4,p32.09.f.C4,p33.09.f.C4,p34.09.f.C4,p35.09.f.C4,p36.09.f.C4)
c4.09s = c(p1.09.s.C4,p2.09.s.C4,p3.09.s.C4,p4.09.s.C4,p5.09.s.C4,p6.09.s.C4,p7.09.s.C4,p8.09.s.C4,p9.09.s.C4,p10.09.s.C4,p11.09.s.C4,p12.09.s.C4,p13.09.s.C4,p14.09.s.C4,p15.09.s.C4,p16.09.s.C4,p17.09.s.C4,p18.09.s.C4,p19.09.s.C4,p20.09.s.C4,p21.09.s.C4,p22.09.s.C4,p23.09.s.C4,p24.09.s.C4,p25.09.s.C4,p26.09.s.C4,p27.09.s.C4,p28.09.s.C4,p29.09.s.C4,p30.09.s.C4,p31.09.s.C4,p32.09.s.C4,p33.09.s.C4,p34.09.s.C4,p35.09.s.C4,p36.09.s.C4)
c4.10f = na.vec
c4.10s = c(p1.10.s.C4,p2.10.s.C4,p3.10.s.C4,p4.10.s.C4,p5.10.s.C4,p6.10.s.C4,p7.10.s.C4,p8.10.s.C4,p9.10.s.C4,p10.10.s.C4,p11.10.s.C4,p12.10.s.C4,p13.10.s.C4,p14.10.s.C4,p15.10.s.C4,p16.10.s.C4,p17.10.s.C4,p18.10.s.C4,p19.10.s.C4,p20.10.s.C4,p21.10.s.C4,p22.10.s.C4,p23.10.s.C4,p24.10.s.C4,p25.10.s.C4,p26.10.s.C4,p27.10.s.C4,p28.10.s.C4,p29.10.s.C4,p30.10.s.C4,p31.10.s.C4,p32.10.s.C4,p33.10.s.C4,p34.10.s.C4,p35.10.s.C4,p36.10.s.C4)
c4.11f = c(p1.11.f.C4,p2.11.f.C4,p3.11.f.C4,p4.11.f.C4,p5.11.f.C4,p6.11.f.C4,p7.11.f.C4,p8.11.f.C4,p9.11.f.C4,p10.11.f.C4,p11.11.f.C4,p12.11.f.C4,p13.11.f.C4,p14.11.f.C4,p15.11.f.C4,p16.11.f.C4,p17.11.f.C4,p18.11.f.C4,p19.11.f.C4,p20.11.f.C4,p21.11.f.C4,p22.11.f.C4,p23.11.f.C4,p24.11.f.C4,p25.11.f.C4,p26.11.f.C4,p27.11.f.C4,p28.11.f.C4,p29.11.f.C4,p30.11.f.C4,p31.11.f.C4,p32.11.f.C4,p33.11.f.C4,p34.11.f.C4,p35.11.f.C4,p36.11.f.C4)
c4.11s = c(p1.11.s.C4,p2.11.s.C4,p3.11.s.C4,p4.11.s.C4,p5.11.s.C4,p6.11.s.C4,p7.11.s.C4,p8.11.s.C4,p9.11.s.C4,p10.11.s.C4,p11.11.s.C4,p12.11.s.C4,p13.11.s.C4,p14.11.s.C4,p15.11.s.C4,p16.11.s.C4,p17.11.s.C4,p18.11.s.C4,p19.11.s.C4,p20.11.s.C4,p21.11.s.C4,p22.11.s.C4,p23.11.s.C4,p24.11.s.C4,p25.11.s.C4,p26.11.s.C4,p27.11.s.C4,p28.11.s.C4,p29.11.s.C4,p30.11.s.C4,p31.11.s.C4,p32.11.s.C4,p33.11.s.C4,p34.11.s.C4,p35.11.s.C4,p36.11.s.C4)
c4.12f = c(p1.12.f.C4,p2.12.f.C4,p3.12.f.C4,p4.12.f.C4,p5.12.f.C4,p6.12.f.C4,p7.12.f.C4,p8.12.f.C4,p9.12.f.C4,p10.12.f.C4,p11.12.f.C4,p12.12.f.C4,p13.12.f.C4,p14.12.f.C4,p15.12.f.C4,p16.12.f.C4,p17.12.f.C4,p18.12.f.C4,p19.12.f.C4,p20.12.f.C4,p21.12.f.C4,p22.12.f.C4,p23.12.f.C4,p24.12.f.C4,p25.12.f.C4,p26.12.f.C4,p27.12.f.C4,p28.12.f.C4,p29.12.f.C4,p30.12.f.C4,p31.12.f.C4,p32.12.f.C4,p33.12.f.C4,p34.12.f.C4,p35.12.f.C4,p36.12.f.C4)
c4.12s = c(p1.12.s.C4,p2.12.s.C4,p3.12.s.C4,p4.12.s.C4,p5.12.s.C4,p6.12.s.C4,p7.12.s.C4,p8.12.s.C4,p9.12.s.C4,p10.12.s.C4,p11.12.s.C4,p12.12.s.C4,p13.12.s.C4,p14.12.s.C4,p15.12.s.C4,p16.12.s.C4,p17.12.s.C4,p18.12.s.C4,p19.12.s.C4,p20.12.s.C4,p21.12.s.C4,p22.12.s.C4,p23.12.s.C4,p24.12.s.C4,p25.12.s.C4,p26.12.s.C4,p27.12.s.C4,p28.12.s.C4,p29.12.s.C4,p30.12.s.C4,p31.12.s.C4,p32.12.s.C4,p33.12.s.C4,p34.12.s.C4,p35.12.s.C4,p36.12.s.C4)
c4.13f = c(p1.13.f.C4,p2.13.f.C4,p3.13.f.C4,p4.13.f.C4,p5.13.f.C4,p6.13.f.C4,p7.13.f.C4,p8.13.f.C4,p9.13.f.C4,p10.13.f.C4,p11.13.f.C4,p12.13.f.C4,p13.13.f.C4,p14.13.f.C4,p15.13.f.C4,p16.13.f.C4,p17.13.f.C4,p18.13.f.C4,p19.13.f.C4,p20.13.f.C4,p21.13.f.C4,p22.13.f.C4,p23.13.f.C4,p24.13.f.C4,p25.13.f.C4,p26.13.f.C4,p27.13.f.C4,p28.13.f.C4,p29.13.f.C4,p30.13.f.C4,p31.13.f.C4,p32.13.f.C4,p33.13.f.C4,p34.13.f.C4,p35.13.f.C4,p36.13.f.C4)
c4.13s = c(p1.13.s.C4,p2.13.s.C4,p3.13.s.C4,p4.13.s.C4,p5.13.s.C4,p6.13.s.C4,p7.13.s.C4,p8.13.s.C4,p9.13.s.C4,p10.13.s.C4,p11.13.s.C4,p12.13.s.C4,p13.13.s.C4,p14.13.s.C4,p15.13.s.C4,p16.13.s.C4,p17.13.s.C4,p18.13.s.C4,p19.13.s.C4,p20.13.s.C4,p21.13.s.C4,p22.13.s.C4,p23.13.s.C4,p24.13.s.C4,p25.13.s.C4,p26.13.s.C4,p27.13.s.C4,p28.13.s.C4,p29.13.s.C4,p30.13.s.C4,p31.13.s.C4,p32.13.s.C4,p33.13.s.C4,p34.13.s.C4,p35.13.s.C4,p36.13.s.C4)
c4.14s = na.vec
c4.14f = c(p1.14.f.C4,p2.14.f.C4,p3.14.f.C4,p4.14.f.C4,p5.14.f.C4,p6.14.f.C4,p7.14.f.C4,p8.14.f.C4,p9.14.f.C4,p10.14.f.C4,p11.14.f.C4,p12.14.f.C4,p13.14.f.C4,p14.14.f.C4,p15.14.f.C4,p16.14.f.C4,p17.14.f.C4,p18.14.f.C4,p19.14.f.C4,p20.14.f.C4,p21.14.f.C4,p22.14.f.C4,p23.14.f.C4,p24.14.f.C4,p25.14.f.C4,p26.14.f.C4,p27.14.f.C4,p28.14.f.C4,p29.14.f.C4,p30.14.f.C4,p31.14.f.C4,p32.14.f.C4,p33.14.f.C4,p34.14.f.C4,p35.14.f.C4,p36.14.f.C4)

##c3
c3.08f = c(p1.08.f.C3,p2.08.f.C3,p3.08.f.C3,p4.08.f.C3,p5.08.f.C3,p6.08.f.C3,p7.08.f.C3,p8.08.f.C3,p9.08.f.C3,p10.08.f.C3,p11.08.f.C3,p12.08.f.C3,p13.08.f.C3,p14.08.f.C3,p15.08.f.C3,p16.08.f.C3,p17.08.f.C3,p18.08.f.C3,p19.08.f.C3,p20.08.f.C3,p21.08.f.C3,p22.08.f.C3,p23.08.f.C3,p24.08.f.C3,p25.08.f.C3,p26.08.f.C3,p27.08.f.C3,p28.08.f.C3,p29.08.f.C3,p30.08.f.C3,p31.08.f.C3,p32.08.f.C3,p33.08.f.C3,p34.08.f.C3,p35.08.f.C3,p36.08.f.C3)
c3.08s = c(p1.08.s.C3,p2.08.s.C3,p3.08.s.C3,p4.08.s.C3,p5.08.s.C3,p6.08.s.C3,p7.08.s.C3,p8.08.s.C3,p9.08.s.C3,p10.08.s.C3,p11.08.s.C3,p12.08.s.C3,p13.08.s.C3,p14.08.s.C3,p15.08.s.C3,p16.08.s.C3,p17.08.s.C3,p18.08.s.C3,p19.08.s.C3,p20.08.s.C3,p21.08.s.C3,p22.08.s.C3,p23.08.s.C3,p24.08.s.C3,p25.08.s.C3,p26.08.s.C3,p27.08.s.C3,p28.08.s.C3,p29.08.s.C3,p30.08.s.C3,p31.08.s.C3,p32.08.s.C3,p33.08.s.C3,p34.08.s.C3,p35.08.s.C3,p36.08.s.C3)
c3.09f = c(p1.09.f.C3,p2.09.f.C3,p3.09.f.C3,p4.09.f.C3,p5.09.f.C3,p6.09.f.C3,p7.09.f.C3,p8.09.f.C3,p9.09.f.C3,p10.09.f.C3,p11.09.f.C3,p12.09.f.C3,p13.09.f.C3,p14.09.f.C3,p15.09.f.C3,p16.09.f.C3,p17.09.f.C3,p18.09.f.C3,p19.09.f.C3,p20.09.f.C3,p21.09.f.C3,p22.09.f.C3,p23.09.f.C3,p24.09.f.C3,p25.09.f.C3,p26.09.f.C3,p27.09.f.C3,p28.09.f.C3,p29.09.f.C3,p30.09.f.C3,p31.09.f.C3,p32.09.f.C3,p33.09.f.C3,p34.09.f.C3,p35.09.f.C3,p36.09.f.C3)
c3.09s = c(p1.09.s.C3,p2.09.s.C3,p3.09.s.C3,p4.09.s.C3,p5.09.s.C3,p6.09.s.C3,p7.09.s.C3,p8.09.s.C3,p9.09.s.C3,p10.09.s.C3,p11.09.s.C3,p12.09.s.C3,p13.09.s.C3,p14.09.s.C3,p15.09.s.C3,p16.09.s.C3,p17.09.s.C3,p18.09.s.C3,p19.09.s.C3,p20.09.s.C3,p21.09.s.C3,p22.09.s.C3,p23.09.s.C3,p24.09.s.C3,p25.09.s.C3,p26.09.s.C3,p27.09.s.C3,p28.09.s.C3,p29.09.s.C3,p30.09.s.C3,p31.09.s.C3,p32.09.s.C3,p33.09.s.C3,p34.09.s.C3,p35.09.s.C3,p36.09.s.C3)
c3.10f = na.vec
c3.10s = c(p1.10.s.C3,p2.10.s.C3,p3.10.s.C3,p4.10.s.C3,p5.10.s.C3,p6.10.s.C3,p7.10.s.C3,p8.10.s.C3,p9.10.s.C3,p10.10.s.C3,p11.10.s.C3,p12.10.s.C3,p13.10.s.C3,p14.10.s.C3,p15.10.s.C3,p16.10.s.C3,p17.10.s.C3,p18.10.s.C3,p19.10.s.C3,p20.10.s.C3,p21.10.s.C3,p22.10.s.C3,p23.10.s.C3,p24.10.s.C3,p25.10.s.C3,p26.10.s.C3,p27.10.s.C3,p28.10.s.C3,p29.10.s.C3,p30.10.s.C3,p31.10.s.C3,p32.10.s.C3,p33.10.s.C3,p34.10.s.C3,p35.10.s.C3,p36.10.s.C3)
c3.11f = c(p1.11.f.C3,p2.11.f.C3,p3.11.f.C3,p4.11.f.C3,p5.11.f.C3,p6.11.f.C3,p7.11.f.C3,p8.11.f.C3,p9.11.f.C3,p10.11.f.C3,p11.11.f.C3,p12.11.f.C3,p13.11.f.C3,p14.11.f.C3,p15.11.f.C3,p16.11.f.C3,p17.11.f.C3,p18.11.f.C3,p19.11.f.C3,p20.11.f.C3,p21.11.f.C3,p22.11.f.C3,p23.11.f.C3,p24.11.f.C3,p25.11.f.C3,p26.11.f.C3,p27.11.f.C3,p28.11.f.C3,p29.11.f.C3,p30.11.f.C3,p31.11.f.C3,p32.11.f.C3,p33.11.f.C3,p34.11.f.C3,p35.11.f.C3,p36.11.f.C3)
c3.11s = c(p1.11.s.C3,p2.11.s.C3,p3.11.s.C3,p4.11.s.C3,p5.11.s.C3,p6.11.s.C3,p7.11.s.C3,p8.11.s.C3,p9.11.s.C3,p10.11.s.C3,p11.11.s.C3,p12.11.s.C3,p13.11.s.C3,p14.11.s.C3,p15.11.s.C3,p16.11.s.C3,p17.11.s.C3,p18.11.s.C3,p19.11.s.C3,p20.11.s.C3,p21.11.s.C3,p22.11.s.C3,p23.11.s.C3,p24.11.s.C3,p25.11.s.C3,p26.11.s.C3,p27.11.s.C3,p28.11.s.C3,p29.11.s.C3,p30.11.s.C3,p31.11.s.C3,p32.11.s.C3,p33.11.s.C3,p34.11.s.C3,p35.11.s.C3,p36.11.s.C3)
c3.12f = c(p1.12.f.C3,p2.12.f.C3,p3.12.f.C3,p4.12.f.C3,p5.12.f.C3,p6.12.f.C3,p7.12.f.C3,p8.12.f.C3,p9.12.f.C3,p10.12.f.C3,p11.12.f.C3,p12.12.f.C3,p13.12.f.C3,p14.12.f.C3,p15.12.f.C3,p16.12.f.C3,p17.12.f.C3,p18.12.f.C3,p19.12.f.C3,p20.12.f.C3,p21.12.f.C3,p22.12.f.C3,p23.12.f.C3,p24.12.f.C3,p25.12.f.C3,p26.12.f.C3,p27.12.f.C3,p28.12.f.C3,p29.12.f.C3,p30.12.f.C3,p31.12.f.C3,p32.12.f.C3,p33.12.f.C3,p34.12.f.C3,p35.12.f.C3,p36.12.f.C3)
c3.12s = c(p1.12.s.C3,p2.12.s.C3,p3.12.s.C3,p4.12.s.C3,p5.12.s.C3,p6.12.s.C3,p7.12.s.C3,p8.12.s.C3,p9.12.s.C3,p10.12.s.C3,p11.12.s.C3,p12.12.s.C3,p13.12.s.C3,p14.12.s.C3,p15.12.s.C3,p16.12.s.C3,p17.12.s.C3,p18.12.s.C3,p19.12.s.C3,p20.12.s.C3,p21.12.s.C3,p22.12.s.C3,p23.12.s.C3,p24.12.s.C3,p25.12.s.C3,p26.12.s.C3,p27.12.s.C3,p28.12.s.C3,p29.12.s.C3,p30.12.s.C3,p31.12.s.C3,p32.12.s.C3,p33.12.s.C3,p34.12.s.C3,p35.12.s.C3,p36.12.s.C3)
c3.13f = c(p1.13.f.C3,p2.13.f.C3,p3.13.f.C3,p4.13.f.C3,p5.13.f.C3,p6.13.f.C3,p7.13.f.C3,p8.13.f.C3,p9.13.f.C3,p10.13.f.C3,p11.13.f.C3,p12.13.f.C3,p13.13.f.C3,p14.13.f.C3,p15.13.f.C3,p16.13.f.C3,p17.13.f.C3,p18.13.f.C3,p19.13.f.C3,p20.13.f.C3,p21.13.f.C3,p22.13.f.C3,p23.13.f.C3,p24.13.f.C3,p25.13.f.C3,p26.13.f.C3,p27.13.f.C3,p28.13.f.C3,p29.13.f.C3,p30.13.f.C3,p31.13.f.C3,p32.13.f.C3,p33.13.f.C3,p34.13.f.C3,p35.13.f.C3,p36.13.f.C3)
c3.13s = c(p1.13.s.C3,p2.13.s.C3,p3.13.s.C3,p4.13.s.C3,p5.13.s.C3,p6.13.s.C3,p7.13.s.C3,p8.13.s.C3,p9.13.s.C3,p10.13.s.C3,p11.13.s.C3,p12.13.s.C3,p13.13.s.C3,p14.13.s.C3,p15.13.s.C3,p16.13.s.C3,p17.13.s.C3,p18.13.s.C3,p19.13.s.C3,p20.13.s.C3,p21.13.s.C3,p22.13.s.C3,p23.13.s.C3,p24.13.s.C3,p25.13.s.C3,p26.13.s.C3,p27.13.s.C3,p28.13.s.C3,p29.13.s.C3,p30.13.s.C3,p31.13.s.C3,p32.13.s.C3,p33.13.s.C3,p34.13.s.C3,p35.13.s.C3,p36.13.s.C3)
c3.14s = na.vec
c3.14f = c(p1.14.f.C3,p2.14.f.C3,p3.14.f.C3,p4.14.f.C3,p5.14.f.C3,p6.14.f.C3,p7.14.f.C3,p8.14.f.C3,p9.14.f.C3,p10.14.f.C3,p11.14.f.C3,p12.14.f.C3,p13.14.f.C3,p14.14.f.C3,p15.14.f.C3,p16.14.f.C3,p17.14.f.C3,p18.14.f.C3,p19.14.f.C3,p20.14.f.C3,p21.14.f.C3,p22.14.f.C3,p23.14.f.C3,p24.14.f.C3,p25.14.f.C3,p26.14.f.C3,p27.14.f.C3,p28.14.f.C3,p29.14.f.C3,p30.14.f.C3,p31.14.f.C3,p32.14.f.C3,p33.14.f.C3,p34.14.f.C3,p35.14.f.C3,p36.14.f.C3)


```


#Matrix Filling/Creation
```{r}
c4.matrix = matrix(c(c4.08s,c4.08f,c4.09s,c4.09f,c4.10s,c4.10f,c4.11s,c4.11f,c4.12s,c4.12f,c4.13s,c4.13f,c4.14s,c4.14f),nrow=14,ncol=36,byrow=TRUE)
dimnames(c4.matrix) = list(c("08S", "08F", "09S", "09F", "10S", "10F", "11S", "11F", "12S", "12F", "13S", "13F", "14S", "14F"),c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25,26,27,28,29,30,31,32,33,34,35,36))

c3.matrix = matrix(c(c3.08s,c3.08f,c3.09s,c3.09f,c3.10s,c3.10f,c3.11s,c3.11f,c3.12s,c3.12f,c3.13s,c3.13f,c3.14s,c3.14f),nrow=14,ncol=36,byrow=TRUE)
dimnames(c3.matrix) = list(c("08S", "08F", "09S", "09F", "10S", "10F", "11S", "11F", "12S", "12F", "13S", "13F", "14S", "14F"),c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25,26,27,28,29,30,31,32,33,34,35,36))

dry = c(1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,0,0,0,0,0,0,0,0,1,1,1,1)
wet = c(0,0,0,0,0,0,0,0,1,1,1,1,0,0,0,0,1,1,1,1,0,0,0,0,1,1,1,1,0,0,0,0,0,0,0,0)
#treatment <- bdry*dry + bwet*wet
```

```{r}
c4.fit.norm = "model{
#priors
r ~ dnorm(0,0.5)
tau0 ~ dgamma(0.5,0.5)
tau1 ~ dgamma(0.5,0.5)
bdry ~ dnorm(0,0.5)
bwet ~ dnorm(0,0.5)
for (i in 1:36) {
    x[1,i]~ dlnorm(0,0.01)
}

sigma ~ dgamma(0.05,0.05)
#process
  
for (i  in 1:36){     # 36 plots
  for (t in 2:n) {    #years process model
    u[t,i] <- log(x[t-1,i]) + r + bdry*dry[i] + bwet*wet[i]
    x[t,i] ~ dlnorm(u[t,i],sigma)
  }
  for (t in 1:n){       #years data model
    tau <- tau0 + tau1
    y[t,i] ~ dnorm(x[t,i],tau)
    py[t,i]~ dnorm(x[t,i],tau)
}
}
}
"

init.cond1 <- list()
init.cond1[[1]] = list("r"=0.1,"sigma"=0.05,"tau"=0.5)
init.cond1[[2]] = list("r"=1,"sigma"=0.1,"tau"=0.1)
init.cond1[[3]] = list("r"=0.01,"sigma"=0.01,"tau"=0.01)


data = list(n=14,y=c4.matrix,dry=dry,wet=wet)
init = init.cond1
  ## compile JAGS model
  c4.j.model <- jags.model(file = textConnection(c4.fit.norm),
                           data = data,
                           inits = init,
                           n.chains = 3)
  ## burn-in
  c4   <- coda.samples (model = c4.j.model,
                              variable.names = c("r","x","py","sigma","tau","bwet","bdry"),
                              n.iter = 2000)

c4mcmc <- c4
c4mcmc.data <- as.data.frame(as.matrix(c4mcmc))

c4grep.x <- grep("x",names(c4mcmc.data))
c4X <- apply(c4mcmc.data[,c4grep.x],2,quantile,c(0.025,0.5,0.975))
c4grep.py <- grep("py",names(c4mcmc.data))
c4PY <- apply(c4mcmc.data[,c4grep.py],2,quantile,c(0.025,0.5,0.975))

no.year= c(1,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14)
correction = 1
plotnumber = seq(from=1,to=36,by=1)

for(i in 1:36) {

#plot
plot(c4.matrix[,i],main = plotnumber[i] ,ylab="biomass", type="b")

#points((c4X[2,(no.year[i]*(i-1)+correction[i]):(14*i)]),col=2)  #50

#CI's
lines((c4X[1,(no.year[i]*(i-1)+correction):(14*i)]), col=5,type="b") #2.5%
lines((c4X[2,(no.year[i]*(i-1)+correction):(14*i)]),col=2)  #50
lines((c4X[3,(no.year[i]*(i-1)+correction):(14*i)]), col=5,type="b")  #97.5%

#Pi's
lines((c4PY[1,(no.year[i]*(i-1)+correction):(14*i)]), col=3,type="b") #2.5%
lines((c4PY[2,(no.year[i]*(i-1)+correction):(14*i)]),col=2,type="b")  #50
lines((c4PY[3,(no.year[i]*(i-1)+correction):(14*i)]), col=3,type="b")  #97.5%

}

```

```{r}
c3.fit.norm = "model{
#priors
r ~ dnorm(0,0.5)
tau ~ dgamma(0.5,0.5)
for (i in 1:36) {
    x[1,i]~ dlnorm(0,0.01)
}

sigma ~ dgamma(0.05,0.05)
#process
  
for (i  in 1:36){     # 36 plots
  for (t in 2:n) {    #years process model
    u[t,i] <- log(x[t-1,i]) - r 
    x[t,i] ~ dlnorm(u[t,i],sigma)
  }
  for (t in 1:n){       #years data model
    y[t,i] ~ dnorm(x[t,i],tau)
    py[t,i]~ dnorm(x[t,i],tau)
}
}
}
"

init.cond2 <- list()
init.cond2[[1]] = list("r"=0.1,"sigma"=0.5,"tau"=0.5)
init.cond2[[2]] = list("r"=1,"sigma"=0.1,"tau"=0.1)
init.cond2[[3]] = list("r"=0.01,"sigma"=0.01,"tau"=0.01)


data2 = list(n=14,y=c3.matrix)
init2 = init.cond2
  ## compile JAGS model
  c3.j.model <- jags.model(file = textConnection(c3.fit.norm),
                           data = data2,
                           inits = init2,
                           n.chains = 3)
  ## burn-in
  c3   <- coda.samples (model = c3.j.model,
                              variable.names = c("r","x","py","sigma","tau"),
                              n.iter = 2000)

c3mcmc <- c3
c3mcmc.data <- as.data.frame(as.matrix(c3mcmc))

c3grep.x <- grep("x",names(c3mcmc.data))
c3X <- apply(c3mcmc.data[,c3grep.x],2,quantile,c(0.025,0.5,0.975))
c3grep.py <- grep("py",names(c3mcmc.data))
c3PY <- apply(c3mcmc.data[,c3grep.py],2,quantile,c(0.025,0.5,0.975))

for(i in 1:36) {

#plot
plot(c3.matrix[,i],main = plotnumber[i] , type="b")

#points((c3X[2,(no.year[i]*(i-1)+correction[i]):(14*i)]),col=2)  #50

#CI's
lines((c3X[1,(no.year[i]*(i-1)+correction):(14*i)]), col=5,type="b") #2.5%
lines((c3X[2,(no.year[i]*(i-1)+correction):(14*i)]),col=2)  #50
lines((c3X[3,(no.year[i]*(i-1)+correction):(14*i)]), col=5,type="b")  #97.5%

#Pi's
lines((c3PY[1,(no.year[i]*(i-1)+correction):(14*i)]), col=3,type="b") #2.5%
lines((c3PY[2,(no.year[i]*(i-1)+correction):(14*i)]),col=2,type="b")  #50
lines((c3PY[3,(no.year[i]*(i-1)+correction):(14*i)]), col=3,type="b")  #97.5%

}

#densityplots

densityplot(c3mcmc.data$"r")
densityplot(c3mcmc.data$"tau")
```

```
#heteroskedastic errors + treatments
```{r}
c4.fit.norm = "model{
#priors
r ~ dnorm(0,0.5)
tau0 ~ dgamma(1.5,1.5)
tau1 ~ dgamma(1.5,1.5)
bdry ~ dnorm(0,0.5)
bwet ~ dnorm(0,0.5)
for (i in 1:36) {
    x[1,i]~ dlnorm(0,0.01)
}

sigma ~ dgamma(0.05,0.05)
#process
  
for (i  in 1:36){     # 36 plots
  for (t in 2:n) {    #years process model
    u[t,i] <- log(x[t-1,i]) + r + bdry*dry[i] + bwet*wet[i]
    x[t,i] ~ dlnorm(u[t,i],sigma)
  }
  for (t in 1:n){       #years data model
    tau[t,i] <- 1/(tau0 + tau1*x[t,i])^2
    y[t,i] ~ dnorm(x[t,i],tau[t,i])
    py[t,i]~ dnorm(x[t,i],tau[t,i])
}
}
}
"

init.cond1 <- list()
init.cond1[[1]] = list("r"=0.1,"sigma"=0.05,"tau0"=0.5)
init.cond1[[2]] = list("r"=1,"sigma"=0.1,"tau0"=0.1)
init.cond1[[3]] = list("r"=0.01,"sigma"=0.01,"tau0"=0.01)


data = list(n=14,y=c4.matrix,dry=dry,wet=wet)
init = init.cond1
  ## compile JAGS model
  c4.j.model <- jags.model(file = textConnection(c4.fit.norm),
                           data = data,
                           inits = init,
                           n.chains = 3)
  ## burn-in
  c4   <- coda.samples (model = c4.j.model,
                              variable.names = c("r","x","py","sigma","bwet","bdry","tau0","tau1"),
                              n.iter = 2000)

c4mcmc <- c4
c4mcmc.data <- as.data.frame(as.matrix(c4mcmc))

c4grep.x <- grep("x",names(c4mcmc.data))
c4X <- apply(c4mcmc.data[,c4grep.x],2,quantile,c(0.025,0.5,0.975))
c4grep.py <- grep("py",names(c4mcmc.data))
c4PY <- apply(c4mcmc.data[,c4grep.py],2,quantile,c(0.025,0.5,0.975))

no.year= c(1,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14)
correction = 1
plotnumber = seq(from=1,to=36,by=1)

for(i in 1:36) {

#plot
plot(c4.matrix[,i],main = plotnumber[i] ,ylab="biomass", type="b")

#points((c4X[2,(no.year[i]*(i-1)+correction[i]):(14*i)]),col=2)  #50

#CI's
lines((c4X[1,(no.year[i]*(i-1)+correction):(14*i)]), col=5,type="b") #2.5%
lines((c4X[2,(no.year[i]*(i-1)+correction):(14*i)]),col=2)  #50
lines((c4X[3,(no.year[i]*(i-1)+correction):(14*i)]), col=5,type="b")  #97.5%

#Pi's
lines((c4PY[1,(no.year[i]*(i-1)+correction):(14*i)]), col=3,type="b") #2.5%
lines((c4PY[2,(no.year[i]*(i-1)+correction):(14*i)]),col=2,type="b")  #50
lines((c4PY[3,(no.year[i]*(i-1)+correction):(14*i)]), col=3,type="b")  #97.5%

}

```

#heteroerrors+seasons+treatment
```{r}
c4.fit.norm = "model{
#priors
r ~ dnorm(0,0.5)
tau0 ~ dgamma(1.5,1.5)
tau1 ~ dgamma(1.5,1.5)
bdry ~ dnorm(0,0.5)
bwet ~ dnorm(0,0.5)
for (i in 1:36) {
    x[1,i]~ dlnorm(0,0.01)
}

sigma ~ dgamma(0.05,0.05)
#process
  
for (i  in 1:36){     # 36 plots
  for (t in 2:n) {    #years process model
    u[t,i] <- log(x[t-1,i]) + r + bdry*dry[i] + bwet*wet[i]
    x[t,i] ~ dlnorm(u[t,i],sigma)
  }
  for (t in 1:n){       #years data model
    tau[t,i] <- 1/(tau0 + tau1*x[t,i])^2
    y[t,i] ~ dnorm(x[t,i],tau[t,i])
    py[t,i]~ dnorm(x[t,i],tau[t,i])
}
}
}
"

init.cond1 <- list()
init.cond1[[1]] = list("r"=0.1,"sigma"=0.05,"tau0"=0.5)
init.cond1[[2]] = list("r"=1,"sigma"=0.1,"tau0"=0.1)
init.cond1[[3]] = list("r"=0.01,"sigma"=0.01,"tau0"=0.01)


data = list(n=14,y=c4.matrix,dry=dry,wet=wet)
init = init.cond1
  ## compile JAGS model
  c4.j.model <- jags.model(file = textConnection(c4.fit.norm),
                           data = data,
                           inits = init,
                           n.chains = 3)
  ## burn-in
  c4   <- coda.samples (model = c4.j.model,
                              variable.names = c("r","x","py","sigma","bwet","bdry","tau0","tau1"),
                              n.iter = 2000)

c4mcmc <- c4
c4mcmc.data <- as.data.frame(as.matrix(c4mcmc))

c4grep.x <- grep("x",names(c4mcmc.data))
c4X <- apply(c4mcmc.data[,c4grep.x],2,quantile,c(0.025,0.5,0.975))
c4grep.py <- grep("py",names(c4mcmc.data))
c4PY <- apply(c4mcmc.data[,c4grep.py],2,quantile,c(0.025,0.5,0.975))

no.year= c(1,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14,14)
correction = 1
plotnumber = seq(from=1,to=36,by=1)

for(i in 1:36) {

#plot
plot(c4.matrix[,i],main = plotnumber[i] ,ylab="biomass", type="b")

#points((c4X[2,(no.year[i]*(i-1)+correction[i]):(14*i)]),col=2)  #50

#CI's
lines((c4X[1,(no.year[i]*(i-1)+correction):(14*i)]), col=5,type="b") #2.5%
lines((c4X[2,(no.year[i]*(i-1)+correction):(14*i)]),col=2)  #50
lines((c4X[3,(no.year[i]*(i-1)+correction):(14*i)]), col=5,type="b")  #97.5%

#Pi's
lines((c4PY[1,(no.year[i]*(i-1)+correction):(14*i)]), col=3,type="b") #2.5%
lines((c4PY[2,(no.year[i]*(i-1)+correction):(14*i)]),col=2,type="b")  #50
lines((c4PY[3,(no.year[i]*(i-1)+correction):(14*i)]), col=3,type="b")  #97.5%

}

```
