---
title: "TotalBiomass"
author: "Anthony Gardella"
date: "Sunday, March 15, 2015"
output: html_document
---

# Data Processing
```{r}
dat.tree=read.csv("2011-13 Tree Biomass.csv", header=TRUE)
colnames(dat.tree)<-c("ID","species","Plot","subplot","height","d10","init.stem.weight","bag","tot.stem.mass","leaf.mass","year","tot.mass","tot.branch.mass")
totalmass=as.numeric(dat.tree$tot.mass)
dat.herb=read.csv("HerbaceousBiomass.csv",header=TRUE)
years=c("08S", "08F", "09S", "09F", "10S", "10F", "11S", "11F", "12S", "12F", "13S", "13F", "14S", "14F")

```

#2008 subsetted by season
```{r}
## 2008 year subsetted by season 
dat.08=dat.herb[dat.herb$Year==2008,]
dat.08.fall=dat.08[dat.08$Season=="Fall",]
dat.08.summ=dat.08[dat.08$Season=="Summer",]
dat.08.fall.m=as.numeric(dat.08.fall$Total.Mass)
dat.08.summ.m=as.numeric(dat.08.summ$Total.Mass)
#Means,95% intervals, standarad deviation, 
dat.08.fall.95=quantile(dat.08.fall.m,c(.05,.95))
dat.08.summ.95=quantile(dat.08.summ.m,c(.05,.95))
dat.08.fall.mean=mean(dat.08.fall.m)
dat.08.summ.mean=mean(dat.08.summ.m)
dat.08.fall.sd=sd(dat.08.fall.m)
dat.08.summ.sd=sd(dat.08.summ.m)
```

#2008 season subsetted by treatment 
```{r}
## Seasonal subsetted by treatment
wt.08.f=dat.08.fall[dat.08.fall$Treatment== "W",]
wt.08.s=dat.08.summ[dat.08.summ$Treatment== "W",]
dr.08.f=dat.08.fall[dat.08.fall$Treatment== "D",]
dr.08.s=dat.08.summ[dat.08.summ$Treatment== "D",]
ab.08.f=dat.08.fall[dat.08.fall$Treatment== "A",]
ab.08.s=dat.08.summ[dat.08.summ$Treatment== "A",]

##Treatment subsetted by mass
wt.08.f.m=as.numeric(wt.08.f$Total.Mass) 
wt.08.s.m=as.numeric(wt.08.s$Total.Mass)
dr.08.f.m=as.numeric(dr.08.f$Total.Mass)
dr.08.s.m=as.numeric(dr.08.s$Total.Mass)
ab.08.f.m=as.numeric(ab.08.f$Total.Mass)
ab.08.s.m=as.numeric(ab.08.s$Total.Mass)

#Summary data
w.08.fall.95=quantile(wt.08.f.m,c(.05,.95),na.rm=TRUE)
w.08.summ.95=quantile(wt.08.s.m,c(.05,.95),na.rm=TRUE)
w.08.fall.mean=mean(wt.08.f.m,na.rm=TRUE)
w.08.summ.mean=mean(wt.08.s.m,na.rm=TRUE)
w.08.fall.sd=sd(wt.08.f.m,na.rm=TRUE)
w.08.summ.sd=sd(wt.08.s.m,na.rm=TRUE)

a.08.fall.95=quantile(ab.08.f.m,c(.05,.95),na.rm=TRUE)
a.08.summ.95=quantile(ab.08.s.m,c(.05,.95),na.rm=TRUE)
a.08.fall.mean=mean(ab.08.f.m,na.rm=TRUE)
a.08.summ.mean=mean(ab.08.s.m,na.rm=TRUE)
a.08.fall.sd=sd(ab.08.f.m,na.rm=TRUE)
a.08.summ.sd=sd(ab.08.s.m,na.rm=TRUE)

d.08.fall.95=quantile(dr.08.f.m,c(.05,.95),na.rm=TRUE)
d.08.summ.95=quantile(dr.08.s.m,c(.05,.95),na.rm=TRUE)
d.08.fall.mean=mean(dr.08.f.m,na.rm=TRUE)
d.08.summ.mean=mean(dr.08.s.m,na.rm=TRUE)
d.08.fall.sd=sd(dr.08.f.m,na.rm=TRUE)
d.08.summ.sd=sd(dr.08.s.m,na.rm=TRUE)
```

##2008 seasons subsetted by plot
```{r}
## Seasonal subsetted by plot
p1.08.f=dat.08.fall[dat.08.fall$Plot %in% 1,]
p2.08.f=dat.08.fall[dat.08.fall$Plot %in% 2,]
p3.08.f=dat.08.fall[dat.08.fall$Plot %in% 3,]
p4.08.f=dat.08.fall[dat.08.fall$Plot %in% 4,]
p5.08.f=dat.08.fall[dat.08.fall$Plot %in% 5,]
p6.08.f=dat.08.fall[dat.08.fall$Plot %in% 6,]
p7.08.f=dat.08.fall[dat.08.fall$Plot %in% 7,]
p8.08.f=dat.08.fall[dat.08.fall$Plot %in% 8,]
p9.08.f=dat.08.fall[dat.08.fall$Plot %in% 9,]
p10.08.f=dat.08.fall[dat.08.fall$Plot %in% 10,]
p11.08.f=dat.08.fall[dat.08.fall$Plot %in% 11,]
p12.08.f=dat.08.fall[dat.08.fall$Plot %in% 12,]
p13.08.f=dat.08.fall[dat.08.fall$Plot %in% 13,]
p14.08.f=dat.08.fall[dat.08.fall$Plot %in% 14,]
p15.08.f=dat.08.fall[dat.08.fall$Plot %in% 15,]
p16.08.f=dat.08.fall[dat.08.fall$Plot %in% 16,]
p17.08.f=dat.08.fall[dat.08.fall$Plot %in% 17,]
p18.08.f=dat.08.fall[dat.08.fall$Plot %in% 18,]
p19.08.f=dat.08.fall[dat.08.fall$Plot %in% 19,]
p20.08.f=dat.08.fall[dat.08.fall$Plot %in% 20,]
p21.08.f=dat.08.fall[dat.08.fall$Plot %in% 21,]
p22.08.f=dat.08.fall[dat.08.fall$Plot %in% 22,]
p23.08.f=dat.08.fall[dat.08.fall$Plot %in% 23,]
p24.08.f=dat.08.fall[dat.08.fall$Plot %in% 24,]
p25.08.f=dat.08.fall[dat.08.fall$Plot %in% 25,]
p26.08.f=dat.08.fall[dat.08.fall$Plot %in% 26,]
p27.08.f=dat.08.fall[dat.08.fall$Plot %in% 27,]
p28.08.f=dat.08.fall[dat.08.fall$Plot %in% 28,]
p29.08.f=dat.08.fall[dat.08.fall$Plot %in% 29,]
p30.08.f=dat.08.fall[dat.08.fall$Plot %in% 30,]
p31.08.f=dat.08.fall[dat.08.fall$Plot %in% 31,]
p32.08.f=dat.08.fall[dat.08.fall$Plot %in% 32,]
p33.08.f=dat.08.fall[dat.08.fall$Plot %in% 33,]
p34.08.f=dat.08.fall[dat.08.fall$Plot %in% 34,]
p35.08.f=dat.08.fall[dat.08.fall$Plot %in% 35,]
p36.08.f=dat.08.fall[dat.08.fall$Plot %in% 36,]

p1.08.s=dat.08.summ[dat.08.summ$Plot %in% 1,]
p2.08.s=dat.08.summ[dat.08.summ$Plot %in% 2,]
p3.08.s=dat.08.summ[dat.08.summ$Plot %in% 3,]
p4.08.s=dat.08.summ[dat.08.summ$Plot %in% 4,]
p5.08.s=dat.08.summ[dat.08.summ$Plot %in% 5,]
p6.08.s=dat.08.summ[dat.08.summ$Plot %in% 6,]
p7.08.s=dat.08.summ[dat.08.summ$Plot %in% 7,]
p8.08.s=dat.08.summ[dat.08.summ$Plot %in% 8,]
p9.08.s=dat.08.summ[dat.08.summ$Plot %in% 9,]
p10.08.s=dat.08.summ[dat.08.summ$Plot %in% 10,]
p11.08.s=dat.08.summ[dat.08.summ$Plot %in% 11,]
p12.08.s=dat.08.summ[dat.08.summ$Plot %in% 12,]
p13.08.s=dat.08.summ[dat.08.summ$Plot %in% 13,]
p14.08.s=dat.08.summ[dat.08.summ$Plot %in% 14,]
p15.08.s=dat.08.summ[dat.08.summ$Plot %in% 15,]
p16.08.s=dat.08.summ[dat.08.summ$Plot %in% 16,]
p17.08.s=dat.08.summ[dat.08.summ$Plot %in% 17,]
p18.08.s=dat.08.summ[dat.08.summ$Plot %in% 18,]
p19.08.s=dat.08.summ[dat.08.summ$Plot %in% 19,]
p20.08.s=dat.08.summ[dat.08.summ$Plot %in% 20,]
p21.08.s=dat.08.summ[dat.08.summ$Plot %in% 21,]
p22.08.s=dat.08.summ[dat.08.summ$Plot %in% 22,]
p23.08.s=dat.08.summ[dat.08.summ$Plot %in% 23,]
p24.08.s=dat.08.summ[dat.08.summ$Plot %in% 24,]
p25.08.s=dat.08.summ[dat.08.summ$Plot %in% 25,]
p26.08.s=dat.08.summ[dat.08.summ$Plot %in% 26,]
p27.08.s=dat.08.summ[dat.08.summ$Plot %in% 27,]
p28.08.s=dat.08.summ[dat.08.summ$Plot %in% 28,]
p29.08.s=dat.08.summ[dat.08.summ$Plot %in% 29,]
p30.08.s=dat.08.summ[dat.08.summ$Plot %in% 30,]
p31.08.s=dat.08.summ[dat.08.summ$Plot %in% 31,]
p32.08.s=dat.08.summ[dat.08.summ$Plot %in% 32,]
p33.08.s=dat.08.summ[dat.08.summ$Plot %in% 33,]
p34.08.s=dat.08.summ[dat.08.summ$Plot %in% 34,]
p35.08.s=dat.08.summ[dat.08.summ$Plot %in% 35,]
p36.08.s=dat.08.summ[dat.08.summ$Plot %in% 36,]

#Plot subsetted by mass
p1.08.f.m=sum(as.numeric(p1.08.f$Total.Mass))
p2.08.f.m=sum(as.numeric(p2.08.f$Total.Mass))
p3.08.f.m=sum(as.numeric(p3.08.f$Total.Mass))
p4.08.f.m=sum(as.numeric(p4.08.f$Total.Mass))
p5.08.f.m=sum(as.numeric(p5.08.f$Total.Mass))
p6.08.f.m=sum(as.numeric(p6.08.f$Total.Mass))
p7.08.f.m=sum(as.numeric(p7.08.f$Total.Mass))
p8.08.f.m=sum(as.numeric(p8.08.f$Total.Mass))
p9.08.f.m=sum(as.numeric(p9.08.f$Total.Mass))
p10.08.f.m=sum(as.numeric(p10.08.f$Total.Mass))
p11.08.f.m=sum(as.numeric(p11.08.f$Total.Mass))
p12.08.f.m=sum(as.numeric(p12.08.f$Total.Mass))
p13.08.f.m=sum(as.numeric(p13.08.f$Total.Mass))
p14.08.f.m=sum(as.numeric(p14.08.f$Total.Mass))
p15.08.f.m=sum(as.numeric(p15.08.f$Total.Mass))
p16.08.f.m=sum(as.numeric(p16.08.f$Total.Mass))
p17.08.f.m=sum(as.numeric(p17.08.f$Total.Mass))
p18.08.f.m=sum(as.numeric(p18.08.f$Total.Mass))
p19.08.f.m=sum(as.numeric(p19.08.f$Total.Mass))
p20.08.f.m=sum(as.numeric(p20.08.f$Total.Mass))
p21.08.f.m=sum(as.numeric(p21.08.f$Total.Mass))
p22.08.f.m=sum(as.numeric(p22.08.f$Total.Mass))
p23.08.f.m=sum(as.numeric(p23.08.f$Total.Mass))
p24.08.f.m=sum(as.numeric(p24.08.f$Total.Mass))
p25.08.f.m=sum(as.numeric(p25.08.f$Total.Mass))
p26.08.f.m=sum(as.numeric(p26.08.f$Total.Mass))
p27.08.f.m=sum(as.numeric(p27.08.f$Total.Mass))
p28.08.f.m=sum(as.numeric(p28.08.f$Total.Mass))
p29.08.f.m=sum(as.numeric(p29.08.f$Total.Mass))
p30.08.f.m=sum(as.numeric(p30.08.f$Total.Mass))
p31.08.f.m=sum(as.numeric(p31.08.f$Total.Mass))
p32.08.f.m=sum(as.numeric(p32.08.f$Total.Mass))
p33.08.f.m=sum(as.numeric(p33.08.f$Total.Mass))
p34.08.f.m=sum(as.numeric(p34.08.f$Total.Mass))
p35.08.f.m=sum(as.numeric(p35.08.f$Total.Mass))
p36.08.f.m=sum(as.numeric(p36.08.f$Total.Mass))

p1.08.s.m=sum(as.numeric(p1.08.s$Total.Mass))
p2.08.s.m=sum(as.numeric(p2.08.s$Total.Mass))
p3.08.s.m=sum(as.numeric(p3.08.s$Total.Mass))
p4.08.s.m=sum(as.numeric(p4.08.s$Total.Mass))
p5.08.s.m=sum(as.numeric(p5.08.s$Total.Mass))
p6.08.s.m=sum(as.numeric(p6.08.s$Total.Mass))
p7.08.s.m=sum(as.numeric(p7.08.s$Total.Mass))
p8.08.s.m=sum(as.numeric(p8.08.s$Total.Mass))
p9.08.s.m=sum(as.numeric(p9.08.s$Total.Mass))
p10.08.s.m=sum(as.numeric(p10.08.s$Total.Mass))
p11.08.s.m=sum(as.numeric(p11.08.s$Total.Mass))
p12.08.s.m=sum(as.numeric(p12.08.s$Total.Mass))
p13.08.s.m=sum(as.numeric(p13.08.s$Total.Mass))
p14.08.s.m=sum(as.numeric(p14.08.s$Total.Mass))
p15.08.s.m=sum(as.numeric(p15.08.s$Total.Mass))
p16.08.s.m=sum(as.numeric(p16.08.s$Total.Mass))
p17.08.s.m=sum(as.numeric(p17.08.s$Total.Mass))
p18.08.s.m=sum(as.numeric(p18.08.s$Total.Mass))
p19.08.s.m=sum(as.numeric(p19.08.s$Total.Mass))
p20.08.s.m=sum(as.numeric(p20.08.s$Total.Mass))
p21.08.s.m=sum(as.numeric(p21.08.s$Total.Mass))
p22.08.s.m=sum(as.numeric(p22.08.s$Total.Mass))
p23.08.s.m=sum(as.numeric(p23.08.s$Total.Mass))
p24.08.s.m=sum(as.numeric(p24.08.s$Total.Mass))
p25.08.s.m=sum(as.numeric(p25.08.s$Total.Mass))
p26.08.s.m=sum(as.numeric(p26.08.s$Total.Mass))
p27.08.s.m=sum(as.numeric(p27.08.s$Total.Mass))
p28.08.s.m=sum(as.numeric(p28.08.s$Total.Mass))
p29.08.s.m=sum(as.numeric(p29.08.s$Total.Mass))
p30.08.s.m=sum(as.numeric(p30.08.s$Total.Mass))
p31.08.s.m=sum(as.numeric(p31.08.s$Total.Mass))
p32.08.s.m=sum(as.numeric(p32.08.s$Total.Mass))
p33.08.s.m=sum(as.numeric(p33.08.s$Total.Mass))
p34.08.s.m=sum(as.numeric(p34.08.s$Total.Mass))
p35.08.s.m=sum(as.numeric(p35.08.s$Total.Mass))
p36.08.s.m=sum(as.numeric(p36.08.s$Total.Mass))
```

#2009 subsetted by season
```{r}

## 2009 year subsetted by season 
dat.09=dat.herb[dat.herb$Year==2009,]
dat.09.fall=dat.09[dat.09$Season=="Fall",]
dat.09.summ=dat.09[dat.09$Season=="Summer",]
dat.09.fall.m=as.numeric(dat.09.fall$Total.Mass)
dat.09.summ.m=as.numeric(dat.09.summ$Total.Mass)
#Means,95% intervals, standarad deviation, 
dat.09.fall.95=quantile(dat.09.fall.m,c(.05,.95))
dat.09.summ.95=quantile(dat.09.summ.m,c(.05,.95))
dat.09.fall.mean=mean(dat.09.fall.m)
dat.09.summ.mean=mean(dat.09.summ.m)
dat.09.fall.sd=sd(dat.09.fall.m)
dat.09.summ.sd=sd(dat.09.summ.m)
```

##2009 subsetted by treatment
```{r}
## Seasonal subsetted by treatment
wt.09.f=dat.09.fall[dat.09.fall$Treatment== "W",]
wt.09.s=dat.09.summ[dat.09.summ$Treatment== "W",]
dr.09.f=dat.09.fall[dat.09.fall$Treatment== "D",]
dr.09.s=dat.09.summ[dat.09.summ$Treatment== "D",]
ab.09.f=dat.09.fall[dat.09.fall$Treatment== "A",]
ab.09.s=dat.09.summ[dat.09.summ$Treatment== "A",]

##Treatment subsetted by mass
wt.09.f.m=as.numeric(wt.09.f$Total.Mass) 
wt.09.s.m=as.numeric(wt.09.s$Total.Mass)
dr.09.f.m=as.numeric(dr.09.f$Total.Mass)
dr.09.s.m=as.numeric(dr.09.s$Total.Mass)
ab.09.f.m=as.numeric(ab.09.f$Total.Mass)
ab.09.s.m=as.numeric(ab.09.s$Total.Mass)

#Summary data
w.09.fall.95=quantile(wt.09.f.m,c(.05,.95),na.rm=TRUE)
w.09.summ.95=quantile(wt.09.s.m,c(.05,.95),na.rm=TRUE)
w.09.fall.mean=mean(wt.09.f.m,na.rm=TRUE)
w.09.summ.mean=mean(wt.09.s.m,na.rm=TRUE)
w.09.fall.sd=sd(wt.09.f.m,na.rm=TRUE)
w.09.summ.sd=sd(wt.09.s.m,na.rm=TRUE)

a.09.fall.95=quantile(ab.09.f.m,c(.05,.95),na.rm=TRUE)
a.09.summ.95=quantile(ab.09.s.m,c(.05,.95),na.rm=TRUE)
a.09.fall.mean=mean(ab.09.f.m,na.rm=TRUE)
a.09.summ.mean=mean(ab.09.s.m,na.rm=TRUE)
a.09.fall.sd=sd(ab.09.f.m,na.rm=TRUE)
a.09.summ.sd=sd(ab.09.s.m,na.rm=TRUE)

d.09.fall.95=quantile(dr.09.f.m,c(.05,.95),na.rm=TRUE)
d.09.summ.95=quantile(dr.09.s.m,c(.05,.95),na.rm=TRUE)
d.09.fall.mean=mean(dr.09.f.m,na.rm=TRUE)
d.09.summ.mean=mean(dr.09.s.m,na.rm=TRUE)
d.09.fall.sd=sd(dr.09.f.m,na.rm=TRUE)
d.09.summ.sd=sd(dr.09.s.m,na.rm=TRUE)
```

#2009 subsetted by plot
```{r}
## Seasonal subsetted by plot
p1.09.f=dat.09.fall[dat.09.fall$Plot %in% 1,]
p2.09.f=dat.09.fall[dat.09.fall$Plot %in% 2,]
p3.09.f=dat.09.fall[dat.09.fall$Plot %in% 3,]
p4.09.f=dat.09.fall[dat.09.fall$Plot %in% 4,]
p5.09.f=dat.09.fall[dat.09.fall$Plot %in% 5,]
p6.09.f=dat.09.fall[dat.09.fall$Plot %in% 6,]
p7.09.f=dat.09.fall[dat.09.fall$Plot %in% 7,]
p8.09.f=dat.09.fall[dat.09.fall$Plot %in% 8,]
p9.09.f=dat.09.fall[dat.09.fall$Plot %in% 9,]
p10.09.f=dat.09.fall[dat.09.fall$Plot %in% 10,]
p11.09.f=dat.09.fall[dat.09.fall$Plot %in% 11,]
p12.09.f=dat.09.fall[dat.09.fall$Plot %in% 12,]
p13.09.f=dat.09.fall[dat.09.fall$Plot %in% 13,]
p14.09.f=dat.09.fall[dat.09.fall$Plot %in% 14,]
p15.09.f=dat.09.fall[dat.09.fall$Plot %in% 15,]
p16.09.f=dat.09.fall[dat.09.fall$Plot %in% 16,]
p17.09.f=dat.09.fall[dat.09.fall$Plot %in% 17,]
p18.09.f=dat.09.fall[dat.09.fall$Plot %in% 18,]
p19.09.f=dat.09.fall[dat.09.fall$Plot %in% 19,]
p20.09.f=dat.09.fall[dat.09.fall$Plot %in% 20,]
p21.09.f=dat.09.fall[dat.09.fall$Plot %in% 21,]
p22.09.f=dat.09.fall[dat.09.fall$Plot %in% 22,]
p23.09.f=dat.09.fall[dat.09.fall$Plot %in% 23,]
p24.09.f=dat.09.fall[dat.09.fall$Plot %in% 24,]
p25.09.f=dat.09.fall[dat.09.fall$Plot %in% 25,]
p26.09.f=dat.09.fall[dat.09.fall$Plot %in% 26,]
p27.09.f=dat.09.fall[dat.09.fall$Plot %in% 27,]
p28.09.f=dat.09.fall[dat.09.fall$Plot %in% 28,]
p29.09.f=dat.09.fall[dat.09.fall$Plot %in% 29,]
p30.09.f=dat.09.fall[dat.09.fall$Plot %in% 30,]
p31.09.f=dat.09.fall[dat.09.fall$Plot %in% 31,]
p32.09.f=dat.09.fall[dat.09.fall$Plot %in% 32,]
p33.09.f=dat.09.fall[dat.09.fall$Plot %in% 33,]
p34.09.f=dat.09.fall[dat.09.fall$Plot %in% 34,]
p35.09.f=dat.09.fall[dat.09.fall$Plot %in% 35,]
p36.09.f=dat.09.fall[dat.09.fall$Plot %in% 36,]

p1.09.s=dat.09.summ[dat.09.summ$Plot %in% 1,]
p2.09.s=dat.09.summ[dat.09.summ$Plot %in% 2,]
p3.09.s=dat.09.summ[dat.09.summ$Plot %in% 3,]
p4.09.s=dat.09.summ[dat.09.summ$Plot %in% 4,]
p5.09.s=dat.09.summ[dat.09.summ$Plot %in% 5,]
p6.09.s=dat.09.summ[dat.09.summ$Plot %in% 6,]
p7.09.s=dat.09.summ[dat.09.summ$Plot %in% 7,]
p8.09.s=dat.09.summ[dat.09.summ$Plot %in% 8,]
p9.09.s=dat.09.summ[dat.09.summ$Plot %in% 9,]
p10.09.s=dat.09.summ[dat.09.summ$Plot %in% 10,]
p11.09.s=dat.09.summ[dat.09.summ$Plot %in% 11,]
p12.09.s=dat.09.summ[dat.09.summ$Plot %in% 12,]
p13.09.s=dat.09.summ[dat.09.summ$Plot %in% 13,]
p14.09.s=dat.09.summ[dat.09.summ$Plot %in% 14,]
p15.09.s=dat.09.summ[dat.09.summ$Plot %in% 15,]
p16.09.s=dat.09.summ[dat.09.summ$Plot %in% 16,]
p17.09.s=dat.09.summ[dat.09.summ$Plot %in% 17,]
p18.09.s=dat.09.summ[dat.09.summ$Plot %in% 18,]
p19.09.s=dat.09.summ[dat.09.summ$Plot %in% 19,]
p20.09.s=dat.09.summ[dat.09.summ$Plot %in% 20,]
p21.09.s=dat.09.summ[dat.09.summ$Plot %in% 21,]
p22.09.s=dat.09.summ[dat.09.summ$Plot %in% 22,]
p23.09.s=dat.09.summ[dat.09.summ$Plot %in% 23,]
p24.09.s=dat.09.summ[dat.09.summ$Plot %in% 24,]
p25.09.s=dat.09.summ[dat.09.summ$Plot %in% 25,]
p26.09.s=dat.09.summ[dat.09.summ$Plot %in% 26,]
p27.09.s=dat.09.summ[dat.09.summ$Plot %in% 27,]
p28.09.s=dat.09.summ[dat.09.summ$Plot %in% 28,]
p29.09.s=dat.09.summ[dat.09.summ$Plot %in% 29,]
p30.09.s=dat.09.summ[dat.09.summ$Plot %in% 30,]
p31.09.s=dat.09.summ[dat.09.summ$Plot %in% 31,]
p32.09.s=dat.09.summ[dat.09.summ$Plot %in% 32,]
p33.09.s=dat.09.summ[dat.09.summ$Plot %in% 33,]
p34.09.s=dat.09.summ[dat.09.summ$Plot %in% 34,]
p35.09.s=dat.09.summ[dat.09.summ$Plot %in% 35,]
p36.09.s=dat.09.summ[dat.09.summ$Plot %in% 36,]

#Plot subsetted by mass
p1.09.f.m=sum(as.numeric(p1.09.f$Total.Mass))
p2.09.f.m=sum(as.numeric(p2.09.f$Total.Mass))
p3.09.f.m=sum(as.numeric(p3.09.f$Total.Mass))
p4.09.f.m=sum(as.numeric(p4.09.f$Total.Mass))
p5.09.f.m=sum(as.numeric(p5.09.f$Total.Mass))
p6.09.f.m=sum(as.numeric(p6.09.f$Total.Mass))
p7.09.f.m=sum(as.numeric(p7.09.f$Total.Mass))
p8.09.f.m=sum(as.numeric(p8.09.f$Total.Mass))
p9.09.f.m=sum(as.numeric(p9.09.f$Total.Mass))
p10.09.f.m=sum(as.numeric(p10.09.f$Total.Mass))
p11.09.f.m=sum(as.numeric(p11.09.f$Total.Mass))
p12.09.f.m=sum(as.numeric(p12.09.f$Total.Mass))
p13.09.f.m=sum(as.numeric(p13.09.f$Total.Mass))
p14.09.f.m=sum(as.numeric(p14.09.f$Total.Mass))
p15.09.f.m=sum(as.numeric(p15.09.f$Total.Mass))
p16.09.f.m=sum(as.numeric(p16.09.f$Total.Mass))
p17.09.f.m=sum(as.numeric(p17.09.f$Total.Mass))
p18.09.f.m=sum(as.numeric(p18.09.f$Total.Mass))
p19.09.f.m=sum(as.numeric(p19.09.f$Total.Mass))
p20.09.f.m=sum(as.numeric(p20.09.f$Total.Mass))
p21.09.f.m=sum(as.numeric(p21.09.f$Total.Mass))
p22.09.f.m=sum(as.numeric(p22.09.f$Total.Mass))
p23.09.f.m=sum(as.numeric(p23.09.f$Total.Mass))
p24.09.f.m=sum(as.numeric(p24.09.f$Total.Mass))
p25.09.f.m=sum(as.numeric(p25.09.f$Total.Mass))
p26.09.f.m=sum(as.numeric(p26.09.f$Total.Mass))
p27.09.f.m=sum(as.numeric(p27.09.f$Total.Mass))
p28.09.f.m=sum(as.numeric(p28.09.f$Total.Mass))
p29.09.f.m=sum(as.numeric(p29.09.f$Total.Mass))
p30.09.f.m=sum(as.numeric(p30.09.f$Total.Mass))
p31.09.f.m=sum(as.numeric(p31.09.f$Total.Mass))
p32.09.f.m=sum(as.numeric(p32.09.f$Total.Mass))
p33.09.f.m=sum(as.numeric(p33.09.f$Total.Mass))
p34.09.f.m=sum(as.numeric(p34.09.f$Total.Mass))
p35.09.f.m=sum(as.numeric(p35.09.f$Total.Mass))
p36.09.f.m=sum(as.numeric(p36.09.f$Total.Mass))

p1.09.s.m=sum(as.numeric(p1.09.s$Total.Mass))
p2.09.s.m=sum(as.numeric(p2.09.s$Total.Mass))
p3.09.s.m=sum(as.numeric(p3.09.s$Total.Mass))
p4.09.s.m=sum(as.numeric(p4.09.s$Total.Mass))
p5.09.s.m=sum(as.numeric(p5.09.s$Total.Mass))
p6.09.s.m=sum(as.numeric(p6.09.s$Total.Mass))
p7.09.s.m=sum(as.numeric(p7.09.s$Total.Mass))
p8.09.s.m=sum(as.numeric(p8.09.s$Total.Mass))
p9.09.s.m=sum(as.numeric(p9.09.s$Total.Mass))
p10.09.s.m=sum(as.numeric(p10.09.s$Total.Mass))
p11.09.s.m=sum(as.numeric(p11.09.s$Total.Mass))
p12.09.s.m=sum(as.numeric(p12.09.s$Total.Mass))
p13.09.s.m=sum(as.numeric(p13.09.s$Total.Mass))
p14.09.s.m=sum(as.numeric(p14.09.s$Total.Mass))
p15.09.s.m=sum(as.numeric(p15.09.s$Total.Mass))
p16.09.s.m=sum(as.numeric(p16.09.s$Total.Mass))
p17.09.s.m=sum(as.numeric(p17.09.s$Total.Mass))
p18.09.s.m=sum(as.numeric(p18.09.s$Total.Mass))
p19.09.s.m=sum(as.numeric(p19.09.s$Total.Mass))
p20.09.s.m=sum(as.numeric(p20.09.s$Total.Mass))
p21.09.s.m=sum(as.numeric(p21.09.s$Total.Mass))
p22.09.s.m=sum(as.numeric(p22.09.s$Total.Mass))
p23.09.s.m=sum(as.numeric(p23.09.s$Total.Mass))
p24.09.s.m=sum(as.numeric(p24.09.s$Total.Mass))
p25.09.s.m=sum(as.numeric(p25.09.s$Total.Mass))
p26.09.s.m=sum(as.numeric(p26.09.s$Total.Mass))
p27.09.s.m=sum(as.numeric(p27.09.s$Total.Mass))
p28.09.s.m=sum(as.numeric(p28.09.s$Total.Mass))
p29.09.s.m=sum(as.numeric(p29.09.s$Total.Mass))
p30.09.s.m=sum(as.numeric(p30.09.s$Total.Mass))
p31.09.s.m=sum(as.numeric(p31.09.s$Total.Mass))
p32.09.s.m=sum(as.numeric(p32.09.s$Total.Mass))
p33.09.s.m=sum(as.numeric(p33.09.s$Total.Mass))
p34.09.s.m=sum(as.numeric(p34.09.s$Total.Mass))
p35.09.s.m=sum(as.numeric(p35.09.s$Total.Mass))
p36.09.s.m=sum(as.numeric(p36.09.s$Total.Mass))
```

## 2012 year subsetted by season
```{r}
 ## 2012 year subsetted by season
dat.12=dat.herb[dat.herb$Year==2012,]
## Seasonal subsetted by treatment
wt.12.f=dat.12[dat.12$Treatment== "W",]
dr.12.f=dat.12[dat.12$Treatment== "D",]
ab.12.f=dat.12[dat.12$Treatment== "A",]
##Treatment subsetted by mass
wt.12.f.m=as.numeric(wt.12.f$Total.Mass) 
dr.12.f.m=as.numeric(dr.12.f$Total.Mass)
ab.12.f.m=as.numeric(ab.12.f$Total.Mass)
## Seasonal subsetted by plot
p1.12.f=dat.12[dat.12$Plot %in% 1,]
p2.12.f=dat.12[dat.12$Plot %in% 2,]
p3.12.f=dat.12[dat.12$Plot %in% 3,]
p4.12.f=dat.12[dat.12$Plot %in% 4,]
p5.12.f=dat.12[dat.12$Plot %in% 5,]
p6.12.f=dat.12[dat.12$Plot %in% 6,]
p7.12.f=dat.12[dat.12$Plot %in% 7,]
p8.12.f=dat.12[dat.12$Plot %in% 8,]
p9.12.f=dat.12[dat.12$Plot %in% 9,]
p10.12.f=dat.12[dat.12$Plot %in% 10,]
p11.12.f=dat.12[dat.12$Plot %in% 11,]
p12.12.f=dat.12[dat.12$Plot %in% 12,]
p13.12.f=dat.12[dat.12$Plot %in% 13,]
p14.12.f=dat.12[dat.12$Plot %in% 14,]
p15.12.f=dat.12[dat.12$Plot %in% 15,]
p16.12.f=dat.12[dat.12$Plot %in% 16,]
p17.12.f=dat.12[dat.12$Plot %in% 17,]
p18.12.f=dat.12[dat.12$Plot %in% 18,]
p19.12.f=dat.12[dat.12$Plot %in% 19,]
p20.12.f=dat.12[dat.12$Plot %in% 20,]
p21.12.f=dat.12[dat.12$Plot %in% 21,]
p22.12.f=dat.12[dat.12$Plot %in% 22,]
p23.12.f=dat.12[dat.12$Plot %in% 23,]
p24.12.f=dat.12[dat.12$Plot %in% 24,]
p25.12.f=dat.12[dat.12$Plot %in% 25,]
p26.12.f=dat.12[dat.12$Plot %in% 26,]
p27.12.f=dat.12[dat.12$Plot %in% 27,]
p28.12.f=dat.12[dat.12$Plot %in% 28,]
p29.12.f=dat.12[dat.12$Plot %in% 29,]
p30.12.f=dat.12[dat.12$Plot %in% 30,]
p31.12.f=dat.12[dat.12$Plot %in% 31,]
p32.12.f=dat.12[dat.12$Plot %in% 32,]
p33.12.f=dat.12[dat.12$Plot %in% 33,]
p34.12.f=dat.12[dat.12$Plot %in% 34,]
p35.12.f=dat.12[dat.12$Plot %in% 35,]
p36.12.f=dat.12[dat.12$Plot %in% 36,]

#Plot subsetted by mass
p1.12.f.m=sum(as.numeric(p1.12.f$Total.Mass))
p2.12.f.m=sum(as.numeric(p2.12.f$Total.Mass))
p3.12.f.m=sum(as.numeric(p3.12.f$Total.Mass))
p4.12.f.m=sum(as.numeric(p4.12.f$Total.Mass))
p5.12.f.m=sum(as.numeric(p5.12.f$Total.Mass))
p6.12.f.m=sum(as.numeric(p6.12.f$Total.Mass))
p7.12.f.m=sum(as.numeric(p7.12.f$Total.Mass))
p8.12.f.m=sum(as.numeric(p8.12.f$Total.Mass))
p9.12.f.m=sum(as.numeric(p9.12.f$Total.Mass))
p10.12.f.m=sum(as.numeric(p10.12.f$Total.Mass))
p11.12.f.m=sum(as.numeric(p11.12.f$Total.Mass))
p12.12.f.m=sum(as.numeric(p12.12.f$Total.Mass))
p13.12.f.m=sum(as.numeric(p13.12.f$Total.Mass))
p14.12.f.m=sum(as.numeric(p14.12.f$Total.Mass))
p15.12.f.m=sum(as.numeric(p15.12.f$Total.Mass))
p16.12.f.m=sum(as.numeric(p16.12.f$Total.Mass))
p17.12.f.m=sum(as.numeric(p17.12.f$Total.Mass))
p18.12.f.m=sum(as.numeric(p18.12.f$Total.Mass))
p19.12.f.m=sum(as.numeric(p19.12.f$Total.Mass))
p20.12.f.m=sum(as.numeric(p20.12.f$Total.Mass))
p21.12.f.m=sum(as.numeric(p21.12.f$Total.Mass))
p22.12.f.m=sum(as.numeric(p22.12.f$Total.Mass))
p23.12.f.m=sum(as.numeric(p23.12.f$Total.Mass))
p24.12.f.m=sum(as.numeric(p24.12.f$Total.Mass))
p25.12.f.m=sum(as.numeric(p25.12.f$Total.Mass))
p26.12.f.m=sum(as.numeric(p26.12.f$Total.Mass))
p27.12.f.m=sum(as.numeric(p27.12.f$Total.Mass))
p28.12.f.m=sum(as.numeric(p28.12.f$Total.Mass))
p29.12.f.m=sum(as.numeric(p29.12.f$Total.Mass))
p30.12.f.m=sum(as.numeric(p30.12.f$Total.Mass))
p31.12.f.m=sum(as.numeric(p31.12.f$Total.Mass))
p32.12.f.m=sum(as.numeric(p32.12.f$Total.Mass))
p33.12.f.m=sum(as.numeric(p33.12.f$Total.Mass))
p34.12.f.m=sum(as.numeric(p34.12.f$Total.Mass))
p35.12.f.m=sum(as.numeric(p35.12.f$Total.Mass))
p36.12.f.m=sum(as.numeric(p36.12.f$Total.Mass))

```

#2010 Herbaceous season subset
```{r}
## 2010 year subsetted by season 
dat.10=dat.herb[dat.herb$Year==2010,]
dat.10.summ=dat.10[dat.10$Season=="Summer",]
dat.10.summ.m=as.numeric(dat.10.summ$Total.Mass)
#Means,95% intervals, standarad deviation, 
dat.10.summ.95=quantile(dat.10.summ.m,c(.05,.95))
dat.10.summ.mean=mean(dat.10.summ.m)
dat.10.summ.sd=sd(dat.10.summ.m)
```

#2010 Herb Subseted by treatment
```{r}
## Seasonal subsetted by treatment
wt.10.s=dat.10.summ[dat.10.summ$Treatment== "W",]
dr.10.s=dat.10.summ[dat.10.summ$Treatment== "D",]
ab.10.s=dat.10.summ[dat.10.summ$Treatment== "A",]

##Treatment subsetted by mass
wt.10.s.m=as.numeric(wt.10.s$Total.Mass) 
dr.10.s.m=as.numeric(dr.10.s$Total.Mass)
ab.10.s.m=as.numeric(ab.10.s$Total.Mass)

#Summary data
w.10.summ.95=quantile(wt.10.s.m,c(.05,.95),na.rm=TRUE)
w.10.summ.mean=mean(wt.10.s.m,na.rm=TRUE)
w.10.summ.sd=sd(wt.10.s.m,na.rm=TRUE)

a.10.summ.95=quantile(ab.10.s.m,c(.05,.95),na.rm=TRUE)
a.10.summ.mean=mean(ab.10.s.m,na.rm=TRUE)
a.10.summ.sd=sd(ab.10.s.m,na.rm=TRUE)

d.10.summ.95=quantile(dr.10.s.m,c(.05,.95),na.rm=TRUE)
d.10.summ.mean=mean(dr.10.s.m,na.rm=TRUE)
d.10.summ.sd=sd(dr.10.s.m,na.rm=TRUE)
```

#2010 Herb subsetted by plot
```{r}
## Seasonal subsetted by plot
p1.10.s=dat.10.summ[dat.10.summ$Plot %in% 1,]
p2.10.s=dat.10.summ[dat.10.summ$Plot %in% 2,]
p3.10.s=dat.10.summ[dat.10.summ$Plot %in% 3,]
p4.10.s=dat.10.summ[dat.10.summ$Plot %in% 4,]
p5.10.s=dat.10.summ[dat.10.summ$Plot %in% 5,]
p6.10.s=dat.10.summ[dat.10.summ$Plot %in% 6,]
p7.10.s=dat.10.summ[dat.10.summ$Plot %in% 7,]
p8.10.s=dat.10.summ[dat.10.summ$Plot %in% 8,]
p9.10.s=dat.10.summ[dat.10.summ$Plot %in% 9,]
p10.10.s=dat.10.summ[dat.10.summ$Plot %in% 10,]
p11.10.s=dat.10.summ[dat.10.summ$Plot %in% 11,]
p12.10.s=dat.10.summ[dat.10.summ$Plot %in% 12,]
p13.10.s=dat.10.summ[dat.10.summ$Plot %in% 13,]
p14.10.s=dat.10.summ[dat.10.summ$Plot %in% 14,]
p15.10.s=dat.10.summ[dat.10.summ$Plot %in% 15,]
p16.10.s=dat.10.summ[dat.10.summ$Plot %in% 16,]
p17.10.s=dat.10.summ[dat.10.summ$Plot %in% 17,]
p18.10.s=dat.10.summ[dat.10.summ$Plot %in% 18,]
p19.10.s=dat.10.summ[dat.10.summ$Plot %in% 19,]
p20.10.s=dat.10.summ[dat.10.summ$Plot %in% 20,]
p21.10.s=dat.10.summ[dat.10.summ$Plot %in% 21,]
p22.10.s=dat.10.summ[dat.10.summ$Plot %in% 22,]
p23.10.s=dat.10.summ[dat.10.summ$Plot %in% 23,]
p24.10.s=dat.10.summ[dat.10.summ$Plot %in% 24,]
p25.10.s=dat.10.summ[dat.10.summ$Plot %in% 25,]
p26.10.s=dat.10.summ[dat.10.summ$Plot %in% 26,]
p27.10.s=dat.10.summ[dat.10.summ$Plot %in% 27,]
p28.10.s=dat.10.summ[dat.10.summ$Plot %in% 28,]
p29.10.s=dat.10.summ[dat.10.summ$Plot %in% 29,]
p30.10.s=dat.10.summ[dat.10.summ$Plot %in% 30,]
p31.10.s=dat.10.summ[dat.10.summ$Plot %in% 31,]
p32.10.s=dat.10.summ[dat.10.summ$Plot %in% 32,]
p33.10.s=dat.10.summ[dat.10.summ$Plot %in% 33,]
p34.10.s=dat.10.summ[dat.10.summ$Plot %in% 34,]
p35.10.s=dat.10.summ[dat.10.summ$Plot %in% 35,]
p36.10.s=dat.10.summ[dat.10.summ$Plot %in% 36,]


#Plot subsetted by mass
p1.10.s.m=sum(as.numeric(p1.10.s$Total.Mass))
p2.10.s.m=sum(as.numeric(p2.10.s$Total.Mass))
p3.10.s.m=sum(as.numeric(p3.10.s$Total.Mass))
p4.10.s.m=sum(as.numeric(p4.10.s$Total.Mass))
p5.10.s.m=sum(as.numeric(p5.10.s$Total.Mass))
p6.10.s.m=sum(as.numeric(p6.10.s$Total.Mass))
p7.10.s.m=sum(as.numeric(p7.10.s$Total.Mass))
p8.10.s.m=sum(as.numeric(p8.10.s$Total.Mass))
p9.10.s.m=sum(as.numeric(p9.10.s$Total.Mass))
p10.10.s.m=sum(as.numeric(p10.10.s$Total.Mass))
p11.10.s.m=sum(as.numeric(p10.10.s$Total.Mass))
p12.10.s.m=sum(as.numeric(p12.10.s$Total.Mass))
p10.10.s.m=sum(as.numeric(p10.10.s$Total.Mass))
p14.10.s.m=sum(as.numeric(p14.10.s$Total.Mass))
p15.10.s.m=sum(as.numeric(p15.10.s$Total.Mass))
p16.10.s.m=sum(as.numeric(p16.10.s$Total.Mass))
p17.10.s.m=sum(as.numeric(p17.10.s$Total.Mass))
p18.10.s.m=sum(as.numeric(p18.10.s$Total.Mass))
p19.10.s.m=sum(as.numeric(p19.10.s$Total.Mass))
p20.10.s.m=sum(as.numeric(p20.10.s$Total.Mass))
p21.10.s.m=sum(as.numeric(p21.10.s$Total.Mass))
p22.10.s.m=sum(as.numeric(p22.10.s$Total.Mass))
p23.10.s.m=sum(as.numeric(p23.10.s$Total.Mass))
p24.10.s.m=sum(as.numeric(p24.10.s$Total.Mass))
p25.10.s.m=sum(as.numeric(p25.10.s$Total.Mass))
p26.10.s.m=sum(as.numeric(p26.10.s$Total.Mass))
p27.10.s.m=sum(as.numeric(p27.10.s$Total.Mass))
p28.10.s.m=sum(as.numeric(p28.10.s$Total.Mass))
p29.10.s.m=sum(as.numeric(p29.10.s$Total.Mass))
p30.10.s.m=sum(as.numeric(p30.10.s$Total.Mass))
p31.10.s.m=sum(as.numeric(p31.10.s$Total.Mass))
p32.10.s.m=sum(as.numeric(p32.10.s$Total.Mass))
p33.10.s.m=sum(as.numeric(p33.10.s$Total.Mass))
p34.10.s.m=sum(as.numeric(p34.10.s$Total.Mass))
p35.10.s.m=sum(as.numeric(p35.10.s$Total.Mass))
p36.10.s.m=sum(as.numeric(p36.10.s$Total.Mass))


```


#2011 Tree data
```{r}
dat.11t<-dat.tree[dat.tree$year==2011,]
dat.11t.fall.m=as.numeric(dat.11t$tot.mass)
#Means,95% intervals, standarad deviation, 
dat.11t.fall.95=quantile(dat.11t.fall.m,c(.05,.95),na.rm=TRUE)
dat.11t.fall.mean=mean(dat.11t.fall.m,na.rm=TRUE)
dat.11t.fall.sd=sd(dat.11t.fall.m,na.rm=TRUE)
```

##2011 TreeTreatment Subset
```{r}
w.11t<-dat.11t[dat.11t$Plot %in% c(9,10,11,12,17,18,19,20,25,26,27,28),]
d.11t<-dat.11t[dat.11t$Plot %in% c(1,2,3,4,21,22,23,24,33,34,35,36),]
a.11t<-dat.11t[dat.11t$Plot %in% c(5,6,7,8,13,14,15,16,29,30,31,32),]
w.11t.tm=as.numeric(w.11t$tot.mass)
d.11t.tm=as.numeric(d.11t$tot.mass)
a.11t.tm=as.numeric(a.11t$tot.mass)
##Summary Stats
w.11t.fall.95=quantile(w.11t.tm,c(.05,.95),na.rm=TRUE)
w.11t.fall.mean=mean(w.11t.tm,na.rm=TRUE)
w.11t.fall.sd=sd(w.11t.tm,na.rm=TRUE)

a.11t.fall.95=quantile(a.11t.tm,c(.05,.95),na.rm=TRUE)
a.11t.fall.mean=mean(a.11t.tm,na.rm=TRUE)
a.11t.fall.sd=sd(a.11t.tm,na.rm=TRUE)

d.11t.fall.95=quantile(d.11t.tm,c(.05,.95),na.rm=TRUE)
d.11t.fall.mean=mean(d.11t.tm,na.rm=TRUE)
d.11t.fall.sd=sd(d.11t.tm,na.rm=TRUE)
```

#2011 Tree Plot subset
```{r}
p1.11t=dat.11t[dat.11t$Plot %in% 1,]
p2.11t=dat.11t[dat.11t$Plot %in% 2,]
p3.11t=dat.11t[dat.11t$Plot %in% 3,]
p4.11t=dat.11t[dat.11t$Plot %in% 4,]
p5.11t=dat.11t[dat.11t$Plot %in% 5,]
p6.11t=dat.11t[dat.11t$Plot %in% 6,]
p7.11t=dat.11t[dat.11t$Plot %in% 7,]
p8.11t=dat.11t[dat.11t$Plot %in% 8,]
p9.11t=dat.11t[dat.11t$Plot %in% 9,]
p10.11t=dat.11t[dat.11t$Plot %in% 10,]
p11t.11t=dat.11t[dat.11t$Plot %in% 11,]
p12.11t=dat.11t[dat.11t$Plot %in% 12,]
p13.11t=dat.11t[dat.11t$Plot %in% 13,]
p14.11t=dat.11t[dat.11t$Plot %in% 14,]
p15.11t=dat.11t[dat.11t$Plot %in% 15,]
p16.11t=dat.11t[dat.11t$Plot %in% 16,]
p17.11t=dat.11t[dat.11t$Plot %in% 17,]
p18.11t=dat.11t[dat.11t$Plot %in% 18,]
p19.11t=dat.11t[dat.11t$Plot %in% 19,]
p20.11t=dat.11t[dat.11t$Plot %in% 20,]
p21.11t=dat.11t[dat.11t$Plot %in% 21,]
p22.11t=dat.11t[dat.11t$Plot %in% 22,]
p23.11t=dat.11t[dat.11t$Plot %in% 23,]
p24.11t=dat.11t[dat.11t$Plot %in% 24,]
p25.11t=dat.11t[dat.11t$Plot %in% 25,]
p26.11t=dat.11t[dat.11t$Plot %in% 26,]
p27.11t=dat.11t[dat.11t$Plot %in% 27,]
p28.11t=dat.11t[dat.11t$Plot %in% 28,]
p29.11t=dat.11t[dat.11t$Plot %in% 29,]
p30.11t=dat.11t[dat.11t$Plot %in% 30,]
p31.11t=dat.11t[dat.11t$Plot %in% 31,]
p32.11t=dat.11t[dat.11t$Plot %in% 32,]
p33.11t=dat.11t[dat.11t$Plot %in% 33,]
p34.11t=dat.11t[dat.11t$Plot %in% 34,]
p35.11t=dat.11t[dat.11t$Plot %in% 35,]
p36.11t=dat.11t[dat.11t$Plot %in% 36,]
```

#2011 Herbaceous season subset
```{r}
## 2011 year subsetted by season 
dat.11=dat.herb[dat.herb$Year==2011,]
dat.11.fall=dat.11[dat.11$Season=="Fall",]
dat.11.summ=dat.11[dat.11$Season=="Summer",]
dat.11.fall.m=as.numeric(dat.11.fall$Total.Mass)
dat.11.summ.m=as.numeric(dat.11.summ$Total.Mass)
#Means,95% intervals, standarad deviation, 
dat.11.fall.95=quantile(dat.11.fall.m,c(.05,.95))
dat.11.summ.95=quantile(dat.11.summ.m,c(.05,.95))
dat.11.fall.mean=mean(dat.11.fall.m)
dat.11.summ.mean=mean(dat.11.summ.m)
dat.11.fall.sd=sd(dat.11.fall.m)
dat.11.summ.sd=sd(dat.11.summ.m)
```

#2011 Herb Subseted by treatment
```{r}
## Seasonal subsetted by treatment
wt.11.f=dat.11.fall[dat.11.fall$Treatment== "W",]
wt.11.s=dat.11.summ[dat.11.summ$Treatment== "W",]
dr.11.f=dat.11.fall[dat.11.fall$Treatment== "D",]
dr.11.s=dat.11.summ[dat.11.summ$Treatment== "D",]
ab.11.f=dat.11.fall[dat.11.fall$Treatment== "A",]
ab.11.s=dat.11.summ[dat.11.summ$Treatment== "A",]

##Treatment subsetted by mass
wt.11.f.m=as.numeric(wt.11.f$Total.Mass) 
wt.11.s.m=as.numeric(wt.11.s$Total.Mass)
dr.11.f.m=as.numeric(dr.11.f$Total.Mass)
dr.11.s.m=as.numeric(dr.11.s$Total.Mass)
ab.11.f.m=as.numeric(ab.11.f$Total.Mass)
ab.11.s.m=as.numeric(ab.11.s$Total.Mass)

#Summary data
w.11.fall.95=quantile(wt.11.f.m,c(.05,.95),na.rm=TRUE)
w.11.summ.95=quantile(wt.11.s.m,c(.05,.95),na.rm=TRUE)
w.11.fall.mean=mean(wt.11.f.m,na.rm=TRUE)
w.11.summ.mean=mean(wt.11.s.m,na.rm=TRUE)
w.11.fall.sd=sd(wt.11.f.m,na.rm=TRUE)
w.11.summ.sd=sd(wt.11.s.m,na.rm=TRUE)

a.11.fall.95=quantile(ab.11.f.m,c(.05,.95),na.rm=TRUE)
a.11.summ.95=quantile(ab.11.s.m,c(.05,.95),na.rm=TRUE)
a.11.fall.mean=mean(ab.11.f.m,na.rm=TRUE)
a.11.summ.mean=mean(ab.11.s.m,na.rm=TRUE)
a.11.fall.sd=sd(ab.11.f.m,na.rm=TRUE)
a.11.summ.sd=sd(ab.11.s.m,na.rm=TRUE)

d.11.fall.95=quantile(dr.11.f.m,c(.05,.95),na.rm=TRUE)
d.11.summ.95=quantile(dr.11.s.m,c(.05,.95),na.rm=TRUE)
d.11.fall.mean=mean(dr.11.f.m,na.rm=TRUE)
d.11.summ.mean=mean(dr.11.s.m,na.rm=TRUE)
d.11.fall.sd=sd(dr.11.f.m,na.rm=TRUE)
d.11.summ.sd=sd(dr.11.s.m,na.rm=TRUE)
```

#2011 Herb subsetted by plot
```{r}
## Seasonal subsetted by plot
p1.11.f=dat.11.fall[dat.11.fall$Plot %in% 1,]
p2.11.f=dat.11.fall[dat.11.fall$Plot %in% 2,]
p3.11.f=dat.11.fall[dat.11.fall$Plot %in% 3,]
p4.11.f=dat.11.fall[dat.11.fall$Plot %in% 4,]
p5.11.f=dat.11.fall[dat.11.fall$Plot %in% 5,]
p6.11.f=dat.11.fall[dat.11.fall$Plot %in% 6,]
p7.11.f=dat.11.fall[dat.11.fall$Plot %in% 7,]
p8.11.f=dat.11.fall[dat.11.fall$Plot %in% 8,]
p9.11.f=dat.11.fall[dat.11.fall$Plot %in% 9,]
p10.11.f=dat.11.fall[dat.11.fall$Plot %in% 10,]
p11.11.f=dat.11.fall[dat.11.fall$Plot %in% 11,]
p12.11.f=dat.11.fall[dat.11.fall$Plot %in% 12,]
p13.11.f=dat.11.fall[dat.11.fall$Plot %in% 13,]
p14.11.f=dat.11.fall[dat.11.fall$Plot %in% 14,]
p15.11.f=dat.11.fall[dat.11.fall$Plot %in% 15,]
p16.11.f=dat.11.fall[dat.11.fall$Plot %in% 16,]
p17.11.f=dat.11.fall[dat.11.fall$Plot %in% 17,]
p18.11.f=dat.11.fall[dat.11.fall$Plot %in% 18,]
p19.11.f=dat.11.fall[dat.11.fall$Plot %in% 19,]
p20.11.f=dat.11.fall[dat.11.fall$Plot %in% 20,]
p21.11.f=dat.11.fall[dat.11.fall$Plot %in% 21,]
p22.11.f=dat.11.fall[dat.11.fall$Plot %in% 22,]
p23.11.f=dat.11.fall[dat.11.fall$Plot %in% 23,]
p24.11.f=dat.11.fall[dat.11.fall$Plot %in% 24,]
p25.11.f=dat.11.fall[dat.11.fall$Plot %in% 25,]
p26.11.f=dat.11.fall[dat.11.fall$Plot %in% 26,]
p27.11.f=dat.11.fall[dat.11.fall$Plot %in% 27,]
p28.11.f=dat.11.fall[dat.11.fall$Plot %in% 28,]
p29.11.f=dat.11.fall[dat.11.fall$Plot %in% 29,]
p30.11.f=dat.11.fall[dat.11.fall$Plot %in% 30,]
p31.11.f=dat.11.fall[dat.11.fall$Plot %in% 31,]
p32.11.f=dat.11.fall[dat.11.fall$Plot %in% 32,]
p33.11.f=dat.11.fall[dat.11.fall$Plot %in% 33,]
p34.11.f=dat.11.fall[dat.11.fall$Plot %in% 34,]
p35.11.f=dat.11.fall[dat.11.fall$Plot %in% 35,]
p36.11.f=dat.11.fall[dat.11.fall$Plot %in% 36,]

p1.11.s=dat.11.summ[dat.11.summ$Plot %in% 1,]
p2.11.s=dat.11.summ[dat.11.summ$Plot %in% 2,]
p3.11.s=dat.11.summ[dat.11.summ$Plot %in% 3,]
p4.11.s=dat.11.summ[dat.11.summ$Plot %in% 4,]
p5.11.s=dat.11.summ[dat.11.summ$Plot %in% 5,]
p6.11.s=dat.11.summ[dat.11.summ$Plot %in% 6,]
p7.11.s=dat.11.summ[dat.11.summ$Plot %in% 7,]
p8.11.s=dat.11.summ[dat.11.summ$Plot %in% 8,]
p9.11.s=dat.11.summ[dat.11.summ$Plot %in% 9,]
p10.11.s=dat.11.summ[dat.11.summ$Plot %in% 10,]
p11.11.s=dat.11.summ[dat.11.summ$Plot %in% 11,]
p12.11.s=dat.11.summ[dat.11.summ$Plot %in% 12,]
p13.11.s=dat.11.summ[dat.11.summ$Plot %in% 13,]
p14.11.s=dat.11.summ[dat.11.summ$Plot %in% 14,]
p15.11.s=dat.11.summ[dat.11.summ$Plot %in% 15,]
p16.11.s=dat.11.summ[dat.11.summ$Plot %in% 16,]
p17.11.s=dat.11.summ[dat.11.summ$Plot %in% 17,]
p18.11.s=dat.11.summ[dat.11.summ$Plot %in% 18,]
p19.11.s=dat.11.summ[dat.11.summ$Plot %in% 19,]
p20.11.s=dat.11.summ[dat.11.summ$Plot %in% 20,]
p21.11.s=dat.11.summ[dat.11.summ$Plot %in% 21,]
p22.11.s=dat.11.summ[dat.11.summ$Plot %in% 22,]
p23.11.s=dat.11.summ[dat.11.summ$Plot %in% 23,]
p24.11.s=dat.11.summ[dat.11.summ$Plot %in% 24,]
p25.11.s=dat.11.summ[dat.11.summ$Plot %in% 25,]
p26.11.s=dat.11.summ[dat.11.summ$Plot %in% 26,]
p27.11.s=dat.11.summ[dat.11.summ$Plot %in% 27,]
p28.11.s=dat.11.summ[dat.11.summ$Plot %in% 28,]
p29.11.s=dat.11.summ[dat.11.summ$Plot %in% 29,]
p30.11.s=dat.11.summ[dat.11.summ$Plot %in% 30,]
p31.11.s=dat.11.summ[dat.11.summ$Plot %in% 31,]
p32.11.s=dat.11.summ[dat.11.summ$Plot %in% 32,]
p33.11.s=dat.11.summ[dat.11.summ$Plot %in% 33,]
p34.11.s=dat.11.summ[dat.11.summ$Plot %in% 34,]
p35.11.s=dat.11.summ[dat.11.summ$Plot %in% 35,]
p36.11.s=dat.11.summ[dat.11.summ$Plot %in% 36,]

#Plot subsetted by mass
p1.11.f.m=sum(as.numeric(p1.11.f$Total.Mass))
p2.11.f.m=sum(as.numeric(p2.11.f$Total.Mass))
p3.11.f.m=sum(as.numeric(p3.11.f$Total.Mass))
p4.11.f.m=sum(as.numeric(p4.11.f$Total.Mass))
p5.11.f.m=sum(as.numeric(p5.11.f$Total.Mass))
p6.11.f.m=sum(as.numeric(p6.11.f$Total.Mass))
p7.11.f.m=sum(as.numeric(p7.11.f$Total.Mass))
p8.11.f.m=sum(as.numeric(p8.11.f$Total.Mass))
p9.11.f.m=sum(as.numeric(p9.11.f$Total.Mass))
p10.11.f.m=sum(as.numeric(p10.11.f$Total.Mass))
p11.11.f.m=sum(as.numeric(p11.11.f$Total.Mass))
p12.11.f.m=sum(as.numeric(p12.11.f$Total.Mass))
p13.11.f.m=sum(as.numeric(p13.11.f$Total.Mass))
p14.11.f.m=sum(as.numeric(p14.11.f$Total.Mass))
p15.11.f.m=sum(as.numeric(p15.11.f$Total.Mass))
p16.11.f.m=sum(as.numeric(p16.11.f$Total.Mass))
p17.11.f.m=sum(as.numeric(p17.11.f$Total.Mass))
p18.11.f.m=sum(as.numeric(p18.11.f$Total.Mass))
p19.11.f.m=sum(as.numeric(p19.11.f$Total.Mass))
p20.11.f.m=sum(as.numeric(p20.11.f$Total.Mass))
p21.11.f.m=sum(as.numeric(p21.11.f$Total.Mass))
p22.11.f.m=sum(as.numeric(p22.11.f$Total.Mass))
p23.11.f.m=sum(as.numeric(p23.11.f$Total.Mass))
p24.11.f.m=sum(as.numeric(p24.11.f$Total.Mass))
p25.11.f.m=sum(as.numeric(p25.11.f$Total.Mass))
p26.11.f.m=sum(as.numeric(p26.11.f$Total.Mass))
p27.11.f.m=sum(as.numeric(p27.11.f$Total.Mass))
p28.11.f.m=sum(as.numeric(p28.11.f$Total.Mass))
p29.11.f.m=sum(as.numeric(p29.11.f$Total.Mass))
p30.11.f.m=sum(as.numeric(p30.11.f$Total.Mass))
p31.11.f.m=sum(as.numeric(p31.11.f$Total.Mass))
p32.11.f.m=sum(as.numeric(p32.11.f$Total.Mass))
p33.11.f.m=sum(as.numeric(p33.11.f$Total.Mass))
p34.11.f.m=sum(as.numeric(p34.11.f$Total.Mass))
p35.11.f.m=sum(as.numeric(p35.11.f$Total.Mass))
p36.11.f.m=sum(as.numeric(p36.11.f$Total.Mass))

p1.11.s.m=sum(as.numeric(p1.11.s$Total.Mass))
p2.11.s.m=sum(as.numeric(p2.11.s$Total.Mass))
p3.11.s.m=sum(as.numeric(p3.11.s$Total.Mass))
p4.11.s.m=sum(as.numeric(p4.11.s$Total.Mass))
p5.11.s.m=sum(as.numeric(p5.11.s$Total.Mass))
p6.11.s.m=sum(as.numeric(p6.11.s$Total.Mass))
p7.11.s.m=sum(as.numeric(p7.11.s$Total.Mass))
p8.11.s.m=sum(as.numeric(p8.11.s$Total.Mass))
p9.11.s.m=sum(as.numeric(p9.11.s$Total.Mass))
p10.11.s.m=sum(as.numeric(p10.11.s$Total.Mass))
p11.11.s.m=sum(as.numeric(p11.11.s$Total.Mass))
p12.11.s.m=sum(as.numeric(p12.11.s$Total.Mass))
p13.11.s.m=sum(as.numeric(p13.11.s$Total.Mass))
p14.11.s.m=sum(as.numeric(p14.11.s$Total.Mass))
p15.11.s.m=sum(as.numeric(p15.11.s$Total.Mass))
p16.11.s.m=sum(as.numeric(p16.11.s$Total.Mass))
p17.11.s.m=sum(as.numeric(p17.11.s$Total.Mass))
p18.11.s.m=sum(as.numeric(p18.11.s$Total.Mass))
p19.11.s.m=sum(as.numeric(p19.11.s$Total.Mass))
p20.11.s.m=sum(as.numeric(p20.11.s$Total.Mass))
p21.11.s.m=sum(as.numeric(p21.11.s$Total.Mass))
p22.11.s.m=sum(as.numeric(p22.11.s$Total.Mass))
p23.11.s.m=sum(as.numeric(p23.11.s$Total.Mass))
p24.11.s.m=sum(as.numeric(p24.11.s$Total.Mass))
p25.11.s.m=sum(as.numeric(p25.11.s$Total.Mass))
p26.11.s.m=sum(as.numeric(p26.11.s$Total.Mass))
p27.11.s.m=sum(as.numeric(p27.11.s$Total.Mass))
p28.11.s.m=sum(as.numeric(p28.11.s$Total.Mass))
p29.11.s.m=sum(as.numeric(p29.11.s$Total.Mass))
p30.11.s.m=sum(as.numeric(p30.11.s$Total.Mass))
p31.11.s.m=sum(as.numeric(p31.11.s$Total.Mass))
p32.11.s.m=sum(as.numeric(p32.11.s$Total.Mass))
p33.11.s.m=sum(as.numeric(p33.11.s$Total.Mass))
p34.11.s.m=sum(as.numeric(p34.11.s$Total.Mass))
p35.11.s.m=sum(as.numeric(p35.11.s$Total.Mass))
p36.11.s.m=sum(as.numeric(p36.11.s$Total.Mass))

```

## 2012 year subsetted by season 
```{r}
## 2012 year subsetted by season 
dat.12=dat.herb[dat.herb$Year==2012,]
dat.12.fall=dat.12[dat.12$Season=="Fall",]
dat.12.fall.m=as.numeric(dat.12.fall$Total.Mass)
#Means,95% intervals, standarad deviation, 
dat.12.fall.95=quantile(dat.12.fall.m,c(.05,.95))
dat.12.fall.mean=mean(dat.12.fall.m)
dat.12.fall.sd=sd(dat.12.fall.m)
```

##2012 Seasonal subsetted by treatment
```{r}
wt.12.f=dat.12[dat.12.fall$Treatment== "W",]
dr.12.f=dat.12[dat.12.fall$Treatment== "D",]
ab.12.f=dat.12[dat.12.fall$Treatment== "A",]
##Treatment subsetted by mass
wt.12.f.m=as.numeric(wt.12.f$Total.Mass) 
dr.12.f.m=as.numeric(dr.12.f$Total.Mass)
ab.12.f.m=as.numeric(ab.12.f$Total.Mass)
#Summary data
w.12.fall.95=quantile(wt.12.f.m,c(.05,.95),na.rm=TRUE)
w.12.fall.mean=mean(wt.12.f.m,na.rm=TRUE)
w.12.fall.sd=sd(wt.12.f.m,na.rm=TRUE)

a.12.fall.95=quantile(ab.12.f.m,c(.05,.95),na.rm=TRUE)
a.12.fall.mean=mean(ab.12.f.m,na.rm=TRUE)
a.12.fall.sd=sd(ab.12.f.m,na.rm=TRUE)

d.12.fall.95=quantile(dr.12.f.m,c(.05,.95),na.rm=TRUE)
d.12.fall.mean=mean(dr.12.f.m,na.rm=TRUE)
d.12.fall.sd=sd(dr.12.f.m,na.rm=TRUE)
```

##2012 Seasonal subsetted by plot
```{r}
p1.12.f=dat.12[dat.12$Plot %in% 1,]
p2.12.f=dat.12[dat.12$Plot %in% 2,]
p3.12.f=dat.12[dat.12$Plot %in% 3,]
p4.12.f=dat.12[dat.12$Plot %in% 4,]
p5.12.f=dat.12[dat.12$Plot %in% 5,]
p6.12.f=dat.12[dat.12$Plot %in% 6,]
p7.12.f=dat.12[dat.12$Plot %in% 7,]
p8.12.f=dat.12[dat.12$Plot %in% 8,]
p9.12.f=dat.12[dat.12$Plot %in% 9,]
p10.12.f=dat.12[dat.12$Plot %in% 10,]
p11.12.f=dat.12[dat.12$Plot %in% 11,]
p12.12.f=dat.12[dat.12$Plot %in% 12,]
p13.12.f=dat.12[dat.12$Plot %in% 13,]
p14.12.f=dat.12[dat.12$Plot %in% 14,]
p15.12.f=dat.12[dat.12$Plot %in% 15,]
p16.12.f=dat.12[dat.12$Plot %in% 16,]
p17.12.f=dat.12[dat.12$Plot %in% 17,]
p18.12.f=dat.12[dat.12$Plot %in% 18,]
p19.12.f=dat.12[dat.12$Plot %in% 19,]
p20.12.f=dat.12[dat.12$Plot %in% 20,]
p21.12.f=dat.12[dat.12$Plot %in% 21,]
p22.12.f=dat.12[dat.12$Plot %in% 22,]
p23.12.f=dat.12[dat.12$Plot %in% 23,]
p24.12.f=dat.12[dat.12$Plot %in% 24,]
p25.12.f=dat.12[dat.12$Plot %in% 25,]
p26.12.f=dat.12[dat.12$Plot %in% 26,]
p27.12.f=dat.12[dat.12$Plot %in% 27,]
p28.12.f=dat.12[dat.12$Plot %in% 28,]
p29.12.f=dat.12[dat.12$Plot %in% 29,]
p30.12.f=dat.12[dat.12$Plot %in% 30,]
p31.12.f=dat.12[dat.12$Plot %in% 31,]
p32.12.f=dat.12[dat.12$Plot %in% 32,]
p33.12.f=dat.12[dat.12$Plot %in% 33,]
p34.12.f=dat.12[dat.12$Plot %in% 34,]
p35.12.f=dat.12[dat.12$Plot %in% 35,]
p36.12.f=dat.12[dat.12$Plot %in% 36,]

#Plot subsetted by mass
p1.12.f.m=sum(as.numeric(p1.12.f$Total.Mass))
p2.12.f.m=sum(as.numeric(p2.12.f$Total.Mass))
p3.12.f.m=sum(as.numeric(p3.12.f$Total.Mass))
p4.12.f.m=sum(as.numeric(p4.12.f$Total.Mass))
p5.12.f.m=sum(as.numeric(p5.12.f$Total.Mass))
p6.12.f.m=sum(as.numeric(p6.12.f$Total.Mass))
p7.12.f.m=sum(as.numeric(p7.12.f$Total.Mass))
p8.12.f.m=sum(as.numeric(p8.12.f$Total.Mass))
p9.12.f.m=sum(as.numeric(p9.12.f$Total.Mass))
p10.12.f.m=sum(as.numeric(p10.12.f$Total.Mass))
p11.12.f.m=sum(as.numeric(p11.12.f$Total.Mass))
p12.12.f.m=sum(as.numeric(p12.12.f$Total.Mass))
p13.12.f.m=sum(as.numeric(p13.12.f$Total.Mass))
p14.12.f.m=sum(as.numeric(p14.12.f$Total.Mass))
p15.12.f.m=sum(as.numeric(p15.12.f$Total.Mass))
p16.12.f.m=sum(as.numeric(p16.12.f$Total.Mass))
p17.12.f.m=sum(as.numeric(p17.12.f$Total.Mass))
p18.12.f.m=sum(as.numeric(p18.12.f$Total.Mass))
p19.12.f.m=sum(as.numeric(p19.12.f$Total.Mass))
p20.12.f.m=sum(as.numeric(p20.12.f$Total.Mass))
p21.12.f.m=sum(as.numeric(p21.12.f$Total.Mass))
p22.12.f.m=sum(as.numeric(p22.12.f$Total.Mass))
p23.12.f.m=sum(as.numeric(p23.12.f$Total.Mass))
p24.12.f.m=sum(as.numeric(p24.12.f$Total.Mass))
p25.12.f.m=sum(as.numeric(p25.12.f$Total.Mass))
p26.12.f.m=sum(as.numeric(p26.12.f$Total.Mass))
p27.12.f.m=sum(as.numeric(p27.12.f$Total.Mass))
p28.12.f.m=sum(as.numeric(p28.12.f$Total.Mass))
p29.12.f.m=sum(as.numeric(p29.12.f$Total.Mass))
p30.12.f.m=sum(as.numeric(p30.12.f$Total.Mass))
p31.12.f.m=sum(as.numeric(p31.12.f$Total.Mass))
p32.12.f.m=sum(as.numeric(p32.12.f$Total.Mass))
p33.12.f.m=sum(as.numeric(p33.12.f$Total.Mass))
p34.12.f.m=sum(as.numeric(p34.12.f$Total.Mass))
p35.12.f.m=sum(as.numeric(p35.12.f$Total.Mass))
p36.12.f.m=sum(as.numeric(p36.12.f$Total.Mass))
```

#2013 Tree data
```{r}
dat.13<-dat.tree[dat.tree$year==2013,]
dat.13.fall.m=as.numeric(dat.13$tot.mass)
#Means,95% intervals, standarad deviation, 
dat.13.fall.95=quantile(dat.13.fall.m,c(.05,.95),na.rm=TRUE)
dat.13.fall.mean=mean(dat.13.fall.m,na.rm=TRUE)
dat.13.fall.sd=sd(dat.13.fall.m,na.rm=TRUE)
```

#2013 Tree height and mass subsets
```{r}
w.13<-dat.13[dat.13$Plot %in% c(9,10,11,12,17,18,19,20,25,26,27,28),]
d.13<-dat.13[dat.13$Plot %in% c(1,2,3,4,21,22,23,24,33,34,35,36),]
a.13<-dat.13[dat.13$Plot %in% c(5,6,7,8,13,14,15,16,29,30,31,32),]
w.13.tm=as.numeric(w.13$tot.mass)
d.13.tm=as.numeric(d.13$tot.mass)
a.13.tm=as.numeric(a.13$tot.mass)
##Summary Stats
w.13.fall.95=quantile(w.13.tm,c(.05,.95),na.rm=TRUE)
w.13.fall.mean=mean(w.13.tm,na.rm=TRUE)
w.13.fall.sd=sd(w.13.tm,na.rm=TRUE)

a.13.fall.95=quantile(a.13.tm,c(.05,.95),na.rm=TRUE)
a.13.fall.mean=mean(a.13.tm,na.rm=TRUE)
a.13.fall.sd=sd(a.13.tm,na.rm=TRUE)

d.13.fall.95=quantile(d.13.tm,c(.05,.95),na.rm=TRUE)
d.13.fall.mean=mean(d.13.tm,na.rm=TRUE)
d.13.fall.sd=sd(d.13.tm,na.rm=TRUE)
```

# 2013 Tree Plot Subsets
```{r}
p1.13=dat.13[dat.13$Plot %in% 1,]
p2.13=dat.13[dat.13$Plot %in% 2,]
p3.13=dat.13[dat.13$Plot %in% 3,]
p4.13=dat.13[dat.13$Plot %in% 4,]
p5.13=dat.13[dat.13$Plot %in% 5,]
p6.13=dat.13[dat.13$Plot %in% 6,]
p7.13=dat.13[dat.13$Plot %in% 7,]
p8.13=dat.13[dat.13$Plot %in% 8,]
p9.13=dat.13[dat.13$Plot %in% 9,]
p10.13=dat.13[dat.13$Plot %in% 10,]
p11.13=dat.13[dat.13$Plot %in% 11,]
p12.13=dat.13[dat.13$Plot %in% 12,]
p13.13=dat.13[dat.13$Plot %in% 13,]
p14.13=dat.13[dat.13$Plot %in% 14,]
p15.13=dat.13[dat.13$Plot %in% 15,]
p16.13=dat.13[dat.13$Plot %in% 16,]
p17.13=dat.13[dat.13$Plot %in% 17,]
p18.13=dat.13[dat.13$Plot %in% 18,]
p19.13=dat.13[dat.13$Plot %in% 19,]
p20.13=dat.13[dat.13$Plot %in% 20,]
p21.13=dat.13[dat.13$Plot %in% 21,]
p22.13=dat.13[dat.13$Plot %in% 22,]
p23.13=dat.13[dat.13$Plot %in% 23,]
p24.13=dat.13[dat.13$Plot %in% 24,]
p25.13=dat.13[dat.13$Plot %in% 25,]
p26.13=dat.13[dat.13$Plot %in% 26,]
p27.13=dat.13[dat.13$Plot %in% 27,]
p28.13=dat.13[dat.13$Plot %in% 28,]
p29.13=dat.13[dat.13$Plot %in% 29,]
p30.13=dat.13[dat.13$Plot %in% 30,]
p31.13=dat.13[dat.13$Plot %in% 31,]
p32.13=dat.13[dat.13$Plot %in% 32,]
p33.13=dat.13[dat.13$Plot %in% 33,]
p34.13=dat.13[dat.13$Plot %in% 34,]
p35.13=dat.13[dat.13$Plot %in% 35,]
p36.13=dat.13[dat.13$Plot %in% 36,]

p1.13.m=as.numeric(p1.13$tot.mass)
p2.13.m=as.numeric(p2.13$tot.mass)
p3.13.m=as.numeric(p3.13$tot.mass)
p4.13.m=as.numeric(p4.13$tot.mass)
p5.13.m=as.numeric(p5.13$tot.mass)
p6.13.m=as.numeric(p6.13$tot.mass)
p7.13.m=as.numeric(p7.13$tot.mass)
p8.13.m=as.numeric(p8.13$tot.mass)
p9.13.m=as.numeric(p9.13$tot.mass)
p10.13.m=as.numeric(p10.13$tot.mass)
p11.13.m=as.numeric(p11.13$tot.mass)
p12.13.m=as.numeric(p12.13$tot.mass)
p13.13.m=as.numeric(p13.13$tot.mass)
p14.13.m=as.numeric(p14.13$tot.mass)
p15.13.m=as.numeric(p15.13$tot.mass)
p16.13.m=as.numeric(p16.13$tot.mass)
p17.13.m=as.numeric(p17.13$tot.mass)
p18.13.m=as.numeric(p18.13$tot.mass)
p19.13.m=as.numeric(p19.13$tot.mass)
p20.13.m=as.numeric(p20.13$tot.mass)
p21.13.m=as.numeric(p21.13$tot.mass)
p22.13.m=as.numeric(p22.13$tot.mass)
p23.13.m=as.numeric(p23.13$tot.mass)
p24.13.m=as.numeric(p24.13$tot.mass)
p25.13.m=as.numeric(p25.13$tot.mass)
p26.13.m=as.numeric(p26.13$tot.mass)
p27.13.m=as.numeric(p27.13$tot.mass)
p28.13.m=as.numeric(p28.13$tot.mass)
p29.13.m=as.numeric(p29.13$tot.mass)
p30.13.m=as.numeric(p30.13$tot.mass)
p31.13.m=as.numeric(p31.13$tot.mass)
p32.13.m=as.numeric(p32.13$tot.mass)
p33.13.m=as.numeric(p33.13$tot.mass)
p34.13.m=as.numeric(p34.13$tot.mass)
p35.13.m=as.numeric(p35.13$tot.mass)
p36.13.m=as.numeric(p36.13$tot.mass)
```

#2013 Herbaceous season subset
```{r}
## 2013 year subsetted by season 
dat.13=dat.herb[dat.herb$Year==2013,]
dat.13.fall=dat.13[dat.13$Season=="Fall",]
dat.13.fall.m=as.numeric(dat.13.fall$Total.Mass)
#Means,95% intervals, standarad deviation, 
dat.13.fall.95=quantile(dat.13.fall.m,c(.05,.95))
dat.13.fall.mean=mean(dat.13.fall.m)
dat.13.fall.sd=sd(dat.13.fall.m)
```

#2013 Herb Subseted by treatment
```{r}
## Seasonal subsetted by treatment
wt.13.f=dat.13.fall[dat.13.fall$Treatment== "W",]
dr.13.f=dat.13.fall[dat.13.fall$Treatment== "D",]
ab.13.f=dat.13.fall[dat.13.fall$Treatment== "A",]

##Treatment subsetted by mass
wt.13.f.m=as.numeric(wt.13.f$Total.Mass) 
dr.13.f.m=as.numeric(dr.13.f$Total.Mass)
ab.13.f.m=as.numeric(ab.13.f$Total.Mass)

#Summary data
w.13.fall.95=quantile(wt.13.f.m,c(.05,.95),na.rm=TRUE)
w.13.fall.mean=mean(wt.13.f.m,na.rm=TRUE)
w.13.fall.sd=sd(wt.13.f.m,na.rm=TRUE)

a.13.fall.95=quantile(ab.13.f.m,c(.05,.95),na.rm=TRUE)
a.13.fall.mean=mean(ab.13.f.m,na.rm=TRUE)
a.13.fall.sd=sd(ab.13.f.m,na.rm=TRUE)

d.13.fall.95=quantile(dr.13.f.m,c(.05,.95),na.rm=TRUE)
d.13.fall.mean=mean(dr.13.f.m,na.rm=TRUE)
d.13.fall.sd=sd(dr.13.f.m,na.rm=TRUE)
```

#2013 Herb subsetted by plot
```{r}
## Seasonal subsetted by plot
p1.13.f=dat.13.fall[dat.13.fall$Plot %in% 1,]
p2.13.f=dat.13.fall[dat.13.fall$Plot %in% 2,]
p3.13.f=dat.13.fall[dat.13.fall$Plot %in% 3,]
p4.13.f=dat.13.fall[dat.13.fall$Plot %in% 4,]
p5.13.f=dat.13.fall[dat.13.fall$Plot %in% 5,]
p6.13.f=dat.13.fall[dat.13.fall$Plot %in% 6,]
p7.13.f=dat.13.fall[dat.13.fall$Plot %in% 7,]
p8.13.f=dat.13.fall[dat.13.fall$Plot %in% 8,]
p9.13.f=dat.13.fall[dat.13.fall$Plot %in% 9,]
p10.13.f=dat.13.fall[dat.13.fall$Plot %in% 10,]
p11.13.f=dat.13.fall[dat.13.fall$Plot %in% 11,]
p12.13.f=dat.13.fall[dat.13.fall$Plot %in% 12,]
p13.13.f=dat.13.fall[dat.13.fall$Plot %in% 13,]
p14.13.f=dat.13.fall[dat.13.fall$Plot %in% 14,]
p15.13.f=dat.13.fall[dat.13.fall$Plot %in% 15,]
p16.13.f=dat.13.fall[dat.13.fall$Plot %in% 16,]
p17.13.f=dat.13.fall[dat.13.fall$Plot %in% 17,]
p18.13.f=dat.13.fall[dat.13.fall$Plot %in% 18,]
p19.13.f=dat.13.fall[dat.13.fall$Plot %in% 19,]
p20.13.f=dat.13.fall[dat.13.fall$Plot %in% 20,]
p21.13.f=dat.13.fall[dat.13.fall$Plot %in% 21,]
p22.13.f=dat.13.fall[dat.13.fall$Plot %in% 22,]
p23.13.f=dat.13.fall[dat.13.fall$Plot %in% 23,]
p24.13.f=dat.13.fall[dat.13.fall$Plot %in% 24,]
p25.13.f=dat.13.fall[dat.13.fall$Plot %in% 25,]
p26.13.f=dat.13.fall[dat.13.fall$Plot %in% 26,]
p27.13.f=dat.13.fall[dat.13.fall$Plot %in% 27,]
p28.13.f=dat.13.fall[dat.13.fall$Plot %in% 28,]
p29.13.f=dat.13.fall[dat.13.fall$Plot %in% 29,]
p30.13.f=dat.13.fall[dat.13.fall$Plot %in% 30,]
p31.13.f=dat.13.fall[dat.13.fall$Plot %in% 31,]
p32.13.f=dat.13.fall[dat.13.fall$Plot %in% 32,]
p33.13.f=dat.13.fall[dat.13.fall$Plot %in% 33,]
p34.13.f=dat.13.fall[dat.13.fall$Plot %in% 34,]
p35.13.f=dat.13.fall[dat.13.fall$Plot %in% 35,]
p36.13.f=dat.13.fall[dat.13.fall$Plot %in% 36,]


#Plot subsetted by mass
p1.13.f.m=sum(as.numeric(p1.13.f$Total.Mass))
p2.13.f.m=sum(as.numeric(p2.13.f$Total.Mass))
p3.13.f.m=sum(as.numeric(p3.13.f$Total.Mass))
p4.13.f.m=sum(as.numeric(p4.13.f$Total.Mass))
p5.13.f.m=sum(as.numeric(p5.13.f$Total.Mass))
p6.13.f.m=sum(as.numeric(p6.13.f$Total.Mass))
p7.13.f.m=sum(as.numeric(p7.13.f$Total.Mass))
p8.13.f.m=sum(as.numeric(p8.13.f$Total.Mass))
p9.13.f.m=sum(as.numeric(p9.13.f$Total.Mass))
p10.13.f.m=sum(as.numeric(p10.13.f$Total.Mass))
p11.13.f.m=sum(as.numeric(p13.13.f$Total.Mass))
p12.13.f.m=sum(as.numeric(p12.13.f$Total.Mass))
p13.13.f.m=sum(as.numeric(p13.13.f$Total.Mass))
p14.13.f.m=sum(as.numeric(p14.13.f$Total.Mass))
p15.13.f.m=sum(as.numeric(p15.13.f$Total.Mass))
p16.13.f.m=sum(as.numeric(p16.13.f$Total.Mass))
p17.13.f.m=sum(as.numeric(p17.13.f$Total.Mass))
p18.13.f.m=sum(as.numeric(p18.13.f$Total.Mass))
p19.13.f.m=sum(as.numeric(p19.13.f$Total.Mass))
p20.13.f.m=sum(as.numeric(p20.13.f$Total.Mass))
p21.13.f.m=sum(as.numeric(p21.13.f$Total.Mass))
p22.13.f.m=sum(as.numeric(p22.13.f$Total.Mass))
p23.13.f.m=sum(as.numeric(p23.13.f$Total.Mass))
p24.13.f.m=sum(as.numeric(p24.13.f$Total.Mass))
p25.13.f.m=sum(as.numeric(p25.13.f$Total.Mass))
p26.13.f.m=sum(as.numeric(p26.13.f$Total.Mass))
p27.13.f.m=sum(as.numeric(p27.13.f$Total.Mass))
p28.13.f.m=sum(as.numeric(p28.13.f$Total.Mass))
p29.13.f.m=sum(as.numeric(p29.13.f$Total.Mass))
p30.13.f.m=sum(as.numeric(p30.13.f$Total.Mass))
p31.13.f.m=sum(as.numeric(p31.13.f$Total.Mass))
p32.13.f.m=sum(as.numeric(p32.13.f$Total.Mass))
p33.13.f.m=sum(as.numeric(p33.13.f$Total.Mass))
p34.13.f.m=sum(as.numeric(p34.13.f$Total.Mass))
p35.13.f.m=sum(as.numeric(p35.13.f$Total.Mass))
p36.13.f.m=sum(as.numeric(p36.13.f$Total.Mass))


```


#2014 subsetted by season
```{r}
## 2014 year subsetted by season 
dat.14=dat.herb[dat.herb$Year==2014,]
dat.14.fall=dat.14[dat.14$Season=="Fall",]
dat.14.fall.m=as.numeric(dat.14.fall$Total.Mass)
#Means,95% intervals, standarad deviation, 
dat.14.fall.95=quantile(dat.14.fall.m,c(.05,.95))
dat.14.fall.mean=mean(dat.14.fall.m)
dat.14.fall.sd=sd(dat.14.fall.m)
```

##2014 subsetted by treatment
```{r}
## Seasonal subsetted by treatment
wt.14.f=dat.14.fall[dat.14.fall$Treatment== "W",]
dr.14.f=dat.14.fall[dat.14.fall$Treatment== "D",]
ab.14.f=dat.14.fall[dat.14.fall$Treatment== "A",]

##Treatment subsetted by mass
wt.14.f.m=as.numeric(wt.14.f$Total.Mass) 
dr.14.f.m=as.numeric(dr.14.f$Total.Mass)
ab.14.f.m=as.numeric(ab.14.f$Total.Mass)
#Summary data
w.14.fall.95=quantile(wt.14.f.m,c(.05,.95),na.rm=TRUE)
w.14.fall.mean=mean(wt.14.f.m,na.rm=TRUE)
w.14.fall.sd=sd(wt.14.f.m,na.rm=TRUE)

a.14.fall.95=quantile(ab.14.f.m,c(.05,.95),na.rm=TRUE)
a.14.fall.mean=mean(ab.14.f.m,na.rm=TRUE)
a.14.fall.sd=sd(ab.14.f.m,na.rm=TRUE)

d.14.fall.95=quantile(dr.14.f.m,c(.05,.95),na.rm=TRUE)
d.14.fall.mean=mean(dr.14.f.m,na.rm=TRUE)
d.14.fall.sd=sd(dr.14.f.m,na.rm=TRUE)
```

##2014 subsetted by plot
```{r}
## Seasonal subsetted by plot
p1.14.f=dat.14.fall[dat.14.fall$Plot %in% 1,]
p2.14.f=dat.14.fall[dat.14.fall$Plot %in% 2,]
p3.14.f=dat.14.fall[dat.14.fall$Plot %in% 3,]
p4.14.f=dat.14.fall[dat.14.fall$Plot %in% 4,]
p5.14.f=dat.14.fall[dat.14.fall$Plot %in% 5,]
p6.14.f=dat.14.fall[dat.14.fall$Plot %in% 6,]
p7.14.f=dat.14.fall[dat.14.fall$Plot %in% 7,]
p8.14.f=dat.14.fall[dat.14.fall$Plot %in% 8,]
p9.14.f=dat.14.fall[dat.14.fall$Plot %in% 9,]
p10.14.f=dat.14.fall[dat.14.fall$Plot %in% 10,]
p11.14.f=dat.14.fall[dat.14.fall$Plot %in% 11,]
p12.14.f=dat.14.fall[dat.14.fall$Plot %in% 12,]
p13.14.f=dat.14.fall[dat.14.fall$Plot %in% 13,]
p14.14.f=dat.14.fall[dat.14.fall$Plot %in% 14,]
p15.14.f=dat.14.fall[dat.14.fall$Plot %in% 15,]
p16.14.f=dat.14.fall[dat.14.fall$Plot %in% 16,]
p17.14.f=dat.14.fall[dat.14.fall$Plot %in% 17,]
p18.14.f=dat.14.fall[dat.14.fall$Plot %in% 18,]
p19.14.f=dat.14.fall[dat.14.fall$Plot %in% 19,]
p20.14.f=dat.14.fall[dat.14.fall$Plot %in% 20,]
p21.14.f=dat.14.fall[dat.14.fall$Plot %in% 21,]
p22.14.f=dat.14.fall[dat.14.fall$Plot %in% 22,]
p23.14.f=dat.14.fall[dat.14.fall$Plot %in% 23,]
p24.14.f=dat.14.fall[dat.14.fall$Plot %in% 24,]
p25.14.f=dat.14.fall[dat.14.fall$Plot %in% 25,]
p26.14.f=dat.14.fall[dat.14.fall$Plot %in% 26,]
p27.14.f=dat.14.fall[dat.14.fall$Plot %in% 27,]
p28.14.f=dat.14.fall[dat.14.fall$Plot %in% 28,]
p29.14.f=dat.14.fall[dat.14.fall$Plot %in% 29,]
p30.14.f=dat.14.fall[dat.14.fall$Plot %in% 30,]
p31.14.f=dat.14.fall[dat.14.fall$Plot %in% 31,]
p32.14.f=dat.14.fall[dat.14.fall$Plot %in% 32,]
p33.14.f=dat.14.fall[dat.14.fall$Plot %in% 33,]
p34.14.f=dat.14.fall[dat.14.fall$Plot %in% 34,]
p35.14.f=dat.14.fall[dat.14.fall$Plot %in% 35,]
p36.14.f=dat.14.fall[dat.14.fall$Plot %in% 36,]



#Plot subsetted by mass
p1.14.f.m=sum(as.numeric(p1.14.f$Total.Mass))
p2.14.f.m=sum(as.numeric(p2.14.f$Total.Mass))
p3.14.f.m=sum(as.numeric(p3.14.f$Total.Mass))
p4.14.f.m=sum(as.numeric(p4.14.f$Total.Mass))
p5.14.f.m=sum(as.numeric(p5.14.f$Total.Mass))
p6.14.f.m=sum(as.numeric(p6.14.f$Total.Mass))
p7.14.f.m=sum(as.numeric(p7.14.f$Total.Mass))
p8.14.f.m=sum(as.numeric(p8.14.f$Total.Mass))
p9.14.f.m=sum(as.numeric(p9.14.f$Total.Mass))
p10.14.f.m=sum(as.numeric(p10.14.f$Total.Mass))
p11.14.f.m=sum(as.numeric(p11.14.f$Total.Mass))
p12.14.f.m=sum(as.numeric(p12.14.f$Total.Mass))
p13.14.f.m=sum(as.numeric(p13.14.f$Total.Mass))
p14.14.f.m=sum(as.numeric(p14.14.f$Total.Mass))
p15.14.f.m=sum(as.numeric(p15.14.f$Total.Mass))
p16.14.f.m=sum(as.numeric(p16.14.f$Total.Mass))
p17.14.f.m=sum(as.numeric(p17.14.f$Total.Mass))
p18.14.f.m=sum(as.numeric(p18.14.f$Total.Mass))
p19.14.f.m=sum(as.numeric(p19.14.f$Total.Mass))
p20.14.f.m=sum(as.numeric(p20.14.f$Total.Mass))
p21.14.f.m=sum(as.numeric(p21.14.f$Total.Mass))
p22.14.f.m=sum(as.numeric(p22.14.f$Total.Mass))
p23.14.f.m=sum(as.numeric(p23.14.f$Total.Mass))
p24.14.f.m=sum(as.numeric(p24.14.f$Total.Mass))
p25.14.f.m=sum(as.numeric(p25.14.f$Total.Mass))
p26.14.f.m=sum(as.numeric(p26.14.f$Total.Mass))
p27.14.f.m=sum(as.numeric(p27.14.f$Total.Mass))
p28.14.f.m=sum(as.numeric(p28.14.f$Total.Mass))
p29.14.f.m=sum(as.numeric(p29.14.f$Total.Mass))
p30.14.f.m=sum(as.numeric(p30.14.f$Total.Mass))
p31.14.f.m=sum(as.numeric(p31.14.f$Total.Mass))
p32.14.f.m=sum(as.numeric(p32.14.f$Total.Mass))
p33.14.f.m=sum(as.numeric(p33.14.f$Total.Mass))
p34.14.f.m=sum(as.numeric(p34.14.f$Total.Mass))
p35.14.f.m=sum(as.numeric(p35.14.f$Total.Mass))
p36.14.f.m=sum(as.numeric(p36.14.f$Total.Mass))

```


```{r}
years=c(1:14)
m.bm=c(dat.08.summ.mean,dat.08.fall.mean,dat.09.summ.mean, dat.09.fall.mean,NA,dat.10.summ.mean,dat.11.summ.mean,dat.11.fall.mean,NA,dat.12.fall.mean,NA,dat.13.fall.mean,NA,dat.14.fall.mean)

## Mean Biomass Time Series
plot(years,m.bm)

## Treatments Mean Biomass  Time Series
wet.m.bm=c(w.08.summ.mean,w.08.fall.mean,w.09.summ.mean, w.09.fall.mean,NA,w.10.summ.mean,w.11.summ.mean,w.11.fall.mean,NA,w.12.fall.mean,NA,w.13.fall.mean,NA,w.14.fall.mean)

amb.m.bm=c(a.08.summ.mean,a.08.fall.mean,a.09.summ.mean, a.09.fall.mean,NA,a.10.summ.mean,a.11.summ.mean,a.11.fall.mean,NA,a.12.fall.mean,NA,a.13.fall.mean,NA,a.14.fall.mean)

dry.m.bm=c(d.08.summ.mean,d.08.fall.mean,d.09.summ.mean, d.09.fall.mean,NA,d.10.summ.mean,d.11.summ.mean,d.11.fall.mean,NA,d.12.fall.mean,NA,d.13.fall.mean,NA,d.14.fall.mean)

plot(years,wet.m.bm,ylab="Mass", type="b")
points(years,amb.m.bm,col=2,type="b")
points(years,dry.m.bm,col=3,type="b")



standev.m=c(dat.08.summ.sd,dat.08.fall.sd,dat.09.summ.sd,dat.09.fall.sd,NA,NA,NA,dat.11.fall.sd,NA,dat.12.fall.sd,NA,dat.13.fall.sd,NA,dat.14.fall.sd)

w.standev.m=c(w.08.summ.sd,w.08.fall.sd,w.09.summ.sd,w.09.fall.sd,NA,NA,NA,w.11.fall.sd,NA,w.12.fall.sd,NA,w.13.fall.sd,NA,w.14.fall.sd)

a.standev.m=c(a.08.summ.sd,a.08.fall.sd,a.09.summ.sd,a.09.fall.sd,NA,NA,NA,a.11.fall.sd,NA,a.12.fall.sd,NA,a.13.fall.sd,NA,a.14.fall.sd)

d.standev.m=c(d.08.summ.sd,d.08.fall.sd,d.09.summ.sd,d.09.fall.sd,NA,NA,NA,d.11.fall.sd,NA,d.12.fall.sd,NA,d.13.fall.sd,NA,d.14.fall.sd)

conf.int=c(dat.08.summ.95,dat.08.fall.95,dat.09.summ.95,dat.09.fall.95,NA,NA,NA,dat.11.fall.95,NA,dat.12.fall.95,NA,dat.13.fall.95,NA,dat.14.fall.95)

w.int=c(w.08.summ.95,w.08.fall.95,w.09.summ.95,w.09.fall.95,NA,NA,NA,w.11.fall.95,NA,w.12.fall.95,NA,w.13.fall.95,NA,w.14.fall.95)

d.int=c(d.08.summ.95,d.08.fall.95,d.09.summ.95,d.09.fall.95,NA,NA,NA,d.11.fall.95,NA,d.12.fall.95,NA,d.13.fall.95,NA,d.14.fall.95)

a.int=c(d.08.summ.95,a.08.fall.95,a.09.summ.95,a.09.fall.95,NA,NA,NA,a.11.fall.95,NA,a.12.fall.95,NA,a.13.fall.95,NA,a.14.fall.95)

summary.data=c(years,m.bm,standev.m)

summary.table=matrix(summary.data,nrow=14,ncol=4,byrow=FALSE,)
```

```{r}
seq1=c(1,2,3,4,5,7,8,10,12,14)
seq1
plot(seq1,c(p36.08.s.m,p36.08.f.m,p36.09.s.m,p36.09.f.m,p36.10.s.m,p36.11.f.m,p36.11.s.m,p36.12.f.m,p36.13.f.m,p36.14.f.m),type="b",ylab="plot 36 biomass")


#functional groups
dat.08=dat.herb[dat.herb$Year==2008,]
dat.08.fall=dat.08[dat.08$Season=="Fall",]
dat.08.summ=dat.08[dat.08$Season=="Summer",]
## Seasonal subsetted by functional group
#2008
c4.08.f=dat.08.fall[dat.08.fall$C4>0,]
c4.08.s=dat.08.summ[dat.08.summ$C4>0,]
c3.08.f=dat.08.fall[dat.08.fall$C3>0,]
c3.08.s=dat.08.summ[dat.08.summ$C3>0,]
Pr.08.f=dat.08.fall[dat.08.fall$Perennial>0,]
Pr.08.s=dat.08.summ[dat.08.summ$Perennial>0,]
AB.08.f=dat.08.fall[dat.08.fall$Annl.Biennial>0,]
AB.08.s=dat.08.summ[dat.08.summ$Annl.Biennial>0,]

c4.08.f.m=sum(as.numeric(c4.08.f$C4))

##c4.08.f.seq=cc(c4.08.f$C4,c4.08.f$Plot) Trying to get plots with data, should try the ;line before tomorrow, its bedtime

c4.08.s.m=sum(as.numeric(c4.08.s$C4))
c3.08.f.m=sum(as.numeric(c3.08.f$C3))
c3.08.s.m=sum(as.numeric(c3.08.s$C3))
Pr.08.f.m=sum(as.numeric(Pr.08.f$Perennial))
Pr.08.s.m=sum(as.numeric(Pr.08.s$Perennial))
AB.08.f.m=sum(as.numeric(AB.08.f$Annl.Biennial))
AB.08.s.m=sum(as.numeric(AB.08.s$Annl.Biennial))

#2009
c4.09.f=dat.09.fall[dat.09.fall$C4>0,]
c4.09.s=dat.09.summ[dat.09.summ$C4>0,]
c3.09.f=dat.09.fall[dat.09.fall$C3>0,]
c3.09.s=dat.09.summ[dat.09.summ$C3>0,]
Pr.09.f=dat.09.fall[dat.09.fall$Perennial>0,]
Pr.09.s=dat.09.summ[dat.09.summ$Perennial>0,]
AB.09.f=dat.09.fall[dat.09.fall$Annl.Biennial>0,]
AB.09.s=dat.09.summ[dat.09.summ$Annl.Biennial>0,]

c4.09.f.m=sum(as.numeric(c4.09.f$C4))
c4.09.s.m=sum(as.numeric(c4.09.s$C4))
c3.09.f.m=sum(as.numeric(c3.09.f$C3))
c3.09.s.m=sum(as.numeric(c3.09.s$C3))
Pr.09.f.m=sum(as.numeric(Pr.09.f$Perennial))
Pr.09.s.m=sum(as.numeric(Pr.09.s$Perennial))
AB.09.f.m=sum(as.numeric(AB.09.f$Annl.Biennial))
AB.09.s.m=sum(as.numeric(AB.09.s$Annl.Biennial))

#2010
c4.10.s=dat.10.summ[dat.10.summ$C4>0,]
c3.10.s=dat.10.summ[dat.10.summ$C3>0,]
Pr.10.s=dat.10.summ[dat.10.summ$Perennial>0,]
AB.10.s=dat.10.summ[dat.10.summ$Annl.Biennial>0,]

c4.10.s.m=sum(as.numeric(c4.10.s$C4))
c3.10.s.m=sum(as.numeric(c3.10.s$C3))
Pr.10.s.m=sum(as.numeric(Pr.10.s$Perennial))
AB.10.s.m=sum(as.numeric(AB.10.s$Annl.Biennial))

#2011
c4.11.f=dat.11.fall[dat.11.fall$C4>0,]
c4.11.s=dat.11.summ[dat.11.summ$C4>0,]
c3.11.f=dat.11.fall[dat.11.fall$C3>0,]
c3.11.s=dat.11.summ[dat.11.summ$C3>0,]
Pr.11.f=dat.11.fall[dat.11.fall$Perennial>0,]
Pr.11.s=dat.11.summ[dat.11.summ$Perennial>0,] #check and update csv with correct 2011 files
AB.11.f=dat.11.fall[dat.11.fall$Annl.Biennial>0,]
AB.11.s=dat.11.summ[dat.11.summ$Annl.Biennial>0,]

c4.11.f.m=sum(as.numeric(c4.11.f$C4))
c4.11.s.m=sum(as.numeric(c4.11.s$C4))
c3.11.f.m=sum(as.numeric(c3.11.f$C3))
c3.11.s.m=sum(as.numeric(c3.11.s$C3))
Pr.11.f.m=sum(as.numeric(Pr.11.f$Perennial))
Pr.11.s.m=sum(as.numeric(Pr.11.s$Perennial))
AB.11.f.m=sum(as.numeric(AB.11.f$Annl.Biennial))
AB.11.s.m=sum(as.numeric(AB.11.s$Annl.Biennial))

#2012
c4.12.f=dat.12.fall[dat.12.fall$C4>0,]
c3.12.f=dat.12.fall[dat.12.fall$C3>0,]
Pr.12.f=dat.12.fall[dat.12.fall$Perennial>0,]
AB.12.f=dat.12.fall[dat.12.fall$Annl.Biennial>0,]

c4.12.f.m=sum(as.numeric(c4.12.f$C4))
c3.12.f.m=sum(as.numeric(c3.12.f$C3))
Pr.12.f.m=sum(as.numeric(Pr.12.f$Perennial))
AB.12.f.m=sum(as.numeric(AB.12.f$Annl.Biennial))

#2013
c4.13.f=dat.13.fall[dat.13.fall$C4>0,]
c3.13.f=dat.13.fall[dat.13.fall$C3>0,]
Pr.13.f=dat.13.fall[dat.13.fall$Perennial>0,] ##plot 17 is negative
AB.13.f=dat.13.fall[dat.13.fall$Annl.Biennial>0,]

c4.13.f.m=sum(as.numeric(c4.13.f$C4))
c3.13.f.m=sum(as.numeric(c3.13.f$C3))
Pr.13.f.m=sum(as.numeric(Pr.13.f$Perennial))
AB.13.f.m=sum(as.numeric(AB.13.f$Annl.Biennial))

#2014
c4.14.f=dat.14.fall[dat.14.fall$C4>0,]
c3.14.f=dat.14.fall[dat.14.fall$C3>0,]
Pr.14.f=dat.14.fall[dat.14.fall$Perennial>0,]
AB.14.f=dat.14.fall[dat.14.fall$Annl.Biennial>0,]

c4.14.f.m=sum(as.numeric(c4.14.f$C4))
c3.14.f.m=sum(as.numeric(c3.14.f$C3))
Pr.14.f.m=sum(as.numeric(Pr.14.f$Perennial))
AB.14.f.m=sum(as.numeric(AB.14.f$Annl.Biennial))

#C4 Grasses over time
plot(seq1,c(c4.08.s.m,c4.08.f.m,c4.09.s.m,c4.09.f.m,c4.10.s.m,c4.11.s.m,c4.11.f.m,c4.12.f.m,c4.13.f.m,c4.14.f.m),type="b",ylab="C4 Grasses over time")
#C3 Grasses over time
plot(seq1,c(c3.08.s.m,c3.08.f.m,c3.09.s.m,c3.09.f.m,c3.10.s.m,c3.11.s.m,c3.11.f.m,c3.12.f.m,c3.13.f.m,c3.14.f.m),type="b",ylab="C3 Grasses over time")
#Perennial Forbs over time
plot(seq1,c(Pr.08.s.m,Pr.08.f.m,Pr.09.s.m,Pr.09.f.m,Pr.10.s.m,Pr.11.s.m,Pr.11.f.m,Pr.12.f.m,Pr.13.f.m,Pr.14.f.m),type="b",ylab="Perennial Forbs over time")
#Annual/Biennial Forbs over time
plot(seq1,c(AB.08.s.m,AB.08.f.m,AB.09.s.m,AB.09.f.m,AB.10.s.m,AB.11.s.m,AB.11.f.m,AB.12.f.m,AB.13.f.m,AB.14.f.m),type="b",ylab="Annual/Biennial Forbs over time")
```